### 2024-09-10 Manuscript/manuscript.tex
introduction of the manuscript

\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage[table,xcdraw]{xcolor}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{yfonts}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\useunder{\uline}{\ul}{}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{}
\newcommand\subject{Final Degree Project}
\newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
\newcommand\hwnumber{1}                  % <-- homework number
\newcommand\NetIDb{Universitat Autònoma de Barcelona}           % <-- NetID of person #2 (Comment this line out for problem sets)

\begin{document}
\title{\vspace{5cm} \normalsize \textsc{\NetIDb}
		\\ [2.0cm]
		\HRule{0.5pt} \\
		\LARGE \textbf{\uppercase{\documenttitle}}
		\HRule{2pt} \\ [0.5cm]
		\normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\
		}\normalsize \vspace*{5\baselineskip}}

\date{\today}

\author{\large \textsc{\subject}}

\begin{titlepage}
\clearpage\maketitle
\thispagestyle{empty}
\end{titlepage}

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\rfoot{\small\thepage}
\headsep 1.5em
The current manuscript format is temporal!!!

\end{document}

### 2024-09-10 Manuscript/manuscript.tex
Adding the references file

@@
 \newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
-\newcommand\hwnumber{1}                  % <-- homework number
-\newcommand\NetIDb{Universitat Autònoma de Barcelona}           % <-- NetID of person #2 (Comment this line out for problem sets)
+\newcommand\hwnumber{1} 
+\newcommand\NetIDb{Universitat Autònoma de Barcelona}
 
@@
 \rhead{\subject}
+\cfoot{}
 \rfoot{\small\thepage}
 \headsep 1.5em
-The current manuscript format is temporal!!!
+The current manuscript's format is temporal!!!\par
+Testing cite: \cite{NationalLibraryOfMedicineGeneralArticle}
+
+\newpage
+%Bibliography %
+\bibliographystyle{plain}
+\bibliography{references} 
+%%%%%%%%
 

### 2024-09-23 Notes/definitions.tex
Definitions and observations of generalities of ML

\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage[table,xcdraw]{xcolor}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{yfonts}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\useunder{\uline}{\ul}{}

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{}
\newcommand\subject{Final Degree Project}
\newcommand\degree{Bachelor's Degree in Chemistry}
\newcommand\documenttitle{Notes: AI application for azophotoswitches' optimization with pharmacological interest}
\newcommand\NetIDb{Universitat Autònoma de Barcelona}

\begin{document}
\title{\vspace{4cm} \normalsize 
		\includegraphics[width = 0.25\textwidth]{GeneralSources/UABLogo.png}\\ [0.5cm]
		\textsc{\NetIDb}\\ [2.0cm]
		\HRule{0.5pt} \\
		\LARGE \textbf{\uppercase{\documenttitle}}
		\HRule{2pt} \\ [1.5cm]
		\normalsize \begin{tabular}{rcl}  % Create a right-left column alignment
        \textsc{Author} & : & \textsc{Sergio Castañeiras Morales} \\
        \textsc{Supervisor} & : & \textsc{Miquel Moreno Ferrer} \\
        \textsc{Co-Supervisor} & : & \textsc{Àngels Gonzalez Lafont}
    \end{tabular}
    \normalsize \vspace*{5\baselineskip}
		}

\date{2024-2025}

\author{\large \textsc{\subject} \\ \textsc{\degree}}

\begin{titlepage}
\clearpage\maketitle
\thispagestyle{empty}
\end{titlepage}

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em
\begin{multicols}{2}
[
\section{Definitions}
]
\begin{definition}\label{definitionIC50}
$IC_{50}$: Half maximal inhibitory concentration "$IC_{50}$ is the concentration of drug required for $50\%$ inhibition. $IC_{50}$ is an operational term dependent on the assay conditions. $IC_{90}$ or $IC_{99}$ is sometimes used when complete inhibition is required. Calculation of the fractional occupancy shows that $IC_{90}$ concentration is approximately 10-fold greater than the $IC_{50}$ concentration assuming one-site binding at equilibrium with a Hill coefficient of 1."\cite{BookIC50}\\
 For this project, we aim to identify substances with the lowest possible $IC_{50}$, as our goal is to minimize the presence of foreign substances in the living organism.
\end{definition}
\begin{definition}
Molecular descriptor: "A molecular descriptor is the final result of a logical and mathematical procedure which transforms chemical information encoded within a symbolic representation of a molecule into a useful number or the result of some standardized experiment."\cite{DescriptorsBook}
\end{definition}
\end{multicols}
\newpage
\begin{multicols}{2}
[
\section{Observations}
]
\begin{observation}
Machine Leaning (ML) and Artificial Intelligence (AI) are not the same concept, in fact, a ML  models are a subset of AIs. The key relies in word \emph{Learning}, generally speaking, an AI does not need to actually learn from a set of data. It can be set up within a decision tree such that logically responses with the proper answer following its criteria. \par
However a Machine Leaning Method is a kind of AI that \emph{learns} from data and evolves with the provided data.
\end{observation}
\begin{observation}
Mathematically speaking, Machine Learning methods are no different from an optimisation problem \cite{MathematicsForMachineLearningBook}.\par
Generally speaking, all ML methods seek to find a criterion to determine the quantity of a certain property of some data, which we lack knowledge of and will call the \emph{target}. In order to do so, they rely on a dataset where the sought property is already known and which establishes relationships between this property and other features of the data. Then, based on these relationships and the properties of the \emph{target}, the model searches for the position where the \emph{target} fits within the data and determines the quantity of the property, taking this placement into account within the known data.\par
For instance, we could think of standard calibration with linear regression as an ultra-simplification of a Machine Learning problem. We have a set of data (such as salt concentration in a solution) $\{x_i\}_{i=0}^n$, where we know the quantity of a certain property (such as the solution's conductivity) for each entry $x_j$, denoted as $\{f(x_i)\}_{i=0}^n$. In this example, our ML method assumes that the data and the property are linearly related and that the distance between data and the property is equivalently defined as $d(x_i, x_j) = \sqrt{x_i^2 + x_j^2}$. Hence, based on the assumption of linearity, the best possible relationship is a straight line, and the method looks for the line that minimises the distance between the line and the data.\par
Then, given a \emph{target} (for instance, a certain concentration), about which we initially lack knowledge, the method is capable of quantitatively computing the theoretical property (for instance, its conductivity) by using the fitted line representing the relationship. Consequently, this can be helpful in determining the theoretical concentration of salt needed to achieve a certain conductivity without having actual data for that concentration.\par
The \emph{learning} part (the most important part) comes from the fact that the model (the line) learns from the data. As we train our system (i.e., perform linear regression) with increasingly larger datasets, the accuracy of our model's predictions improves. Thus, we can conclude that the system is \emph{learning} from the data, which qualifies it as a Machine Learning model.\par
\end{observation}
\begin{observation}
Since we are working with molecules our Machine Learning model will need from a certain parameters to determine the relationship with the property. \par
Surely our \emph{property} (i.e., $\{f(x_i)\}_{i=0}^n$) will be the inhibition of a certain protein (COX-2) in this case more accurately will be $IC_{50}$/$IC_{90}$/$IC_{99}$ (\ref{definitionIC50}).\par
Moreover, our \emph{parameters} (i.e., $\{x_i\}_{i=0}^n$) will be the descriptors of the molecules which must be \textbf{carefully chosen}. This problem has extra difficulties in comparison to the linear regression one. 
\begin{itemize}
\item Will be taking about $10^3$ descriptors, then it turns out to a $10^3$ dimension problem.
\item We want the system to automatically discard non-relevant data since some molecules could be exceptions for external causes.
\item We do not have linearity. 
\item All the descriptors do not have the same distancies/weights since we'll want some of them to be more relevant than others.
\end{itemize}
But, fun fact, in some way, we can say that this project will be no different from computing a linear regression...
\end{observation}
\end{multicols}

\newpage
%Bibliography %
\bibliographystyle{plain}
\bibliography{references} 
%%%%%%%%

\end{document}

### 2024-09-23 Notes/definitions.tex
Definitions and observations of generalities of ML

@@
 \begin{observation}
-Since we are working with molecules our Machine Learning model will need from a certain parameters to determine the relationship with the property. \par
-Surely our \emph{property} (i.e., $\{f(x_i)\}_{i=0}^n$) will be the inhibition of a certain protein (COX-2) in this case more accurately will be $IC_{50}$/$IC_{90}$/$IC_{99}$ (\ref{definitionIC50}).\par
-Moreover, our \emph{parameters} (i.e., $\{x_i\}_{i=0}^n$) will be the descriptors of the molecules which must be \textbf{carefully chosen}.
-This problem has extra difficulties in comparison to the linear regression one.
+Since we are working with molecules, our Machine Learning model will require certain parameters to determine the relationship with the property.\par
+In this case, our \emph{property} (i.e., $\{f(x_i)\}_{i=0}^n$) will be the inhibition of a specific protein (COX-2), and more specifically, it will be $IC_{50}$, $IC_{90}$, or $IC_{99}$ (\ref{definitionIC50}).\par
+Moreover, our \emph{parameters} (i.e., $\{x_i\}_{i=0}^n$) will be the molecular descriptors, which must be \textbf{carefully chosen}.
+This problem introduces additional complexities compared to the linear regression case:
 \begin{itemize}
-\item Will be taking about $10^3$ descriptors, then it turns out to a $10^3$ dimension problem.
-\item We want the system to automatically discard non-relevant data since some molecules could be exceptions for external causes.
-\item We do not have linearity. 
-\item All the descriptors do not have the same distancies/weights since we'll want some of them to be more relevant than others.
+    \item We will be working with approximately $10^3$ descriptors, making this a $10^3$-dimensional problem.
+    \item We want the system to automatically discard non-relevant data, as some molecules could be exceptions due to external factors.
+    \item We do not assume linearity.
+    \item Not all descriptors have the same distances or weights, as we will want some of them to be more relevant than others.
 \end{itemize}
-But, fun fact, in some way, we can say that this project will be no different from computing a linear regression...
+Interestingly enough, despite these complexities, in some way, we can say that this project is not entirely different from computing a linear regression...
 \end{observation}

### 2024-09-24 Notes/Notes.tex
defining some descriptors

\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage[table,xcdraw]{xcolor}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{float}
\usepackage{chemfig}
\usepackage{yfonts}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\useunder{\uline}{\ul}{}

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{reflection}{Reflection}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{}
\newcommand\subject{Final Degree Project}
\newcommand\degree{Bachelor's Degree in Chemistry}
\newcommand\documenttitle{Notes: AI application for azophotoswitches' optimization with pharmacological interest}
\newcommand\NetIDb{Universitat Autònoma de Barcelona}

\begin{document}
\title{\vspace{4cm} \normalsize 
		\includegraphics[width = 0.25\textwidth]{GeneralSources/UABLogo.png}\\ [0.5cm]
		\textsc{\NetIDb}\\ [2.0cm]
		\HRule{0.5pt} \\
		\LARGE \textbf{\uppercase{\documenttitle}}
		\HRule{2pt} \\ [1.5cm]
		\normalsize \begin{tabular}{rcl}  % Create a right-left column alignment
        \textsc{Author} & : & \textsc{Sergio Castañeiras Morales} \\
        \textsc{Supervisor} & : & \textsc{Miquel Moreno Ferrer} \\
        \textsc{Co-Supervisor} & : & \textsc{Àngels Gonzalez Lafont}
    \end{tabular}
    \normalsize \vspace*{5\baselineskip}
		}

\date{2024-2025}

\author{\large \textsc{\subject} \\ \textsc{\degree}}

\begin{titlepage}
\clearpage\maketitle
\thispagestyle{empty}
\end{titlepage}

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% DEFINITIONS %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}
[
\section{Definitions}
]
\begin{definition}\label{definitionIC50}
$IC_{50}$: Half maximal inhibitory concentration "$IC_{50}$ is the concentration of drug required for $50\%$ inhibition. $IC_{50}$ is an operational term dependent on the assay conditions. $IC_{90}$ or $IC_{99}$ is sometimes used when complete inhibition is required. Calculation of the fractional occupancy shows that $IC_{90}$ concentration is approximately 10-fold greater than the $IC_{50}$ concentration assuming one-site binding at equilibrium with a Hill coefficient of 1."\cite{BookIC50}\\
 For this project, we aim to identify substances with the lowest possible $IC_{50}$, as our goal is to minimize the presence of foreign substances in the living organism.
\end{definition}

\begin{definition}
Molecular descriptor: "A molecular descriptor is the final result of a logical and mathematical procedure which transforms chemical information encoded within a symbolic representation of a molecule into a useful number or the result of some standardized experiment."\cite{DescriptorsBook}
\end{definition}

\begin{definition}
Constitutional Indices Descriptors: Kind of descriptor based on the constitutional composure of a molecule. They describe the basic composition of the molecule without considering its geometry or connectivity of it.
\end{definition}

\begin{definition}
Ring Descriptors: Kind of descriptor that describes the ring systems of our molecule. Quantifies properties such as the ring connectivity, type of ring (odd/even ring), aromaticy \& saturation.
\end{definition}

\begin{definition}
Topological Indices: These descriptors are based on the connectivity of atoms in a molecule without considering three-dimensional coordinates in the context of chemical graph theory. They help to describe the molecular graph (atoms as vertices, bonds as edges) using metrics like the Wiener index or the Zagreb index.
\end{definition}

\begin{definition}\label{DefinitionWienerIndices}
Wiener index: Specific topological descriptor based defined as the sum of the lengths of the shortest paths between all possible vertices in the chemical graph. Mathematically speaking, if we have a molecule with a set of $\{A_i\}_{i=0}^n$ atoms and we denote $d_B(A_i,A_j)$ the bond distance between atoms $A_i$ and $A_j$, we define the Wiener index of this molecule as,
\begin{align}
Ind_{Wiener}=\sum_{i=0}^n\sum_{j>i}^nd_B(A_i,A_j)
\end{align}
\par
For instance, if we take the n-Butane \& Isobutane  chemical graph from the Figure (\ref{figurenButaneIsobutaneGraph}) the Wiener index would be,
\begin{align}
d_B(C_1,C_2)+d_B(C_1,C_3)+d_B(C_1,C_4)\\
+ d_B(C_2,C_3)+d_B(C_2,C_4)+d_B(C_3,C_4)
\end{align}
Though this quantity is computed equally for both, n-Butane \& Isobutane, it results different due to their connectivity. For the n-Butane:
\begin{align}
1+2+3+1+2+1=10
\end{align}
While for the Isobutane:
\begin{align}
1+1+1+2+2+2=9 
\end{align}
\begin{figure}[H]
\centering
\chemfig{C_1-[1]C_2-[-1]C_3-[1]C_4}\hspace{1cm}
\chemfig{C_2-[1]C_1(-[2]C_3)-[-1]C_4}
\caption{n-Butane's \& Isobutane's  chemical graphs.}
\label{figurenButaneIsobutaneGraph}
\end{figure}
\end{definition}

\begin{definition}\label{DefinitionZagrebIndices}
Zagreb index: "For a (molecular) graph, the first Zagreb index $M_1$
 is equal to the sum of squares of the degrees of vertices, and the second Zagreb index $M_2$
 is equal to the sum of the products of the degrees of pairs of adjacent vertices." \cite{ZagrebIndicesArticle}
\end{definition}

\begin{definition}
Walk and Path Counts Descriptors: Kind of descriptor focused on counting specific paths or walks (connected sequences of atoms) in the molecular graph. For instance we can get a Walk and Path Counts Descriptor quantifying the number of Eulerian paths in a molecule's graph. They give insights into the molecule’s connectivity and complexity.
\end{definition}

\begin{enumerate}
    \item Connectivity Indices: These indices quantify the degree of connectivity between atoms based on the topology of the molecule. Popular examples include the Randic index and the Balaban index.
    \item Information Indices: These are based on the concept of information theory, where the structure is interpreted as a distribution of information (or entropy). They measure molecular complexity and diversity.
    \item 2D-Matrix Based Descriptors: These descriptors use matrices (such as adjacency or distance matrices) derived from the 2D molecular graph. They help describe relationships between atoms in a molecule.
    \item 2D Autocorrelations: These descriptors calculate correlations between atomic properties at different distances in the molecular graph. They capture how molecular properties change across the structure.
    \item Burden Eigenvalues: These descriptors are derived from the eigenvalues of matrices related to the structure, such as the Burden matrix, which takes into account atomic properties like electronegativity and partial charges.
    \item P\_VSA-like Descriptors: P\_VSA stands for “Property-weighted Van der Waals Surface Area.” These descriptors quantify the surface area of a molecule associated with specific properties like polarizability or charge.
    \item ETA Indices (Extended Topochemical Atom): ETA indices capture aspects of molecular topology in conjunction with atomic properties. They are often used in the analysis of electronic properties or biological activities.
    \item Edge Adjacency Indices: These descriptors are derived from the adjacency of bonds (edges) in the molecular graph. They measure the proximity of bonds in the structure and can reflect molecular complexity.
    \item Fractional Group Counts: These descriptors count specific chemical groups or fragments within the molecule, providing information about the functional groups present.
    \item Atom-Centered Fragments: These descriptors focus on the environment of individual atoms within a molecule. They describe the types and arrangements of atoms surrounding each atom in the structure.
    \item Atom-Type E-State Indices: The E-State (Electrotopological State) descriptors combine information about the electronic environment and topology of atoms. They reflect the potential reactivity of atoms in the molecule.
    \item Pharmacophore Descriptors: These describe the spatial arrangement of features critical for molecular recognition by biological targets, such as hydrogen bond donors/acceptors, hydrophobic regions, or aromatic rings.
    \item 2D Atom Pairs: These descriptors capture the relationships between pairs of atoms at a specific distance (in terms of bonds) from each other. They describe the distribution of atom pairs within the molecular structure.
    \item Charge Descriptors: These describe the charge distribution within the molecule, including total charge, partial atomic charges, and the dipole moment.
    \item Molecular Properties: These include physical and chemical properties of the molecule such as molecular weight, boiling point, or solubility.
    \item Drug-Like Indices: These descriptors quantify how closely the molecule follows the rules for drug-likeness, such as Lipinski’s Rule of Five, which includes factors like molecular weight, hydrophobicity, and hydrogen bonding.
    \item MDE Descriptors (Molecular Distance Edge descriptors): These describe the distances between atoms in a molecule based on the molecular graph. They are useful for capturing molecular shape and spatial relationships.
    \item Chirality Descriptors: These quantify the chirality (handedness) of molecules. They reflect the 3D arrangement of atoms around chiral centers, which can influence how molecules interact with biological systems.
\end{enumerate}

\begin{definition}
QSAR: "Quantitative Structure–Activity Relationships are the finnal result of the
process that starts with a suitable description of molecular structures and ends with
some inference, hypothesis, and prediction on the behaviour of molecules in environmental, biological, and physico-chemical systems in analysis.\par
QSARs are based on the assumption that the structure of a molecule (for example,
its geometric, steric, and electronic properties) must contain features responsible for
its physical, chemical, and biological properties and on the ability to capture these
features into one or more numerical descriptors. By QSAR models, the biological
activity (or property, reactivity, etc.) of a new designed or untested chemical can be
inferred from the molecular structure of similar compounds whose activities
(properties, reactivities, etc.) have already been assessed."\cite{DescriptorsBookClassification}
\end{definition}
\end{multicols}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% OSERVATIONS %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}
[
\section{Observations}
]
\begin{observation}
Machine Leaning (ML) and Artificial Intelligence (AI) are not the same concept, in fact, a ML  models are a subset of AIs. The key relies in word \emph{Learning}, generally speaking, an AI does not need to actually learn from a set of data. It can be set up within a decision tree such that logically responses with the proper answer following its criteria. \par
However a Machine Leaning Method is a kind of AI that \emph{learns} from data and evolves with the provided data.
\end{observation}
\begin{observation}
Mathematically speaking, Machine Learning methods are no different from an optimisation problem \cite{MathematicsForMachineLearningBook}.\par
Generally speaking, all ML methods seek to find a criterion to determine the quantity of a certain property of some data, which we lack knowledge of and will call the \emph{target}. In order to do so, they rely on a dataset where the sought property is already known and which establishes relationships between this property and other features of the data. Then, based on these relationships and the properties of the \emph{target}, the model searches for the position where the \emph{target} fits within the data and determines the quantity of the property, taking this placement into account within the known data.\par
For instance, we could think of standard calibration with linear regression as an ultra-simplification of a Machine Learning problem. We have a set of data (such as salt concentration in a solution) $\{x_i\}_{i=0}^n$, we also know the quantity of a certain property (such as the solution's conductivity) for each entry $x_j$, denoted as $\{f(x_i)\}_{i=0}^n$. In this example, our ML method assumes that the data and the property are linearly related and that the distance between data and the property is equivalently defined as $d(x_i, x_j) = \sqrt{x_i^2 + x_j^2}$. Hence, based on the assumption of linearity, the best possible relationship is a straight line, and the method looks for the line that minimises the distance between the line and the data.\par
Then, given a \emph{target} (for instance, a certain concentration), about which we initially lack knowledge, the method is capable of quantitatively computing the theoretical property (for instance, its conductivity) by using the fitted line representing the relationship. Consequently, this can be helpful in determining the theoretical concentration of salt needed to achieve a certain conductivity without having actual data for that concentration.\par
The \emph{learning} part (the most important part) comes from the fact that the model (the line) learns from the data. As we train our system (i.e., perform linear regression) with increasingly larger datasets, the accuracy of our model's predictions improves. Thus, we can conclude that the system is \emph{learning} from the data, which qualifies it as a Machine Learning model.\par
\end{observation}
\begin{observation}
Since we are working with molecules, our Machine Learning model will require certain parameters to determine the relationship with the property.\par
In this case, our \emph{property} (i.e., $\{f(x_i)\}_{i=0}^n$) will be the inhibition of a specific protein (COX-2), and more specifically, it will be $IC_{50}$, $IC_{90}$, or $IC_{99}$ (\ref{definitionIC50}).\par
Moreover, our \emph{parameters} (i.e., $\{x_i\}_{i=0}^n$) will be the molecular descriptors, which must be \textbf{carefully chosen}. This problem introduces additional complexities compared to the linear regression case:
\begin{itemize}
    \item We will be working with approximately $10^3$ descriptors, making this a $10^3$-dimensional problem.
    \item We want the system to automatically discard non-relevant data, as some molecules could be exceptions due to external factors.
    \item We do not assume linearity.
    \item Not all descriptors have the same distances or weights, as we will want some of them to be more relevant than others.
    \item Some descriptors will be continuous (for instance, bond distances) while others will remain discrete (for instance, topological indexes) by construction  which implies that some dimensions need to be treated differently to others.
\end{itemize}
Interestingly enough, despite these complexities, in some way, we can say that this project is not entirely different from computing a linear regression...
\end{observation}
\begin{observation}
Taking into account definitions (\ref{DefinitionWienerIndices}) and (\ref{DefinitionZagrebIndices}), we can also define a norm, denoted by $\mathcal{N}(A,B)$, which refers to the norm between molecules $A$ and $B$. For instance, this can be expressed as $\mathcal{N}(A,B) = |Ind_A - Ind_B|$, where $Ind_A$ and $Ind_B$ represent the respective indices (Wiener, Zagreb, etc.) of the molecules\footnote{Actually, any kind of norm would work, as long as it depends on the indices.}. Using this norm, we can generate a metric space that tells us how close two molecules are, based on the similarity of their indices.

In this way, we can apply the concept of “linear regression” and compute the relationship between the indices and the $IC_{50}$. This refers to one dimension, corresponding to a specific topological index. We can then extend this to consider all remaining indices (approximately $10^3$), and find the optimal position in this $10^3$-dimensional space for our resulting molecule.
\end{observation}
\end{multicols}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% REFLECTIONS %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}
[
\section{Reflections}
]
\begin{reflection}
During the first meeting with Dra.González, Dr. Moreno \& Dr. Lluch a certain theme was brought up. "Wouldn't be great to actually have the wave function of the molecules?" This way we could avoid the use of descriptors and QSARs and have more accurate results. \par
Though it was a joke, it might not be a utopia someday. I believe quantum computers will be capable of this task and maybe a hundred years from today, this project could be doable working directly with the waves functions (not analytically obviously). How knows? Time will tell us.
\end{reflection}
\begin{reflection}
Fun fact, \cite{ZagrebIndicesArticle} is a mathematical article, completely apart from the chemical world but somehow we can manage to use it to describe molecules whatsoever. I believe applying knowledge from other sectors is key to evolve and reach even greater results.
\end{reflection}
\end{multicols}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
\bibliography{references} 
%%%%%%%%

\end{document}

### 2024-09-25 Notes/Notes.tex
Notes update

@@
 
+\begin{definition}
+Connectivity Indices: Connectivity Indices are a class of molecular descriptors that quantify the connectivity or bonding patterns between atoms in a molecule based on its topology (i.e., the molecular graph).
+These indices capture the degree to which atoms are connected, considering how atoms are bonded to each other rather than their physical 3D arrangement.
+They are typically derived from graph theory, where atoms are represented as vertices and bonds as edges.\cite{connectivityIndicesArticle}
+\end{definition}
+
+\begin{definition}
+Randic Index: Specific connectivity index defined as the following,
+\begin{align}
+\sum_{\text{all bonds}}\frac{1}{\sqrt{d_id_j}}
+\end{align}
+where $d_i$ and $d_j$ denote the number of bonds of atoms $i$ and $j$ connected by a bond.\cite{RandicIndexArticle}
+\end{definition}
+
+\begin{definition}
+Information Indices: Kind of descriptor based on the information theory, where the molecular structure is represented as a distribution of information (or entropy).
+They measure molecular complexity and diversity.
+\end{definition}
+
+\begin{definition}
+2D-Matrix Based Descriptors: Kind of descriptor based in the matricidal representation of a molecule\cite{DescriptorsBookClassification}. 
+\end{definition}
+
+\begin{definition}
+Adjacency Matrix: Matricidal representation of a molecule.
+If we have $\{x\}_{i=1}^n$ atoms that form our molecule, labeled from 1 to n, the adjacent matrix $A$ will contain as the element $a_{i,j}$ 1 if the atom $i$ and $j$ are connected and 0 otherwise.
+(We can also naturally add the possibilities of $a_{i,j}=2,3$ for double and triple bonds).\par
+For instant in the Figure (\ref{figurenButaneIsobutaneGraph}) the adjacent matrix for the n-Butane is
+\begin{align}
+\text{n-Butane AM}=\begin{pmatrix}
+0 & 1 & 0 & 0 \\
+1 & 0 & 1 & 0 \\
+0 & 1 & 0 & 1 \\
+0 & 0 & 1 & 0 
+\end{pmatrix}
+\end{align}
+Trivially we observe that the main diagonal will always be filled with 0s and the matrices will also be doubly symmetrical (respect both diagonals) due to the bounds transitivity and reflectivities properties.
+\end{definition}
+
 \begin{enumerate}
-    \item Connectivity Indices: These indices quantify the degree of connectivity between atoms based on the topology of the molecule. Popular examples include the Randic index and the Balaban index.
-    \item Information Indices: These are based on the concept of information theory, where the structure is interpreted as a distribution of information (or entropy).
-They measure molecular complexity and diversity.
-    \item 2D-Matrix Based Descriptors: These descriptors use matrices (such as adjacency or distance matrices) derived from the 2D molecular graph.
-They help describe relationships between atoms in a molecule.
     \item 2D Autocorrelations: These descriptors calculate correlations between atomic properties at different distances in the molecular graph.

### 2024-09-25 Notes/Notes.tex
ACS style

@@
 \usepackage[table,xcdraw]{xcolor}
-\usepackage{natbib}
 \usepackage{enumitem}
@@
 \useunder{\uline}{\ul}{}
+
+\usepackage{achemso}
 
@@
 \begin{definition}
-Adjacency Matrix: Matricidal representation of a molecule.
-If we have $\{x\}_{i=1}^n$ atoms that form our molecule, labeled from 1 to n, the adjacent matrix $A$ will contain as the element $a_{i,j}$ 1 if the atom $i$ and $j$ are connected and 0 otherwise.
+Adjacency Matrix: Specific 2D-Matrix Based Descriptor based on the matricidal representation of a molecule.
+If we have $\{x\}_{i=1}^n$ atoms that form our molecule, labeled from 1 to n, the adjacent matrix $A$ will contain as the element $a_{i,j}$ the number 1 if the atom $i$ and $j$ are connected and 0 otherwise.
 (We can also naturally add the possibilities of $a_{i,j}=2,3$ for double and triple bonds).\par
@@
 Trivially we observe that the main diagonal will always be filled with 0s and the matrices will also be doubly symmetrical (respect both diagonals) due to the bounds transitivity and reflectivities properties.
+\end{definition}
+
+\begin{definition}
+Distance Matrix: Specific 2D-Matrix Based Descriptor based on the computation of the shortest pathways between atoms.
+If we have $\{x\}_{i=1}^n$ atoms that form our molecule, labeled from 1 to n, the adjacent matrix $A$ will contain as the element $a_{i,j}$ the shortest bond distance between atom $i$ and atom $j$.\par
+For instant in the Figure (\ref{figurenButaneIsobutaneGraph}) the distance matrix for the n-Butane is
+\begin{align}
+\text{n-Butane DM}=\begin{pmatrix}
+0 & 1 & 2 & 3 \\
+1 & 0 & 1 & 2 \\
+2 & 1 & 0 & 1 \\
+3 & 2 & 1 & 0 
+\end{pmatrix}
+\end{align}
 \end{definition}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{achemso}
 \bibliography{references} 

### 2024-09-25 Notes/Notes.tex
New types of descriptors

@@
 
-\begin{definition}
+\begin{definition}\label{AdjacencyMatrixDefinition}
 Adjacency Matrix: Specific 2D-Matrix Based Descriptor based on the matricidal representation of a molecule.
@@
 
+\begin{definition}
+2D Autocorrelations: a type of molecular descriptor that quantifies the correlations between properties of atoms within a molecule based on their positions relative to one another in the molecular structure.
+These descriptors analyse how specific atomic properties are distributed across the molecule, capturing the spatial relationships of these properties.
+\par
+For a given property and distance $d$, the autocorrelation is calculated by summing the products of the property values for all pairs of atoms that are separated by that distance.
+Mathematically, the autocorrelation  $A_d(P)$  at distance  $d$  for a property $P$  is given by,
+\begin{align}
+A_d(P)=\sum_{d(i,j)=d}P(i)P(j)
+\end{align}
+\end{definition}
+\begin{definition}
+Burden Eigenvalues: Kind of descriptor extracted from the Burden Matrix of a molecule\cite{BurdenIndicesArticle}, which is a modification of the adjacency matrix from the definition (\ref{AdjacencyMatrixDefinition}).
+\end{definition}
+
+\begin{definition}
+P\_VSA-like Descriptors: (Property-weighted Van der Waals Surface Area descriptors) descriptors deviated from the computation of the Van der Waals Surface of a molecule.
+For instance, we could talk about polarity indices, high/low electron density regions...
+\end{definition}
+
+\begin{definition}
+ETA Indices: (Extended Topochemical Atom) kind of indices that capture aspects of molecular topology in conjunction with atomic properties.
+They are often used in the analysis of electronic properties or biological activities.
+\end{definition}
+
 \begin{enumerate}
-    \item 2D Autocorrelations: These descriptors calculate correlations between atomic properties at different distances in the molecular graph.
-They capture how molecular properties change across the structure.
-    \item Burden Eigenvalues: These descriptors are derived from the eigenvalues of matrices related to the structure, such as the Burden matrix, which takes into account atomic properties like electronegativity and partial charges.
-    \item P\_VSA-like Descriptors: P\_VSA stands for “Property-weighted Van der Waals Surface Area.” These descriptors quantify the surface area of a molecule associated with specific properties like polarizability or charge.
-    \item ETA Indices (Extended Topochemical Atom): ETA indices capture aspects of molecular topology in conjunction with atomic properties.
-They are often used in the analysis of electronic properties or biological activities.
     \item Edge Adjacency Indices: These descriptors are derived from the adjacency of bonds (edges) in the molecular graph.

### 2024-09-28 Notes/Notes.tex
End of descriptors definitions

@@
 \newtheorem{reflection}{Reflection}
+\newtheorem{book}{Book}
 
@@
 ETA Indices: (Extended Topochemical Atom) kind of indices that capture aspects of molecular topology in conjunction with atomic properties.
-They are often used in the analysis of electronic properties or biological activities.
+They are often used in the analysis of electronic properties or biological activities.\cite{DescriptorsBook}
 \end{definition}
 
-\begin{enumerate}
-    \item Edge Adjacency Indices: These descriptors are derived from the adjacency of bonds (edges) in the molecular graph.
-They measure the proximity of bonds in the structure and can reflect molecular complexity.
-    \item Fractional Group Counts: These descriptors count specific chemical groups or fragments within the molecule, providing information about the functional groups present.
-    \item Atom-Centered Fragments: These descriptors focus on the environment of individual atoms within a molecule.
-They describe the types and arrangements of atoms surrounding each atom in the structure.
-    \item Atom-Type E-State Indices: The E-State (Electrotopological State) descriptors combine information about the electronic environment and topology of atoms.
-They reflect the potential reactivity of atoms in the molecule.
-    \item Pharmacophore Descriptors: These describe the spatial arrangement of features critical for molecular recognition by biological targets, such as hydrogen bond donors/acceptors, hydrophobic regions, or aromatic rings.
-    \item 2D Atom Pairs: These descriptors capture the relationships between pairs of atoms at a specific distance (in terms of bonds) from each other.
-They describe the distribution of atom pairs within the molecular structure.
-    \item Charge Descriptors: These describe the charge distribution within the molecule, including total charge, partial atomic charges, and the dipole moment.
-    \item Molecular Properties: These include physical and chemical properties of the molecule such as molecular weight, boiling point, or solubility.
-    \item Drug-Like Indices: These descriptors quantify how closely the molecule follows the rules for drug-likeness, such as Lipinski’s Rule of Five, which includes factors like molecular weight, hydrophobicity, and hydrogen bonding.
-    \item MDE Descriptors (Molecular Distance Edge descriptors): These describe the distances between atoms in a molecule based on the molecular graph.
+\begin{definition}
+Edge Adjacency Indices: Kind of descriptor that relies on the chemical graph theory and is related to the number of bonds that each atom generates.
+This descriptors are tightly related to the molecule's complexity.\cite{DescriptorsBook}
+\end{definition}
+
+\begin{definition}
+Fractional Group Counts (FGC): kind of molecular descriptor related to the chemical functional groups.
+For instance, in the case of cyclopentanone Figure (\ref{figurenCiclopentanone}), the Ketones Group Counts  is $\frac{1}{6}$, since we have 1 ketone for 6 atoms(we do not typically compute the hydrogen atoms).\cite{DescriptorsBook}
+\begin{figure}[H]
+\centering
+\chemfig{O=*5(-----)}\hspace{1cm}
+\caption{Cycloentanone's chemical graph.}
+\label{figurenCiclopentanone}
+\end{figure}
+\end{definition}
+
+\begin{definition}
+Atom-Centered Fragments (ACF): Kind of molecular descriptor concerned about atoms separately.
+For a given molecule conformed by $n$ atoms, and a specific Atom-Centered Fragment descriptor, we can compute $n$ descriptors of this kind based one per each atom separately.
+Each descriptor describes an atom itself, its surroundings and its bounding types.\cite{DescriptorsBook}
+\end{definition}
+
+\begin{definition}
+Atom-Type E-State Indices: Kind of molecular descriptor that describes the electronic state of an individual atom.
+Some Atom-Type E-State Indices describe the hybridisation state (e.g., $sp^2$, $sp^3$), the local bonding environment (e.g., single, double, or aromatic bonds), the presence of electronegative atoms nearby or the topological distance to other atoms in the molecule.
+For a given atom, a atom-type e-etate Indiex is the combination of 2 terms.
+The intrinsic term that depends on the atom hybridization and the perturbation term which is adjusted depending in the atom's surroundings.\cite{DescriptorsBook}
+\end{definition}
+
+\begin{definition}
+Pharmacophore Descriptors: Kind of descriptor refered to the functionals groups of a given molecule and its molecular features.
+they describe properties such as hydrogen donation (-OH), hydrogen acceptation (C=O), Positive or negative ionizable groups (-COO$^-$)...
+This kind of descriptor does not worry about the molecular structure rather than the molecular properties as a hole.\cite{PharmacophoreDescriptorsBook}
+\end{definition}
+
+\begin{definition}
+2D Atom Pairs: Kind of descriptor that focuses on pairs of atoms and captures information about the types of atoms involved, as well as the distance between them in a two-dimensional representation of the molecular structure.
+\end{definition}
+
+\begin{definition}
+Charge descriptors: Kind of descriptor that describes a molecular charge, as a complete element as well as the composure of several elements.
+One of the key features of this kind of descriptors is their high dependency on dipole moment as well as the electronegativity of the atoms that it describes.
+\end{definition}
+
+\begin{definition}
+Molecular Properties: The most intuitive kind of descriptor. These descriptors are the \emph{traditional features} of a substance such as it molecular weight, boiling point, solubility, density...
+\end{definition}
+
+\begin{definition}
+Drug-Like Indices: These descriptors quantify how closely the molecule follows the rules for drug-likeness, such as Lipinski’s Rule of Five, which includes factors like molecular weight, hydrophobicity, and hydrogen bonding.
+\end{definition}
+
+\begin{definition}
+MDE Descriptors (Molecular Distance Edge descriptors): These describe the distances between atoms in a molecule based on the molecular graph.
 They are useful for capturing molecular shape and spatial relationships.
-    \item Chirality Descriptors: These quantify the chirality (handedness) of molecules.
+\end{definition}
+
+\begin{definition}
+Chirality Descriptors: These quantify the chirality (handedness) of molecules.
 They reflect the 3D arrangement of atoms around chiral centers, which can influence how molecules interact with biological systems.
-\end{enumerate}
+\end{definition}
 
@@
 \end{definition}
+
+\begin{definition}
+Machine Learning Model: For a given problem, Machine Learning Model is the procedure to resolve the problem in a Machine Learning like format. 
+\end{definition}
+
+\begin{definition}
+The efficiency of a Machine Learning Model relies in the following quantities:
+\begin{itemize}
+\item True Positives (TP): number of true positives results.
+\item False Positives (FP): number of false positives results.
+\item True Negatives (TN): number of true negatives results.
+\item Fales Negatives (FN): number of false negatives results.
+\end{itemize}
+\end{definition}
+
+\begin{definition}
+True Positive Rate: quantity related to a Machine Learning Model's sensitivity defined as:
+\begin{align}
+\frac{TP}{TP+FN}
+\end{align}
+\end{definition}
+
+\begin{definition}
+True Negative Rate: quantity related to a Machine Learning Model's specificity defined as:
+\begin{align}
+\frac{TN}{TN+FN}
+\end{align}
+\end{definition}
+
+\begin{definition}
+Classification Accuracy: quantity related to a Machine Learning Model's efectiveness defined as:
+\begin{align}
+\frac{TP+TN}{TP+FP+TN+FN}
+\end{align}
+\end{definition}
+
+\begin{definition}
+Matthews Correlation Coefficient: quantity related to a Machine Learning Model's prediction capacity defined as:
+{\scriptsize
+\begin{align}
+\frac{(TP\times TN)-(FP\times FN)}{\sqrt{(TP+FP)\times(TP+FN)\times(TN+FP)\times(TN+FN)}}
+\end{align}
+}
+A Matthews Correlation Coefficient equal to 1 stands for a perfect prediction a Matthews Correlation Coefficient equal to 0 indicates that the classifier’s predictions are no better than random guessing, and a Matthews Correlation Coefficient equal to -1 stand for a total disagreement between predictions and actual outcomes.
+\end{definition}
+
 \end{multicols}
-\newpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\newpage
 \begin{multicols}{2}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%% CONTACTS %%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Contacts}
+IIIA (Institut d'Investigació en Inteligència Artificial): 
+\begin{itemize}
+\item General consultes \href{tel:93 580 9570}{+34 93 580 9570}
+\item \href{https://www.iiia.csic.es/en-us/people/person/?person_id=39}{Pablo Noriega}: \href{mailto:pablo@iiia.csic.es}{pablo@iiia.csic.es}
+\end{itemize}
+Chemistry department - UAB
+\begin{itemize}
+\item General consultes \href{tel:93 580 9570}{+34 93 580 9570}
+\item \href{https://www.iiia.csic.es/en-us/people/person/?person_id=39}{Pablo Noriega}: \href{mailto:pablo@iiia.csic.es}{pablo@iiia.csic.es}
+\end{itemize}
+
+\section{Physical books in the library}
+\begin{book}
+Molecular descriptors for chemoinformatics. Todeschini, Roberto.; Consonni, Viviana. 2009. Volum: 2.
+
+Localization: Ciència i Tecnologia.
+
+Signatura: 54:68 Tod.
+
+Codi de Barres: 1501208901
+\end{book}
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
@@
 
-\bibliographystyle{achemso}
+% \bibliographystyle{achemso}
 \bibliography{references} 

### 2024-10-02 Notes/Notes.tex
Contacts update
Contacts.md creation
Creation of the ChEMBL_ExtractorData

@@
 
+%%%%%%%%%%%%%%% CODELISTINGS %%%%%%%%%%%%%%%%
+\usepackage{listings}
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=t,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \usepackage{achemso}
@@
 \newtheorem{reflection}{Reflection}
+\newtheorem{PyPackage}{Package}
 \newtheorem{book}{Book}
@@
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Packages}
+
+\begin{PyPackage}
+"Requests allows you to send HTTP/1.1 requests extremely easily.
+There’s no need to manually add query strings to your URLs, or to form-encode your POST data.
+Keep-alive and HTTP connection pooling are 100\% automatic, thanks to urllib3."
+\cite{PythonPackageRequests}. We will use this package to create requests to the ChEMBL database.
+\end{PyPackage}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% CONTACTS %%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% BOOKS %%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Contacts}
-IIIA (Institut d'Investigació en Inteligència Artificial): 
-\begin{itemize}
-\item General consultes \href{tel:93 580 9570}{+34 93 580 9570}
-\item \href{https://www.iiia.csic.es/en-us/people/person/?person_id=39}{Pablo Noriega}: \href{mailto:pablo@iiia.csic.es}{pablo@iiia.csic.es}
-\end{itemize}
-Chemistry department - UAB
-\begin{itemize}
-\item General consultes \href{tel:93 580 9570}{+34 93 580 9570}
-\item \href{https://www.iiia.csic.es/en-us/people/person/?person_id=39}{Pablo Noriega}: \href{mailto:pablo@iiia.csic.es}{pablo@iiia.csic.es}
-\end{itemize}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% VARIOUS %%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Various}
+
+\begin{lstlisting}[language=C, caption=Example of a JSON file.]
+{
+  "page_meta": {
+    "limit": 1000,
+    "offset": 0,
+    "total_count": 1500,
+    "next": "/chembl/api/data/activity.json?limit=1000&offset=1000&target_chembl_id=CHEMBL372&standard_type=IC50",
+    "previous": null
+  },
+  "activities": [
+    {
+      "activity_id": 123456789,
+      "assay_chembl_id": "CHEMBL123456",
+      "molecule_chembl_id": "CHEMBL25",
+      "canonical_smiles": "CCOCCO",
+      "standard_value": "50",
+      "standard_units": "nM",
+      "standard_type": "IC50",
+      "target_chembl_id": "CHEMBL372",
+      "assay_type": "B",
+      "relation": "=",
+      "document_chembl_id": "CHEMBL12345"
+    },
+    {
+      "activity_id": 987654321,
+      "assay_chembl_id": "CHEMBL654321",
+      "molecule_chembl_id": "CHEMBL1095",
+      "canonical_smiles": "CCCN(CC)CC",
+      "standard_value": "25",
+      "standard_units": "nM",
+      "standard_type": "IC50",
+      "target_chembl_id": "CHEMBL372",
+      "assay_type": "B",
+      "relation": "<",
+      "document_chembl_id": "CHEMBL54321"
+    }
+    // More activity entries...
+  ]
+}
+\end{lstlisting}
+
 \newpage

### 2024-10-02 scripts/ChEMBLDataExtractor.py
Creating the READMEScripts.md file

@@ -1,0 +1,71 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     02/10/2024                                                                                #
+#  Purpose:  Import molecule's data with a known IC50 activity respect a certain protein (i.e, COX-2)  #
+#                                                                                                      #
+########################################################################################################
+
+import requests
+import pandas as pd
+
+
+dataBaseBaseURL  = "https://www.ebi.ac.uk" # Defining the ChEMBL API web
+targetIDChEMBL   = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
+targetProperty   = "IC50" # Defining our target poperty
+requestDataLimit = "1000" # The ChEMBL database has a limit of 1000 requests at the same time.
+# However, we will send multimples request to extract all the data aviable.
+
+# Setting up the query URL with the previous data
+queryURL         = f"{dataBaseBaseURL}/chembl/api/data/activity.json?target_chembl_id={targetIDChEMBL}&standard_type={targetProperty}&limit={requestDataLimit}"
+
+# Initialize a list to store all activities
+allActivities   = []
+
+# Announcing the beinning of the requesting process
+print(f"Requesting data to the ChEMBL's database with the url:{queryURL}\n")
+
+while queryURL: # Using the loop to send multiple request 
+    response = requests.get(queryURL) # Getting the response for each request
+    if response.status_code == 200: # Checking if the request was successful
+        # Parsing the JSON response and selecting the activities (rellevant data) 
+        data = response.json()
+        activities = data['activities']
+        allActivities.extend(activities )# Appending the activities to the list
+        nextURL = data.get('page_meta', {}).get('next', None) # Gettin the URL for the next page, if it is available
+        if nextURL and nextURL.startswith('/'):# If the next URL is relative, prepend the base URL
+            queryURL = dataBaseBaseURL + nextURL
+        else:
+            queryURL = nextURL
+        print(f"Fetched {len(allActivities)} total activities so far...") # Indicating the progress
+    else:
[…]

### 2024-10-02 scripts/ChEMBL_Extractor.py
Removing duplicated files

@@ -1,71 +1,0 @@
-########################################################################################################
-#                                                                                                      #
-#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
-#  Author:   Sergio Castañeiras Morales                                                                #
-#  Date:     02/10/2024                                                                                #
-#  Purpose:  Import molecule's data with a known IC50 activity respect a certain protein (i.e, COX-2)  #
-#                                                                                                      #
-########################################################################################################
-
-import requests
-import pandas as pd
-
-
-dataBaseBaseURL  = "https://www.ebi.ac.uk" # Defining the ChEMBL API web
-targetIDChEMBL   = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
-targetProperty   = "IC50" # Defining our target poperty
-requestDataLimit = "1000" # The ChEMBL database has a limit of 1000 requests at the same time.
-# However, we will send multimples request to extract all the data aviable.
-
-# Setting up the query URL with the previous data
-queryURL         = f"{dataBaseBaseURL}/chembl/api/data/activity.json?target_chembl_id={targetIDChEMBL}&standard_type={targetProperty}&limit={requestDataLimit}"
-
-# Initialize a list to store all activities
-allActivities   = []
-
-# Announcing the beinning of the requesting process
-print(f"Requesting data to the ChEMBL's database with the url:{queryURL}\n")
-
-while queryURL: # Using the loop to send multiple request 
-    response = requests.get(queryURL) # Getting the response for each request
-    if response.status_code == 200: # Checking if the request was successful
-        # Parsing the JSON response and selecting the activities (rellevant data) 
-        data = response.json()
-        activities = data['activities']
-        allActivities.extend(activities )# Appending the activities to the list
-        nextURL = data.get('page_meta', {}).get('next', None) # Gettin the URL for the next page, if it is available
-        if nextURL and nextURL.startswith('/'):# If the next URL is relative, prepend the base URL
-            queryURL = dataBaseBaseURL + nextURL
-        else:
-            queryURL = nextURL
-        print(f"Fetched {len(allActivities)} total activities so far...") # Indicating the progress
-    else:
[…]

### 2024-10-02 Notes/Notes.tex
Packages addition to notes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{multicols}{2}
+[
 \section{Packages}
-
+]
 \begin{PyPackage}
@@
 \end{PyPackage}
+
+\begin{PyPackage}
+"Pandas is a Python package that provides fast, flexible, and expressive data structures designed to make working with "relational" or "labeled" data both easy and intuitive.
+It aims to be the fundamental high-level building block for doing practical, real world data analysis in Python.
+Additionally, it has the broader goal of becoming the most powerful and flexible open source data analysis / manipulation tool available in any language.
+It is already well on its way towards this goal"\cite{PythonPackagePandas}.
+We will use this package to interact with the data using a built-in Pandas class called \emph{Data Frames}.
+\end{PyPackage}
+\end{multicols}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\newpage
 \section{Various}

### 2024-10-05 Scripts/ChEMBLDataExtractor.py
Adding a filter to the data

@@ -46,26 +46,33 @@ while queryURL: # Using the loop to send multiple request
 # Printing the amount of data
 print(f"\nEnd of the requesting process, we have downloaded a total of {len(allActivities)} molecule's data.")
 
-# We want to save the data in a proper format
+# We want to save the data in a proper format, a Data Frame
 requestedData = pd.DataFrame(allActivities) # Converting all the extracted data into a DataFrame
 # Listing all the numerical variables
 numericalVariables = ['activity_id','document_year','pchembl_value','record_id','src_id','standard_flag','standard_value','target_tax_id','value']
 for iVariable in numericalVariables: # Converting all the numerical values to actual numbers. (Otherways they would be strings)
     requestedData[iVariable] = pd.to_numeric(requestedData[iVariable], errors='coerce')
 
+# Removing entries with the same canonical smile
+requestedData = requestedData.drop_duplicates(subset=['canonical_smiles'],keep='first')
+# Removing entries with no value in the targetProperty
+requestedData = requestedData.dropna(subset=['standard_value'])
+requestedData = requestedData.reset_index() # Reseting the index of the dataframe...
+print(f"Deleting molecules with the same canonical smile and no targetProperty entries. {len(requestedData)} molecule's data remaining.")
+
 # Finding the minimum and maximum 'standard_value' indices
-minimumTargetProperty = requestedData['standard_value'].idxmin()
-maximumTargetProperty = requestedData['standard_value'].idxmax()
+minimumTargetPropertyID = requestedData['standard_value'].idxmin()
+maximumTargetPropertyID = requestedData['standard_value'].idxmax()
 
 # Printing the minimum and maximum 'standard_value' and their corresponding 'standard_units'
-print(f"The minimum {targetProperty} found value is {requestedData.loc[minimumTargetProperty, 'standard_value']} {requestedData.loc[minimumTargetProperty, 'standard_units']}")
-print(f"The maximum {targetProperty} found value is {requestedData.loc[maximumTargetProperty, 'standard_value']} {requestedData.loc[maximumTargetProperty, 'standard_units']}")
[…]

### 2024-10-05 Scripts/DataFilterAndPlots.py

@@ -1,0 +1,68 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     05/10/2024                                                                                #
+#  Purpose:  Analyse the extracted data by ChEMBLDataExtractor.py in order to filter out irrellevant   #
+#            entries                                                                                   #
+#                                                                                                      #
+########################################################################################################
+
+import pandas as pd # Importing pandas in order to use DataFrames
+import matplotlib.pyplot as plt # Importing matplotlib for perfoming plots
+
+targetIDChEMBL  	 = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
+targetProperty  	 = "IC50" # Defining our target poperty
+requestDataLimit	 = "1000" # The ChEMBL database has a limit of 1000 requests at the same time.
+dataFileName    	 = f"ChEMBL_ExtractorData{targetIDChEMBL},{targetProperty},{requestDataLimit}" # Defining the name of the data file 
+dataFilePath     	 = "../Data/" # Defining the path where the data file is stored
+plotingPath			 = "../Plots/" # Defining the path where the plots files are stored
+lowerTargetProperty  = -1   # Defining the lowest 'standard_value' (= targetProperty) we want to take into acount
+higherTargetProperty = 200  # Defining the highest 'standard_value' (= targetProperty) we want to take into acount
+
+dataImported = pd.read_feather(dataFilePath+dataFileName+".feather") # Creating the datafame, using feather files for faster read/write performance
+
+# Anouncing the previous data entries 
+print(f'Number of previous entries:         {len(dataImported)}')
+
+# Finding the minimum and maximum 'standard_value' (= targetProperty) indices for the dataImported
+minimumImportedPropertyID = dataImported['standard_value'].idxmin()
+maximumImportedPropertyID = dataImported['standard_value'].idxmax()
+
+# Printing the values
[…]

### 2024-10-05 Notes/Notes.tex
Adding a filter to the data

@@
 \end{observation}
+
+\begin{observation}
+We have extracted all the aviable data from the \emph{ChEMBL} database with a known $IC_{50}$ value for the COX-2.
+After deleting  entries with the same canonical smile we remain with 4827 entries.
+We filter, keeping just those with a $IC_{50}\in [-1,200]$\footnote{Note that the lower constrain won't be ever surpassed by the $IC_{50}$ defintion \ref{definitionIC50}.
+This is equivalent to avoid constraining the data.}.
+Then we obtain a remaining set of 1518 entries represented in the Figure (\ref{figDataRepresentationFiltering}).
+\begin{figure}[H]
+\centering
+\includegraphics[width = 0.5\textwidth]{../Plots/DataRepresentationIC50min_-1max_200.pdf}
+\caption{Data representation after the filtering.}
+\label{figDataRepresentationFiltering}
+\end{figure}
+\end{observation}
 \end{multicols}

### 2024-10-06 Scripts/DataFilterAndPlots.py
Adding the Gap Feature in DataFilterAndPlots.py

@@ -15,12 +15,44 @@ targetIDChEMBL  	 = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target.
 targetProperty  	 = "IC50" # Defining our target poperty
 requestDataLimit	 = "1000" # The ChEMBL database has a limit of 1000 requests at the same time.
 dataFileName    	 = f"ChEMBL_ExtractorData{targetIDChEMBL},{targetProperty},{requestDataLimit}" # Defining the name of the data file 
-dataFilePath     	 = "../Data/" # Defining the path where the data file is stored
+dataFilePath     	 = "../Data/"  # Defining the path where the data file is stored
 plotingPath			 = "../Plots/" # Defining the path where the plots files are stored
 lowerTargetProperty  = -1   # Defining the lowest 'standard_value' (= targetProperty) we want to take into acount
 higherTargetProperty = 200  # Defining the highest 'standard_value' (= targetProperty) we want to take into acount
+percentageEresed	 = 0.2	# Defining the percentage of the data we want to erase (number between 0 and 1)
+unwantedVariables	 = ['index','action_type', 'activity_comment', 'activity_properties', 'assay_type', 'assay_variant_accession', 
+						'assay_variant_mutation', 'bao_endpoint', 'bao_format', 'bao_label', 'ligand_efficiency', 'potential_duplicate',
+						'qudt_units','standard_upper_value','text_value','toid','upper_value']
+
+# Making sure that the given value for 'percentageEresed' is a number between 0 and 1
+if percentageEresed<0 or percentageEresed>1:
+	raise ValueError("The 'percentageEresed variable' is not properly defined")
+
+# Defining two functions used to find the splits values
+def splitDataFrameIteration (dataFrame,column,splitValue):
+	upperCounter = 0; underCounter = 0
+	for iData in dataFrame[column]:
+		if iData >= splitValue : upperCounter+=1
+		if iData <= splitValue : underCounter+=1
+	return underCounter,upperCounter
+
+def findSplitDataFrame (dataFrame,column,percentageEresed):
+	iSplitValueUnder = 0
+	while True:
[…]

### 2024-10-07 Scripts/ChEMBLDataExtractor.py
Creating the Traing/Test split

@@ -57,7 +57,7 @@ for iVariable in numericalVariables: # Converting all the numerical values to ac
 requestedData = requestedData.drop_duplicates(subset=['canonical_smiles'],keep='first')
 # Removing entries with no value in the targetProperty
 requestedData = requestedData.dropna(subset=['standard_value'])
-requestedData = requestedData.reset_index() # Reseting the index of the dataframe...
+requestedData = requestedData.reset_index(inplace=True) # Reseting the index of the dataframe...
 print(f"Deleting molecules with the same canonical smile and no targetProperty entries. {len(requestedData)} molecule's data remaining.")
 
 # Finding the minimum and maximum 'standard_value' indices

### 2024-10-07 Scripts/DataFilterAndPlots.py

@@ -10,6 +10,8 @@
 
 import pandas as pd # Importing pandas in order to use DataFrames
 import matplotlib.pyplot as plt # Importing matplotlib for perfoming plots
+from sklearn.model_selection import train_test_split # Importing the funtion "train_test_split" for spliting our data in two 
+# sets. The training set and the testing set.
 
 targetIDChEMBL  	 = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
 targetProperty  	 = "IC50" # Defining our target poperty
@@ -20,6 +22,8 @@ plotingPath			 = "../Plots/" # Defining the path where the plots files are store
 lowerTargetProperty  = -1   # Defining the lowest 'standard_value' (= targetProperty) we want to take into acount
 higherTargetProperty = 200  # Defining the highest 'standard_value' (= targetProperty) we want to take into acount
 percentageEresed	 = 0.2	# Defining the percentage of the data we want to erase (number between 0 and 1)
+testSizeProportion	 = 0.2  # Defining the percentage of the data we want to keep for our training set (number between 0 and 1)
+randomSplitState     = 42	# Defining the randomness for the Train/test splitting (Typically will be around 42)
 unwantedVariables	 = ['index','action_type', 'activity_comment', 'activity_properties', 'assay_type', 'assay_variant_accession', 
 						'assay_variant_mutation', 'bao_endpoint', 'bao_format', 'bao_label', 'ligand_efficiency', 'potential_duplicate',
 						'qudt_units','standard_upper_value','text_value','toid','upper_value']
@@ -103,8 +107,7 @@ maximumGapPropertyID = dataWithGapUpper['standard_value'].idxmin()
 # Anouncing the data gap
 print(f'Minimum {targetProperty} gap:                   {float(dataWithGapUnder.loc[minimumGapPropertyID,'standard_value'])} {dataWithGapUnder.loc[minimumGapPropertyID, 'standard_units']}')
 print(f'Maximum {targetProperty} gap:                   {float(dataWithGapUpper.loc[maximumGapPropertyID,'standard_value'])} {dataWithGapUpper.loc[maximumGapPropertyID, 'standard_units']}')
-dataWithGapAll.reset_index()
-
[…]

### 2024-10-09 Notes/Notes.tex
Adding the Gap Feature in DataFilterAndPlots.py
COX-2 Notes

@@
 \usepackage{wrapfig}
+\usepackage{url}
 \usepackage[normalem]{ulem}
@@
 
+\begin{definition}
+Cyclooxygenase-2: (COX-2), also known as prostaglandin-endoperoxide synthase 2 is "An enzyme that speeds up the formation of substances that cause inflammation and pain.
+It may also cause tumor cells to grow.
+Some tumors have high levels of COX-2 and blocking its activity may reduce tumor growth.
+Also called cyclooxygenase-2 and prostaglandin-endoperoxide synthase 2."\cite{DefinitionCOX2CancerDictionary} This enzyme will be our main object of study.
+It is encoded by the PTGS2 gene and its main functionality is converting arachidonic acid to prostaglandin \chemfig{H_2} Figure (\ref{Cox2MainReaction}).
+
+\end{definition}
 \end{multicols}
+\begin{figure}[H]
+\centering
+\schemestart
+\scalebox{0.7}{
+\chemname{\chemfig[angle increment=30, scale=0.1]{
+HO-[1](=[3]O)-[-1]-[1]-[-1]-[1]=[-1]-[-3]-[-1]=[-3]-[7]-[-3]=[7]-[-7]-[7]=[-7]-[3]-[-7]-[7]-[-7]-[7]
+}}{Arachidonic acid}
+}
+\arrow{->}
+\scalebox{0.7}{
+\chemname{\chemfig[angle increment=30]{OH-[5](=[3]O)-[7]-[-3]-[7]-[-3]=[7]-[5]>:[7]*6(-(<[-3.8])-O-O-(<[3.8]C)-(<[-1]=[1]-[-1](<:[-3]OH)-[1]-[-1]-[1]-[-1]-[1])-)
+}}{Prostaglandin \chemfig{H_2}}
+}
+\schemestop
+\caption{Reaction catalysed by the COX-2 between arachidonic acid to prostaglandin H$_2$.}
+\label{Cox2MainReaction}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width = \textwidth]{GeneralSources/COX-2Image.png}
+\caption{Crystal structure of uninhibited cyclooxygenase-2 Molecular graphics images were produced using the UCSF Chimera package\cite{Cox2WikiImage}.}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width = 0.5\textwidth]{../Plots/DataRepresentationIC50min_-1max_200.pdf}
+\includegraphics[width = 0.5\textwidth]{../Plots/DataGapRepresentationIC50percentageEresed20.0Gap_min_17Gap_max_47.pdf}
 \caption{Data representation after the filtering.}

### 2024-10-12 Notes/Notes.tex
Adding COX-2 inhibitors info to the notes

@@
 \end{figure}
+
+\begin{multicols}{2}
+\begin{definition}
+Non-steroidal anti-inflammatory drug: (NSAID) kind of drug commonly used for therapeutic purposes that focuses in pain, inflammation and fever reduction and blood clots prevention.
+They are characterised by inhibiting the activity of enzymes called cyclooxygenase (COX).
+This drug type is known to produce side-effects such as:
+\begin{itemize}
+\item NSAIDs block COX-1, which helps protect the stomach lining. Long-term use can lead to ulcers and gastrointestinal bleeding. 
+\item Stomach pain, indigestion, heartburn.
+\item Particularly \textbf{COX-2 inhibitors}, may increase the risk of \textbf{heart attack}, stroke, and blood clots.
+\item Increased Blood Pressure.
+\item Allergic Reactions.
+\item Liver Toxicity.
+\item Fluid Retention and Edema.
+\end{itemize}
+Some well-known NSAIDs are Ibuprofen, Aspirin and Celecoxib where the last one is specific a specific inhibitor for the COX-2.\cite{Cox2InhibitorsReview}\par
+In the Figure (\ref{Cox2BondingSiteFigureRef}) we can observe the binding site of COX-2 for the celecoxib.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{GeneralSources/COXII-receptor.png}
+\caption{COX-2 receptor site and its amino acid profile with celecoxib in the binding site.\cite{Cox2BondingSiteFigure}}
+\label{Cox2BondingSiteFigureRef}
+\end{figure}
+\end{definition}
+
+\begin{definition}
+Celecoxib: \footnote{UPAC name: 4-[5-(4-Methylphenyl)-3-(trifluoromethyl)pyrazol-1-yl]benzenesulfonamide} drug known to be a selective COX-2 inhibitor (currently is not \emph{highly selective} respect to newer drugs), see Figure (\ref{CelecoxibFigure}).
+We will use the chemical descriptors of this molecule to compute its theoretical $IC_{50}$(one that our Machine Learning Model predicts) to have some sore of feed back of the ML reliability.
+\end{definition}
+
+\begin{definition}
+Rofecoxib: \footnote{UPAC name: 4-(4-methylsulfonylphenyl)-3-phenyl-5H-furan-2-one} drug known to be a selective COX-2 inhibitor, see Figure (\ref{RofecoxibFigure}).
+We will use the chemical descriptors of this molecule to compute its theoretical $IC_{50}$(one that our Machine Learning Model predicts) to have some sore of feed back of the ML reliability.
+\end{definition}
+
+\begin{definition}
+Ibuprofen: \footnote{UPAC name: (RS)-2-(4-(2-Methylpropyl)phenyl)propanoic acid} drug known to be a selective COX-1 and COX-2 inhibitor, see Figure (\ref{IbuprofenFigure}).
+We will use the chemical descriptors of this molecule to compute its theoretical $IC_{50}$(one that our Machine Learning Model predicts) to have some sore of feed back of the ML reliability.
+\end{definition}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+H_2N-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
+}}
+\caption{Chemical graph of Celecoxib.}
+\label{CelecoxibFigure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]*5(--O-(=[2.25]O)-(-[4.5]*6(-=-=-=))=))=-=)
+}}
+\caption{Chemical graph of Rofecoxib.}
+\label{RofecoxibFigure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+-[1](-[3])-[-1]-[1]*6(-=-(-[1](-[3])-[-1](=[-3]O)-[1]OH)=-=)
+}}
+\caption{Chemical graph of Ibuprofen.}
+\label{IbuprofenFigure}
+\end{figure}
+
+\end{multicols}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-10-12 Scripts/ChEMBLDataExtractor.py
Turning the scripts into macros

@@ -1,78 +1,0 @@
-########################################################################################################
-#                                                                                                      #
-#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
-#  Author:   Sergio Castañeiras Morales                                                                #
-#  Date:     02/10/2024                                                                                #
-#  Purpose:  Import molecule's data with a known IC50 activity respect a certain protein (i.e, COX-2)  #
-#                                                                                                      #
-########################################################################################################
-
-import requests
-import pandas as pd
-
-
-dataBaseBaseURL  = "https://www.ebi.ac.uk" # Defining the ChEMBL API web
-targetIDChEMBL   = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
-targetProperty   = "IC50" # Defining our target poperty
-requestDataLimit = "1000" # The ChEMBL database has a limit of 1000 requests at the same time.
-# However, we will send multimples request to extract all the data aviable.
-
-# Setting up the query URL with the previous data
-queryURL         = f"{dataBaseBaseURL}/chembl/api/data/activity.json?target_chembl_id={targetIDChEMBL}&standard_type={targetProperty}&limit={requestDataLimit}"
-
-# Initialize a list to store all activities
-allActivities   = []
-
-# Announcing the beinning of the requesting process
-print(f"Requesting data to the ChEMBL's database with the url:{queryURL}\n")
-
-while queryURL: # Using the loop to send multiple request 
-    response = requests.get(queryURL) # Getting the response for each request
-    if response.status_code == 200: # Checking if the request was successful
-        # Parsing the JSON response and selecting the activities (rellevant data) 
-        data = response.json()
-        activities = data['activities']
-        allActivities.extend(activities )# Appending the activities to the list
-        nextURL = data.get('page_meta', {}).get('next', None) # Gettin the URL for the next page, if it is available
-        if nextURL and nextURL.startswith('/'):# If the next URL is relative, prepend the base URL
-            queryURL = dataBaseBaseURL + nextURL
-        else:
-            queryURL = nextURL
-        print(f"Fetched {len(allActivities)} total activities so far...") # Indicating the progress
-    else:
[…]

### 2024-10-12 Scripts/ChEMBLDataExtractorMacro.py

@@ -1,0 +1,79 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     02/10/2024                                                                                #
+#  Purpose:  Import molecule's data with a known property activity respect a certain protein           #
+#            (i.e, COX-2)                                                                              #
+#                                                                                                      #
+########################################################################################################
+
+import requests # Package used for generating the database requests
+import pandas as pd # Importing pandas in order to use DataFrames
+
+# Defining the funtion responsable of extracting the data
+def ChEMBLExtractData(targetIDChEMBL, targetProperty, requestDataLimit=1000, saveDir="../Data", silentMode = False): 
+    dataBaseBaseURL = "https://www.ebi.ac.uk"  # Defining the ChEMBL API web
+    
+    # Setting up the query URL with the provided parameters
+    queryURL = f"{dataBaseBaseURL}/chembl/api/data/activity.json?target_chembl_id={targetIDChEMBL}&standard_type={targetProperty}&limit={requestDataLimit}"
+
+    allActivities = []
+
+    # Announcing the beginning of the requesting process
+    if silentMode != True: print(f"Requesting data from the ChEMBL database with the URL: {queryURL}\n")
+
+    while queryURL:
+        response = requests.get(queryURL)  # Getting the response for each request
+        if response.status_code == 200:  # Checking if the request was successful
+            data = response.json()
+            activities = data['activities']
+            allActivities.extend(activities)  # Appending the activities to the list
+            nextURL = data.get('page_meta', {}).get('next', None)  # Getting the next page URL, if available
+            if nextURL and nextURL.startswith('/'):  # If next URL is relative, prepend the base URL
+                queryURL = dataBaseBaseURL + nextURL
+            else:
+                queryURL = nextURL
+            if silentMode != True: print(f"Fetched {len(allActivities)} total activities so far...")
+        else:
+            if silentMode != True: print(f"Failed to fetch data: {response.status_code}")
+            break
+
[…]

### 2024-10-12 Scripts/DataFilterAndPlots.py

@@ -1,167 +1,0 @@
-########################################################################################################
-#                                                                                                      #
-#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
-#  Author:   Sergio Castañeiras Morales                                                                #
-#  Date:     05/10/2024                                                                                #
-#  Purpose:  Analyse the extracted data by ChEMBLDataExtractor.py in order to filter out irrellevant   #
-#            entries                                                                                   #
-#                                                                                                      #
-########################################################################################################
-
-import pandas as pd # Importing pandas in order to use DataFrames
-import matplotlib.pyplot as plt # Importing matplotlib for perfoming plots
-from sklearn.model_selection import train_test_split # Importing the funtion "train_test_split" for spliting our data in two 
-# sets. The training set and the testing set.
-
-targetIDChEMBL  	 = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
-targetProperty  	 = "IC50" # Defining our target poperty
-requestDataLimit	 = "1000" # The ChEMBL database has a limit of 1000 requests at the same time.
-dataFileName    	 = f"ChEMBL_ExtractorData{targetIDChEMBL},{targetProperty},{requestDataLimit}" # Defining the name of the data file 
-dataFilePath     	 = "../Data/"  # Defining the path where the data file is stored
-plotingPath			 = "../Plots/" # Defining the path where the plots files are stored
-lowerTargetProperty  = -1   # Defining the lowest 'standard_value' (= targetProperty) we want to take into acount
-higherTargetProperty = 200  # Defining the highest 'standard_value' (= targetProperty) we want to take into acount
-percentageEresed	 = 0.2	# Defining the percentage of the data we want to erase (number between 0 and 1)
[…]

### 2024-10-12 Scripts/DataFilterAndPlotsMacro.py

@@ -1,0 +1,130 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     05/10/2024                                                                                #
+#  Purpose:  Analyse the extracted data by ChEMBLDataExtractor.py in order to filter out irrellevant   #
+#            entries                                                                                   #
+#                                                                                                      #
+########################################################################################################
+
+import pandas as pd # Importing pandas in order to use DataFrames
+import matplotlib.pyplot as plt # Importing matplotlib for perfoming plots
+from sklearn.model_selection import train_test_split # Importing the funtion "train_test_split" for spliting our data in two sets. The training set and the testing set.
+
+import SlpitAndPrintDataFrameMacro # Importing the macro called "SlpitAndPrintDataFrameMacro.py"
+
+def ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty, lowerTargetProperty, higherTargetProperty,
+                              percentageEresed, testSizeProportion, randomSplitState,
+                              requestDataLimit = "1000", dataFilePath = "../Data/", plotingPath = "../Plots/", 
+                              silentMode = False):
+
+    # Defining file name based on target and property
+    dataFileName = f"ChEMBL_ExtractorData_{targetIDChEMBL}_{targetProperty}_{requestDataLimit}"
+
+    # List of unwanted variables to be dropped from the dataset
+    unwantedVariables = ['action_type', 'activity_comment', 'activity_properties', 'assay_type',
+                         'assay_variant_accession', 'assay_variant_mutation', 'bao_endpoint', 'bao_format',
+                         'bao_label', 'ligand_efficiency', 'potential_duplicate', 'qudt_units',
[…]

### 2024-10-12 Scripts/Main.py

@@ -1,0 +1,27 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     12/10/2024                                                                                #
+#  Purpose:  Link all the files and store the hole Machine Learning Process                            #
+#                                                                                                      #
+########################################################################################################
+
+
+import requests     # Package used for generating the database requests
+import pandas as pd # Importing pandas in order to use DataFrames
+
+import ChEMBLDataExtractorMacro # Importing the macro called "ChEMBLDataExtractorMacro.py"
+import DataFilterAndPlotsMacro  # Importing the macro called "DataFilterAndPlotsMacro.py"
+
+targetIDChEMBL       = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
+targetProperty       = "IC50"      # Defining our target poperty
+lowerTargetProperty  = -1          # Defining the lowest 'standard_value' (= targetProperty) we want to take into acount
+higherTargetProperty = 200         # Defining the highest 'standard_value' (= targetProperty) we want to take into acount
+percentageEresed	 = 0.2	       # Defining the percentage of the data we want to erase (number between 0 and 1)
+testSizeProportion	 = 0.2         # Defining the percentage of the data we want to keep for our training set (number between 0 and 1)
+randomSplitState     = 42	       # Defining the randomness for the Train/test splitting (Typically will be around 42)
+
+ChEMBLDataExtractorMacro.ChEMBLExtractData(targetIDChEMBL, targetProperty)
+DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty,lowerTargetProperty,higherTargetProperty,
+												  percentageEresed,testSizeProportion,randomSplitState)

### 2024-10-12 Scripts/SlpitAndPrintDataFrameMacro.py

@@ -1,0 +1,48 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     12/10/2024                                                                                #
+#  Purpose:  Macro used for spliting data frames evenly and printing their rellevant information       #
+#                                                                                                      #
+########################################################################################################
+
+import pandas as pd # Importing pandas in order to use DataFrames
+import matplotlib.pyplot as plt # Importing matplotlib for perfoming plots
+from sklearn.model_selection import train_test_split # Importing the funtion "train_test_split" for spliting our data in two 
+# sets. The training set and the testing set.
+
+# Helper function to split the dataframe iteratively
+def splitDataFrameIteration(dataFrame, column, splitValue):
+    upperCounter = 0; underCounter = 0
+    for iData in dataFrame[column]:
+        if iData >= splitValue:
+            upperCounter += 1
+        if iData <= splitValue:
+            underCounter += 1
+    return underCounter, upperCounter
+
+# Helper function to find split values for data gaps
+def findSplitDataFrame(dataFrame, column, percentageEresed):
+    iSplitValueUnder = 0
+    while True:
+        if splitDataFrameIteration(dataFrame, column, iSplitValueUnder)[0] < len(dataFrame) * (1 - percentageEresed) / 2:
+            iSplitValueUnder += 1
+        else:
+            break
+
+    iSplitValueUpper = iSplitValueUnder
+    while True:
+        if splitDataFrameIteration(dataFrame, column, iSplitValueUpper)[0] < len(dataFrame) * (1 + percentageEresed) / 2:
+            iSplitValueUpper += 1
+        else:
+            break
+
+    return iSplitValueUnder, iSplitValueUpper
+
+def printDataFrameLenMaxMin(dataFrame, targetProperty, standardValue = 'standard_value', standardUnits = 'standard_units', silentMode = False):
+    if silentMode != True: print(f'Number of entries:                  {len(dataFrame)}')
+    minimum = dataFrame[standardValue].idxmin()
+    maximum = dataFrame[standardValue].idxmax()
+    if silentMode != True: print(f'Minimum {targetProperty}:                       {float(dataFrame.loc[minimum,standardValue])} {dataFrame.loc[minimum, standardUnits]}')
[…]

### 2024-12-02 Notes/Notes.tex
Comenting the pearson correlation factors

@@
 \label{IbuprofenFigure}
+
 \end{figure}
-
+\begin{definition}\label{definitionPersonCoefficient}
+Pearson correlation coefficient: Given set of pairs of data $\{(x_i,y_i)\}_{i=1}^n$ the pearson correlation factor $r_{xy}$ is defined as,
+\begin{align}
+r_{xy}=\frac{\sum_{i=1}^n(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum_{i=1}^n(x_i-\bar{x}^2)}\sqrt{\sum_{i=1}^n(y_i-\bar{y}^2)}},
+\end{align}
+where $\bar{x}$ and $\bar{y}$ stand for the average value of ${x_i}_{i=1}^n$ and ${y_i}_{i=1}^n$ respectively.
+Note that $r_{xy}\in[-1,1]$.
+Therefore the sign of $r_{xy}$ is tightly related to the sign of alinear regression, more precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
+\end{definition}
 \end{multicols}
@@
 \end{figure}
+\end{observation}
+
+\begin{observation}
+Figure (\ref{figDataRepresentationFiltering}) clearly shows that multiples of 10 are significantly overrepresented compared to other values.
+Additionally, analyzing data from other proteins confirms that this is not an exception but rather a common pattern.
+It appears that experimental chemists have a preference for multiples of 10, often rounding their results to the nearest value in this category.
+Consequently, an inherent error associated with these values will always be present, and it will not be possible to completely eliminate it.
+\end{observation}
+
+\begin{observation}
+Once the chemical descriptors are computed, we proceed to calculate the Pearson correlation coefficients as defined in Definition (\ref{definitionPersonCoefficient}).
+The results are subsequently plotted in Figure (\ref{figPersonCorrelationFactors}).
+From the plot, we observe a “Gaussian bell” shape centered around zero, which aligns with our expectations.
+This suggests that there is no inherently preferred set of chemical descriptors for the protein, a finding that may initially seem at odds with the project’s goals.
+
+However, our hypothesis states that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
+This observation does not contradict that statement.
+Intuitively, we believe that filtering out descriptors with the lowest  $r^2$  values might lead to improved results.
+This possibility will be explored in subsequent discussions.
+\begin{figure}[H]
+\centering
+\includegraphics[width = 0.5\textwidth]{../Plots/CorrelationFactors.pdf}
+\caption{Representation of the Pearson correlation factors.}
+\label{figPersonCorrelationFactors}
+\end{figure}
+
 \end{observation}

### 2024-12-02 Scripts/RandomForest.py
Starting the implementation of the RandomForest Algorithm

@@ -1,0 +1,36 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     02/12/2024                                                                                #
+#  Purpose:  Implementing the "Random forest" algorithm in order to predict standard values            #
+#                                                                                                      #
+########################################################################################################
+
+import pandas as pd
+from sklearn.model_selection import train_test_split
+from sklearn.ensemble import RandomForestRegressor
+from sklearn.metrics import mean_squared_error, r2_score
+
+# Importing the desired files
+TrainingDataFrame = pd.read_feather("../data/ChEMBL_ExtractorData_CHEMBL372_IC50_1000min_-1max_200FilteredGap_min_17Gap_max_47Train.feather")
+TestingDataFrame  = pd.read_feather("../data/ChEMBL_ExtractorData_CHEMBL372_IC50_1000min_-1max_200FilteredGap_min_17Gap_max_47Test.feather")
+
+# adapting the data to the "RandomForest" format
+ChemDescriptorsTraining     = TrainingDataFrame.drop(['standard_value','canonical_smiles'], axis=1)
+InhibitionPotentialTraining = TrainingDataFrame['standard_value']
+ChemDescriptorsTesting      = TestingDataFrame.drop(['standard_value','canonical_smiles'], axis=1)
+InhibitionPotentialTesting  = TestingDataFrame['standard_value']
+
+numberOfTreesInTheForrest = [50, 100, 200, 500]
+
+for iNumberOfTrees in numberOfTreesInTheForrest:
+    RandomForest = RandomForestRegressor(n_estimators=iNumberOfTrees, random_state=42)
+    print(f"Using the 'RandomForest' algorithm for fitting the data with {iNumberOfTrees} trees. This may take a while")
+    RandomForest.fit(ChemDescriptorsTraining, InhibitionPotentialTraining)
+    InhibitionPotentialPredicted = RandomForest.predict(ChemDescriptorsTesting)
+    MeanSquaredError = mean_squared_error(InhibitionPotentialTesting, InhibitionPotentialPredicted)
+    r2 = r2_score(InhibitionPotentialTesting, InhibitionPotentialPredicted)
+    print(f"iNumberOfTrees    : {iNumberOfTrees}")
+    print(f"Mean Squared Error: {MeanSquaredError}")
+    print(f"R-squared         : {r2}")

### 2024-12-19 Notes/Notes.tex
Correlation factor results

@@
 \usepackage{tikz}
+\usepackage{forest}
 \usepackage{wrapfig}
@@
 \end{definition}
+\begin{definition}\label{definitionDecisionTree}
+A decision tree is a classification algorithm based on a series of ordered \emph{if} statements.
+The algorithm begins at the top of the tree, where a question is posed to the data.
+Depending on the answer, the data follows different branches, each corresponding to a subsequent question.
+This process is repeated at each node until the data reaches the bottom of the tree, where the path it has followed determines the classification of the given data.
+\par
+
+For example, a simple depiction of a decision tree is shown in Figure (\ref{figExDecisionTree}), where the decision of whether to enjoy a golfing day or not is determined based on a series of questions.
+\begin{figure}[H]
+\begin{forest}
+  for tree={ draw, rounded corners, align=center, edge={->}, parent anchor=south, child anchor=north, s sep+=5mm, l sep+=5mm  }
+  [Is it Sunny?
+    [$\checkmark$\\ Is Humidity High? 
+      [$\checkmark$\\ Don't Play, draw=red] 
+      [$\times$\\ Play, draw=green] 
+    ]
+    [$\times$\\ Is it Rainy? 
+      [$\times$\\ Is it Windy? 
+        [$\checkmark$\\ Don't Play, draw=red] 
+        [$\times$\\ Play, draw=green] 
+      ]
+      [$\checkmark$\\ Don't play, draw=red] 
+    ]
+  ]
+\end{forest}
+\caption{Example of a decision tree}
+\label{figExDecisionTree}
+\end{figure}
+This kind of algorithm is vividly present in the chemical landscape, for instance in the spectroscopy realm the determination of a molecule's symmetry group is provided by a decision tree such as Figure (\ref{figExScpectroDecisionTree})
+
+\begin{figure}[H]
+\centering
+\includegraphics[width = 0.5\textwidth]{GeneralSources/Point_group_determination_flowchart_v2.png}
+\caption{Decision tree for determining the point group of a molecule}
+\label{figExScpectroDecisionTree}
+\end{figure}
+
+\end{definition}
 \end{multicols}
@@
 \centering
-\includegraphics[width = 0.5\textwidth]{../Plots/DataGapRepresentationIC50percentageEresed20.0Gap_min_17Gap_max_47.pdf}
+\includegraphics[width = 0.5\textwidth]{../Plots/DataGapRepresentationIC50percentageEresed25.0Gap_min_15Gap_max_50.pdf}
 \caption{Data representation after the filtering.}
@@
 
-\begin{observation}
+\begin{observation}\label{observationCorrelationFactor}
 Once the chemical descriptors are computed, we proceed to calculate the Pearson correlation coefficients as defined in Definition (\ref{definitionPersonCoefficient}).
@@
 \centering
-\includegraphics[width = 0.5\textwidth]{../Plots/CorrelationFactors.pdf}
+\includegraphics[width = 0.5\textwidth]{../Plots/ChEMBL_ExtractorData_CHEMBL372_IC50_1000CorrelationFactors.pdf}
 \caption{Representation of the Pearson correlation factors.}
@@
 \end{figure}
+\end{observation}
+
+\begin{observation}
+The first algorithm implemented in this project is the \emph{Random Forest} machine learning algorithm.
+Although the project’s primary focus is not the detailed workings of machine learning algorithms, it is natural to ponder the essence of what the machine is doing.
+The name “Random Forest” is directly tied to the analogy between a tree and a decision tree.
+\par
+
+As described in Definition (\ref{definitionDecisionTree}), the Random Forest algorithm generates a collection of random decision trees.
+The number of trees in the forest is a configurable parameter of the algorithm.
+More specifically, the Random Forest algorithm produces a set of decision trees, each trained on a random subset of the training data.
+The structure of each tree adjusts during training to make predictions that closely approximate the true target values.
+The final output of the Random Forest is typically an aggregate of the predictions from all the individual trees, such as a majority vote for classification tasks or an average for regression tasks.
+\par
+
+One notable characteristic of this method is its inherent randomness.
+Each Random Forest model is unique, even if configured with the same parameters and initialized under identical conditions.
+However, experimental evidence suggests that this randomness does not significantly impact the results.
+If two Random Forest algorithms are trained on the same dataset using identical parameters, their outputs will converge, even if the internal structures of their decision trees differ.
+\end{observation}
+
+\begin{observation}
+From Observation (\ref{observationCorrelationFactor}), one might hypothesize that training with chemical descriptors that have higher correlation factors, or discarding those with low correlation factors, would lead to better predictions.
+Numerically, however, this hypothesis is contradicted, as shown in Table (\ref{tableCorrelationFactorVariation}).
+Despite this, the result remains consistent with our core hypothesis: the correlation factor of a chemical descriptor does not necessarily indicate its relevance in protein inhibition.
+Our key assertion is that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
+\par
+
+This suggests that the specific combinations of descriptors correlated with protein inhibition are not dependent on the individual correlation factor values.
+At first glance, a lack of correlation does not imply a lack of relationship to the inhibition!
 
 \end{observation}
+
 \end{multicols}
+\begin{table}[H]
+\centering
+\caption{Results for; Maximum $IC_{50}$ = 200 nM, Gap of the 25.0\% of the set, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+\label{tableCorrelationFactorVariation}
+\begin{tabular}{c||c|c|c|c}
+          &$\sigma\leq0$ & $\sigma\leq0.05$ & $\sigma\leq0.075$  & $\sigma\leq0.10$ \\\hline\hline
+$r^2$ & 0.9607020297015885 & 0.9608545198149474 & 0.9605224652065423 & 0.9599158186858139 \\\hline
+Mean Squared Error & 162.70220420738363 & 162.0708617391865 & 163.4456405456867 & 165.9572900112382 \\\hline
+number of descriptors & 2911 & 1485 & 1001 & 568
+\end{tabular}
+\end{table}
 \newpage

### 2024-12-19 Scripts/Main.py

@@ -17,11 +17,16 @@ config.read('config.ini')
 mode = 'DEFAULT'
 
 ChEMBLDataExtractorMacro.ChEMBLExtractData(config[mode]['targetIDChEMBL'], config[mode]['targetProperty'])
-dataFile = DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(config[mode]['targetIDChEMBL'], config[mode]['targetProperty'],
-                                                             int(config[mode]['lowerTargetProperty']), int(config[mode]['higherTargetProperty']), 
-                                                             float(config[mode]['percentageErased']), float(config[mode]['testSizeProportion']),
-                                                             int(config[mode]['randomSplitState']), config[mode]['AlvaDescPath'], 
-                                                             config[mode]['correlationMethod'], float(config[mode]['correlationLimitValue']))
+dataFile = DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(config[mode]['targetIDChEMBL'], 
+                                                             config[mode]['targetProperty'],
+                                                             int(config[mode]['lowerTargetProperty']), 
+                                                             int(config[mode]['higherTargetProperty']), 
+                                                             float(config[mode]['percentageErased']), 
+                                                             float(config[mode]['testSizeProportion']),
+                                                             int(config[mode]['randomSplitState']), 
+                                                             config[mode]['AlvaDescPath'], 
+                                                             config[mode]['correlationMethod'], 
+                                                             float(config[mode]['correlationLimitValue']))
 
 RandomForest.RandomForest(dataFile, int(config[mode]['numberOfTrees']), float(config[mode]['percentageErased']), 
                           float(config[mode]['testSizeProportion']), float(config[mode]['correlationLimitValue']))

### 2024-12-23 Notes/Notes.tex
Percentatge erased result

@@
 \usepackage{enumitem}
+\usepackage{pgfplots}
 \usepackage{float}
@@
 \usepackage{forest}
+\usepackage{pdflscape}
 \usepackage{wrapfig}
@@
 
-\begin{observation}
+\begin{observation}\label{ObsDescriptorsCorrelationFactor}
 From Observation (\ref{observationCorrelationFactor}), one might hypothesize that training with chemical descriptors that have higher correlation factors, or discarding those with low correlation factors, would lead to better predictions.
@@
 
+\begin{observation}
+The dependency on the gap generations seems much relevant than the dependency on the descriptors' correlation factor (Observation (\ref{ObsDescriptorsCorrelationFactor})).
+By changing the erased percentage (i.e.
+the fraction of data discarded in the gap generation) we can compute $r^2$ and the Mean Square Error (i.e.
+the statistical deviation) which provides the results depicted in Figure (\ref{FigPlotErasedPercentageVSRSquare}) and Figure (\ref{FigPlotErasedPercentageVSMeanSquaredError}) respectively.
+\end{observation}
+
+\begin{figure}[H]
+\caption{Plot of $\%_{\text{Erased}}$ vs $r^2$.For: maximum $IC_{50}$ = 200 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+\label{FigPlotErasedPercentageVSRSquare}
+\begin{tikzpicture}
+\begin{axis}[
+    width=0.5\textwidth,
+    height=8cm,
+    xlabel={$\%_{\text{Erased}}$},
+    ylabel={$r^2$},
+    xmin=0, xmax=100,
+    ymin=0.94, ymax=1.0,
+    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
+    ytick={0.9, 0.92, 0.94, 0.96, 0.98, 1.0},
+    legend pos=south east,
+    legend style={font=\small},
+    tick label style={font=\small},
+    label style={font=\small},
+]
+
+\addplot[
+    color=magenta,
+    mark=diamond*,
+    thick
+] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSRSquare.txt};
+
+\end{axis}
+\end{tikzpicture}
+\end{figure}
+
+\begin{figure}[H]
+\caption{Plot of $\%_{\text{Erased}}$ vs $Mean Squared Error$.For: maximum $IC_{50}$ = 200 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+\label{FigPlotErasedPercentageVSMeanSquaredError}
+\begin{tikzpicture}
+\begin{axis}[
+    width=0.5\textwidth,
+    height=8cm,
+    xlabel={$\%_{\text{Erased}}$},
+    ylabel={Mean Squared Error},
+    xmin=0, xmax=100,
+    ymin=0, ymax=200,
+    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
+    legend pos=north east,
+    legend style={font=\small},
+    tick label style={font=\small},
+    label style={font=\small}
+]
+
+\addplot[
+    color=magenta,
+    mark=diamond*,
+    thick
+] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSMeanSquaredError.txt};
+
+\legend{Mean Squared Error}
+\end{axis}
+\end{tikzpicture}
+\end{figure}
+
 \end{multicols}
-\begin{table}[H]
-\centering
-\caption{Results for; Maximum $IC_{50}$ = 200 nM, Gap of the 25.0\% of the set, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
-The training is done with 200 trees.}
-\label{tableCorrelationFactorVariation}
-\begin{tabular}{c||c|c|c|c}
-          &$\sigma\leq0$ & $\sigma\leq0.05$ & $\sigma\leq0.075$  & $\sigma\leq0.10$ \\\hline\hline
-$r^2$ & 0.9607020297015885 & 0.9608545198149474 & 0.9605224652065423 & 0.9599158186858139 \\\hline
-Mean Squared Error & 162.70220420738363 & 162.0708617391865 & 163.4456405456867 & 165.9572900112382 \\\hline
-number of descriptors & 2911 & 1485 & 1001 & 568
-\end{tabular}
-\end{table}
+
 \newpage
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\begin{landscape}
+\section{Results}
+\begin{table}[H]
+\centering
+\caption{Results for; Maximum $IC_{50}$ = 200 nM, Gap of the 25.0\% of the set, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+\label{tableCorrelationFactorVariation}
+\begin{tabular}{c||c|c|c|c}
+          &$\sigma\leq0$ & $\sigma\leq0.05$ & $\sigma\leq0.075$  & $\sigma\leq0.10$ \\\hline\hline
+$r^2$ & 0.9607020297015885 & 0.9608545198149474 & 0.9605224652065423 & 0.9599158186858139 \\\hline
+Mean Squared Error & 162.70220420738363 & 162.0708617391865 & 163.4456405456867 & 165.9572900112382 \\\hline
+number of descriptors & 2911 & 1485 & 1001 & 568
+\end{tabular}
+\end{table}
+
+\begin{table}[H]
+\centering
+\caption{Results for; Maximum $IC_{50}$ = 200 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+
+\begin{tabular}{c||c|c|c|c}
+$\%_{\text{Erased}}$  	& 0\% & 5\% & 10\%  & 15\% \\\hline\hline
+$r^2$ 				& 0.9410691012016194 & 0.9450975181635125 & 0.9492662637374885 & 0.954840165823525 \\\hline
+Mean Squared Error 		& 195.50415499282306 & 187.34588735050227 & 189.17427179281864 & 167.5904134577239 
+\end{tabular}
+\begin{tabular}{c||c|c|c|c} 
+$\%_{\text{Erased}}$  	&  20\%  & 25\% & 30\% & 35\% \\\hline\hline
+$r^2$ 				& 0.960093147530398 & 0.9607020297015885 & 0.9659474255238565 & 0.970950038525679 \\\hline
+Mean Squared Error 		& 159.86610568752263 & 162.70220420738363 & 150.60605102824292 & 132.53106869928666
+\end{tabular}
+\begin{tabular}{c||c|c|c|c}
+$\%_{\text{Erased}}$         & 40\%  & 45\% & 50\% & 55\% \\\hline\hline
+$r^2$ 				& 0.9735150867866535 & 0.9761682347024537 & 0.9794766777874534 & 0.9836139552920377 \\\hline
+Mean Squared Error 		& 130.3450775382814 &  124.45078192954777 & 112.31398471818515 & 94.8719409443141
+\end{tabular}
+\begin{tabular}{c||c|c|c|c}
+$\%_{\text{Erased}}$  	&60\%  & 65\% & 70\% & 75\%  \\\hline\hline
+$r^2$ 				&0.9858128266667714 & 0.9920845685273683 & 0.9950402754045806 & 0.9960292052079258\\\hline
+Mean Squared Error 		&85.87640609411348 &  53.48552498895907 & 35.71100434005104 & 30.45304023300008
+\end{tabular}
+
+\begin{tabular}{c||c|c|c|c}
+$\%_{\text{Erased}}$  	&80\%  & 85\% & 90\% & 95\% \\\hline\hline
+$r^2$ 				&0.9971354719623441 & 0.9993589449322425 & 0.9996146336878613 & 0.9999982353685487\\\hline
+Mean Squared Error 		&22.873087477997174 &  5.275980426255672 & 3.083365552988717 & 0.010325883398321972
+\end{tabular}
+
+\end{table}
+
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%% VARIOUS %%%%%%%%%%%%%%%%%%

### 2025-02-03 Notes/Notes.tex
Some notes

@@
 \end{titlepage}
+
+\newpage
+\thispagestyle{empty}
+\vspace*{\fill} % Push content to vertical center
+\begin{flushright}
+    \emph{“The dumbest people I know are those who know it all.”}\\[1em]
+    \textbf{Malcolm S. Forbes}
+\end{flushright}
+\vspace*{\fill} % Balance vertical spacing
 
@@
 We have extracted all the aviable data from the \emph{ChEMBL} database with a known $IC_{50}$ value for the COX-2.
-After deleting  entries with the same canonical smile we remain with 4827 entries.
-We filter, keeping just those with a $IC_{50}\in [-1,200]$\footnote{Note that the lower constrain won't be ever surpassed by the $IC_{50}$ defintion \ref{definitionIC50}.
-This is equivalent to avoid constraining the data.}.
-Then we obtain a remaining set of 1518 entries represented in the Figure (\ref{figDataRepresentationFiltering}).
+After deleting  entries with the same canonical smile 4827 entries remain.
+By keeping just those with a $IC_{50}\in [-1,200]$\footnote{Note that the lower constrain won't be ever surpassed by the $IC_{50}$ defintion \ref{definitionIC50}.
+This is equivalent to avoid constraining the data.}, we obtain a remaining set of 1518 entries represented in the Figure (\ref{figDataRepresentationFiltering}).
 \begin{figure}[H]
@@
 
-\begin{observation}
-Figure (\ref{figDataRepresentationFiltering}) clearly shows that multiples of 10 are significantly overrepresented compared to other values.
-Additionally, analyzing data from other proteins confirms that this is not an exception but rather a common pattern.
-It appears that experimental chemists have a preference for multiples of 10, often rounding their results to the nearest value in this category.
-Consequently, an inherent error associated with these values will always be present, and it will not be possible to completely eliminate it.
+\begin{observation}\label{ObsDataInherentError}
+Figure (\ref{figDataRepresentationFiltering}) clearly shows multiples of 10 are significantly overrepresented respect to other values.
+Additionally, by analyzing data from other proteins we can confirm this is not an exception but rather the norm.
+It looks like experimental chemists have a preference for multiples of 10, often rounding their results to the nearest value in this category.
+Consequently, an inherent error associated with these values will always be present, and we will have to deal with it.
 \end{observation}
@@
 \end{figure}
+
+\begin{observation}
+From Observation (\ref{ObsDataInherentError}), we know the data has an inherent precision problem, especially when approaching higher  $IC_{50}$  values, additionally we do not now the precision of some measurements.
+Since our working models do not account for the lack of precision in each molecule’s data, the values of  $r^2$  and mean squared error are not expected to be exactly 1 and 0, respectively.
+In fact, some variance and uncertainty are inevitable.
+Therefore, discarding more than 50\% of our data would be a critical mistake, even if statistical measures suggest otherwise.
+
+For example, suppose we aim to build a table.
+We have an arbitrarily large number of table legs, each varying slightly in length.
+On one hand, if we choose to build a three-legged table, we would obtain a rigid structure with no variance (i.e.
+statistically, this would be considered the “best” table).
+However, it would be steeply inclined and therefore useless, as any object placed on it would slide off.
+On the other hand, if we use as many legs as possible, the table may initially be unstable due to variations in leg length.
+Nevertheless, as more legs are added, the instability decreases, eventually allowing us to place objects on it and even have a meal.
+
+This example highlights the fact that an  $r^2$  value of 1 and a mean squared error of 0 are not absolute requirements in this case, due to Observation (\ref{ObsDataInherentError}).
+However, these values still serve as a good reflection of our method’s reliability up to a certain threshold.
+
+In this work, we will arbitrarily set this threshold at  $r^2 = 0.96$ .
+This hard-coded decision is purely conventional, as we need to establish a point beyond which  $r^2$  values become meaningless (i.e., obtaining  $r^2$  values above 0.96 is unnecessary, given that such variance is inherent to our data).
+The justification for this choice is that, in some areas of chemistry\footnote{Particularly in analytical chemistry} two data sets are generally considered correlated if their  $r^2$  value exceeds 0.96.
+
+However, it is important to emphasize that this convention is purely subjective and should not be regarded as an inviolable rule.
+
+\end{observation}
 

### 2025-02-06 Manuscript/manuscript.tex
Starting to write

@@
 \usepackage[english]{babel}
+\usepackage{lipsum}
 \usepackage[table,xcdraw]{xcolor}
-\usepackage{natbib}
 \usepackage{enumitem}
+\usepackage{pgfplots}
+\usepackage{float}
+\usepackage{chemfig}
 \usepackage{yfonts}
 \usepackage{tikz}
+\usepackage{forest}
+\usepackage{pdflscape}
 \usepackage{wrapfig}
+\usepackage{url}
 \usepackage[normalem]{ulem}
@@
 \useunder{\uline}{\ul}{}
+
+%%%%%%%%%%%%%%% CODELISTINGS %%%%%%%%%%%%%%%%
+\usepackage{listings}
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=t,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{achemso}
+
+\usepackage{titlesec}
+\titleformat{\section}[block]{\normalfont\large\bfseries\centering}{\thesection}{1em}{} % changing the "section" fontsize and centering it
+\renewcommand{\thesection}{\Roman{section}}  % Roman numerals for section numbers
+
+\newtheorem{definition}{Definition}
+\newtheorem{observation}{Observation}
+\newtheorem{reflection}{Reflection}
+\newtheorem{PyPackage}{Package}
+\newtheorem{book}{Book}
 
@@
 \newcommand\subject{Final Degree Project}
-\newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
-\newcommand\hwnumber{1} 
+\newcommand\degree{Bachelor's Degree in Chemistry}
+\newcommand\documenttitle{Notes: AI application for azophotoswitches' optimization with pharmacological interest}
 \newcommand\NetIDb{Universitat Autònoma de Barcelona}
@@
 \begin{document}
-\title{\vspace{5cm} \normalsize \textsc{\NetIDb}
-		\\ [2.0cm]
+\title{\vspace{4cm} \normalsize 
+		\includegraphics[width = 0.25\textwidth]{GeneralSources/UABLogo.png}\\ [0.5cm]
+		\textsc{\NetIDb}\\ [2.0cm]
 		\HRule{0.5pt} \\
 		\LARGE \textbf{\uppercase{\documenttitle}}
-		\HRule{2pt} \\ [0.5cm]
-		\normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\
-		}\normalsize \vspace*{5\baselineskip}}
+		\HRule{2pt} \\ [1.5cm]
+		\normalsize \begin{tabular}{rcl}  % Create a right-left column alignment
+        \textsc{Author} & : & \textsc{Sergio Castañeiras Morales} \\
+        \textsc{Supervisor} & : & \textsc{Miquel Moreno Ferrer} \\
+        \textsc{Co-Supervisor} & : & \textsc{Àngels Gonzalez Lafont}
+    \end{tabular}
+    \normalsize \vspace*{5\baselineskip}
+		}
 
-\date{\today}
+\date{2024-2025}
 
-\author{\large \textsc{\subject}}
+\author{\large \textsc{\subject} \\ \textsc{\degree}}
 
@@
 \newpage
+\thispagestyle{empty}
+\mbox{} 
+\newpage
+\thispagestyle{empty}
+\vspace*{\fill} % Push content to vertical center
+\begin{flushright}
+    \emph{“The dumbest people I know are those who know it all.”}\\[1em]
+    \textbf{Malcolm S. Forbes}
+\end{flushright}
+\vspace*{\fill} % Balance vertical spacing
+\newpage
 \pagestyle{fancyplain}
@@
 \rhead{\subject}
-\cfoot{}
-\rfoot{\small\thepage}
+\cfoot{\small\thepage}
+\rfoot{}
 \headsep 1.5em
-The current manuscript's format is temporal!!!\par
-Testing cite: \cite{NationalLibraryOfMedicineGeneralArticle}
 
 \newpage
-%Bibliography %
-\bibliographystyle{plain}
+\begin{multicols}{2}[\begin{center}
+\begin{abstract}
+Insert abstract
+\end{abstract}
+\end{center}
+]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%&%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+The impact of Artificial Intelligence on science has being nothing but an outstanding breakthrough without many comparable predecessors.
+This projects aims to develop an implementation of artificial intelligence in computational chemistry, more concretely we aim to use artificial intelligence - based algorithms to predict the inhibition potential of a molecules for a certain protein.
+\par
+
+Now a days one of the main goals of computational chemistry is the capability of predicting certain properties of unstudied substances without the experimental costs.
+Moreover we do focus on the \emph{cyclooxygenase-2} (COX-2) since is well known to be related to cancer development.
+
+\end{multicols}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \bibliographystyle{achemso}
 \bibliography{references} 

### 2025-02-07 Manuscript/manuscript.tex
Writing the introduction

@@
 \usepackage{titlesec}
-\titleformat{\section}[block]{\normalfont\large\bfseries\centering}{\thesection}{1em}{} % changing the "section" fontsize and centering it
+\titleformat{\section}[block]{\normalfont\normalsize\bfseries\centering}{\thesection}{1em}{} % changing the "section" fontsize and centering it
 \renewcommand{\thesection}{\Roman{section}}  % Roman numerals for section numbers
@@
 \newpage
+
+\setcounter{page}{1}
 \pagestyle{fancyplain}
@@
 
-\newpage
 \begin{multicols}{2}[\begin{center}
 \begin{abstract}
-Insert abstract
+We explore AI-based algorithms capabilities, specifically the Random Forest model, to predict a drug’s inhibition potential for cyclooxygenase-2 (COX-2), a key protein linked to cancer.
+Using molecular descriptors extracted from the ChEMBL database, AI models are trained to identify patterns correlating with inhibition potential.
+The study aims to validate AI’s effectiveness in drug discovery and molecular analysis, demonstrating its potential as a powerful tool in computational chemistry research.
 \end{abstract}
@@
 \section{Introduction}
-The impact of Artificial Intelligence on science has being nothing but an outstanding breakthrough without many comparable predecessors.
-This projects aims to develop an implementation of artificial intelligence in computational chemistry, more concretely we aim to use artificial intelligence - based algorithms to predict the inhibition potential of a molecules for a certain protein.
+The impact of Artificial Intelligence (AI) on science has been nothing but an outstanding breakthrough, with few comparable predecessors.
+The rapid advancements in AI have transformed numerous scientific fields, including computational chemistry.
+Nowadays, one of the main goals of computational chemistry is to predict certain properties of unstudied substances with minimal experimental costs.
+Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive and resource-intensive.
+AI provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.
+AI algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception.\par
+
+This project aims to implement artificial intelligence in computational chemistry, concretely, using AI-based algorithms to predict a drug’s inhibition potential for a given protein.
+To achieve this, we make use of the ChEMBL database, a vast repository of bioactive molecules with drug-like properties.
+We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset.
+The chemical descriptors of each molecule in the database are then computed using AlvaDesk software.
+Around $10^4$ descriptors are calculated, which go from the elemental molecular weight, to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
+The resulting dataset is subsequently used to train AI models, enabling them to predict the inhibition potential of unknown compounds.
+Finally, we evaluate the reliability of each model by testing it against real experimental data.
 \par
 
-Now a days one of the main goals of computational chemistry is the capability of predicting certain properties of unstudied substances without the experimental costs.
-Moreover we do focus on the \emph{cyclooxygenase-2} (COX-2) since is well known to be related to cancer development.
+It is important to emphasize the central hypothesis of this project: \emph{There exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
+While this idea may seem fundamental, it remains unproven due to the complexity of molecular interactions and the vast number of possible descriptor combinations.
+Despite significant progress in computational chemistry, identifying the exact descriptors that govern inhibition potential has been a persistent challenge.
+The lack of an ultimate proof underscores the need for advanced computational techniques.
+By analyzing large datasets, AI can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par
+
+At this stage, we focus on cyclooxygenase-2 (COX-2), a protein well known for its strong association with cancer development and inflammatory diseases.
+COX-2 plays a crucial role in the biosynthesis of prostaglandins, which mediate inflammation and pain.
+Overexpression of COX-2 has been linked to various types of cancer, making it a prime target for drug development.
+COX-2 inhibitors, such as celecoxib and rofecoxib, have been widely studied for their therapeutic potential.
+The scientific community has devoted an extensive research to COX-2, even before the rise of AI, due to its biomedical significance.
+By applying AI models to COX-2, we assess their compatibility with the latest research findings, demonstrating AI’s potential as a powerful tool in computational chemistry research.
+Our approach not only validates AI’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing COX-2 interactions.\par
+
+The AI algorithm used in this study is the Random Forest algorithm, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
+This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting.
+The Random Forest algorithm operates by constructing numerous random decision trees, each trained on different subsets of the dataset.
+The final prediction is obtained by averaging the outputs of all trees, ensuring robust and reliable results.
+
+Moreover, the choice of the Random Forest algorithm is motivated by the presence of decision trees in various chemistry-related fields.
+In spectroscopy, for instance, decision trees are used in group theory to classify molecular symmetry.
+Similarly, in analytical chemistry, decision trees assist in substance separation techniques, while in organic chemistry, they are used to model reaction pathways.\par
+
+This study aims to bridge the gap between artificial intelligence and computational chemistry, demonstrating AI’s potential to revolutionize drug discovery and molecular research.
+The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process.
+Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.
 

### 2025-02-07 Manuscript/manuscript.tex
Writing the introduction
Comencing the methodology writting

@@
 \documentclass[12pt,letterpaper]{article}
+% \documentclass[journal=acsomega,manuscript=article]{achemso}
 \usepackage{fullpage}
@@
 \usepackage{achemso}
+% \bibliographystyle{achemso}
 
@@
 \newcommand\degree{Bachelor's Degree in Chemistry}
-\newcommand\documenttitle{Notes: AI application for azophotoswitches' optimization with pharmacological interest}
+\newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
 \newcommand\NetIDb{Universitat Autònoma de Barcelona}
@@
 Using molecular descriptors extracted from the ChEMBL database, AI models are trained to identify patterns correlating with inhibition potential.
-The study aims to validate AI’s effectiveness in drug discovery and molecular analysis, demonstrating its potential as a powerful tool in computational chemistry research.
+The study validates AI’s effectiveness in drug discovery and molecular analysis, proving its potential as a powerful tool in computational chemistry research.
 \end{abstract}
 \end{center}
+Keywords: \emph{COX-2, cyclooxygenase-2, Random Forest, Machine Learning, AI, Artificial Intelligence}.
 ]
@@
 The impact of Artificial Intelligence (AI) on science has been nothing but an outstanding breakthrough, with few comparable predecessors.
-The rapid advancements in AI have transformed numerous scientific fields, including computational chemistry.
-Nowadays, one of the main goals of computational chemistry is to predict certain properties of unstudied substances with minimal experimental costs.
+The rapid advancements in AI have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry.
+Nowadays, one of the main goals of computational chemistry is to predict certain properties of unstudied substances with minimal experimental costs\cite{AlphaFold2CommumityAssesment}.
 Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive and resource-intensive.
-AI provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.
-AI algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception.\par
+On the other hand, AI algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception.
+AI provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.\par
 
-This project aims to implement artificial intelligence in computational chemistry, concretely, using AI-based algorithms to predict a drug’s inhibition potential for a given protein.
-To achieve this, we make use of the ChEMBL database, a vast repository of bioactive molecules with drug-like properties.
+This project aims to implement artificial intelligence in computational chemistry, concretely, using AI-based algorithms to predict a drug’s inhibition potential\cite{BookIC50} for a given protein.
+To achieve this, we make use of the ChEMBL database\cite{ChemblDatabase}, a vast repository of bioactive molecules with drug-like properties.
 We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset.
-The chemical descriptors of each molecule in the database are then computed using AlvaDesk software.
-Around $10^4$ descriptors are calculated, which go from the elemental molecular weight, to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
+The chemical descriptors of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
+Around $10^4$ descriptors are calculated\cite{DescriptorsBookClassification}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
 The resulting dataset is subsequently used to train AI models, enabling them to predict the inhibition potential of unknown compounds.
@@
 
-It is important to emphasize the central hypothesis of this project: \emph{There exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
+It is important to emphasise the central hypothesis of this project: \emph{There exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
 While this idea may seem fundamental, it remains unproven due to the complexity of molecular interactions and the vast number of possible descriptor combinations.
@@
 The lack of an ultimate proof underscores the need for advanced computational techniques.
-By analyzing large datasets, AI can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par
+By analysing large datasets, AI can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par
 
-At this stage, we focus on cyclooxygenase-2 (COX-2), a protein well known for its strong association with cancer development and inflammatory diseases.
+At this stage, we focus on cyclooxygenase-2 (COX-2), a protein well known for its strong association with cancer development and inflammatory diseases\cite{DefinitionCOX2CancerDictionary}.
 COX-2 plays a crucial role in the biosynthesis of prostaglandins, which mediate inflammation and pain.
@@
 COX-2 inhibitors, such as celecoxib and rofecoxib, have been widely studied for their therapeutic potential.
-The scientific community has devoted an extensive research to COX-2, even before the rise of AI, due to its biomedical significance.
+The scientific community has devoted an extensive research to COX-2, even before the rise of AI, due to its biomedical significance\cite{Cox2InhibitorsReview}.
 By applying AI models to COX-2, we assess their compatibility with the latest research findings, demonstrating AI’s potential as a powerful tool in computational chemistry research.
@@
 
-The AI algorithm used in this study is the Random Forest algorithm, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
+The AI algorithm used in this study is the Random Forest algorithm\cite{MachineLearningRandomForest}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
 This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting.
@@
 
-This study aims to bridge the gap between artificial intelligence and computational chemistry, demonstrating AI’s potential to revolutionize drug discovery and molecular research.
+This study aims to bridge the gap between artificial intelligence and computational chemistry, proving AI’s potential to revolutionise drug discovery and molecular research.
 The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process.
@@
 
-\end{multicols}
+\section{Methodology}
+The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database.
+Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Def.
+\ref{definitionIC50}) with a limit of 1000 entries per request.
+The process is iterated until all data is extracted leading a total of 7979 molecules.
+By removing entries with the same canonical smiles a total of 5112 molecules remain.
+Among this entries well known drugs such as Celecoxib (Def.
+\ref{definitionCelecoxib}), Rofecoxib (Def.
+\ref{definitionRofecoxib}) or even Ibuprofen can be found.
+However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure.
+A hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{Similar $IC_{50}$ working range have also been used in similar studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e.
+molecules).
 
@@
 
-% \bibliographystyle{achemso}
 \bibliography{references} 
 %%%%%%%%
+\appendix
+\section{Relevant definitions}
+\begin{definition}\label{definitionIC50}
+$IC_{50}$: Half maximal inhibitory concentration assigned to the drug concentration required for a $50\%$ inhibition a protein.
+Other quantities such as $IC_{90}$ or $IC_{99}$ are also commonly used.
+However, $IC_{90}$ is generally approximated as 10 times the $IC_{50}$ concentration in virtue of oexperimental observations\cite{BookIC50}.
+For this project, we aim to identify substances with the lowest possible $IC_{50}$, as our goal is to minimize the presence of foreign substances in the living organism.
+\end{definition}
+
+\begin{definition}\label{definitionCelecoxib}
+Celecoxib: \footnote{UPAC name: 4-[5-(4-Methylphenyl)-3-(trifluoromethyl)pyrazol-1-yl]benzenesulfonamide} drug known to be a selective COX-2 inhibitor (currently is not \emph{highly selective} respect to newer drugs), see Figure (\ref{CelecoxibFigure}).
+It $IC_{50}$ value is $120$ nM.
+\end{definition}
+
+\begin{definition}\label{definitionRofecoxib}
+Rofecoxib: \footnote{UPAC name: 4-(4-methylsulfonylphenyl)-3-phenyl-5H-furan-2-one} drug known to be a selective COX-2 inhibitor, see Figure (\ref{RofecoxibFigure}). It $IC_{50}$ value is $180$ nM.
+\end{definition}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+H_2N-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
+}}
+\caption{Chemical graph of Celecoxib.}
+\label{CelecoxibFigure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]*5(--O-(=[2.25]O)-(-[4.5]*6(-=-=-=))=))=-=)
+}}
+\caption{Chemical graph of Rofecoxib.}
+\label{RofecoxibFigure}
+\end{figure}
+\end{multicols}
 

### 2025-02-07 Scripts/ChEMBLDataExtractorMacro.py

@@ -18,11 +18,12 @@ def ChEMBLExtractData(targetIDChEMBL, targetProperty, requestDataLimit=1000, sav
     if os.path.exists(f"{saveDir}/ChEMBL_ExtractorData_{targetIDChEMBL}_{targetProperty}_{requestDataLimit}.feather"): 
         print("The data is already downloaded!")
         return 
-
     dataBaseBaseURL = "https://www.ebi.ac.uk"  # Defining the ChEMBL API web
     
     # Setting up the query URL with the provided parameters
     queryURL = f"{dataBaseBaseURL}/chembl/api/data/activity.json?target_chembl_id={targetIDChEMBL}&standard_type={targetProperty}&limit={requestDataLimit}"
+    
+    print(queryURL)
 
     allActivities = []
 

### 2025-02-07 Scripts/DataFilterAndPlotsMacro.py

@@ -79,7 +79,7 @@ def ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty, lowerTargetPropert
     if not silentMode: print("Deleting descriptors with correlation factors below ", correlationLimitValue)
     
     # ploting the correlation factors histogram
-    if not silentMode: print(f"Ploting the correlation factors in ../Plots/{dataFileName}CorrelationFactors.pdf")
+    if not silentMode: print(f"Ploting the correlation factors in ../Plots/{targetIDChEMBL}{dataFileName}CorrelationFactors.pdf")
     plt.hist(correlationDataFrame, bins=40, color='purple', range = (-1,1), label=f"Number of descriptors {dataFiltered.shape[1]-1}")
     plt.title('Correlation factors of the computed chemical descriptors')
     plt.xlabel('Correlation Values')

### 2025-02-07 Scripts/Main.py

@@ -17,6 +17,7 @@ config.read('config.ini')
 mode = 'DEFAULT'
 
 ChEMBLDataExtractorMacro.ChEMBLExtractData(config[mode]['targetIDChEMBL'], config[mode]['targetProperty'])
+
 dataFile = DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(config[mode]['targetIDChEMBL'], 
                                                              config[mode]['targetProperty'],
                                                              int(config[mode]['lowerTargetProperty']), 

### 2025-02-07 Scripts/Testing.py

@@ -1,0 +1,22 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     02/10/2024                                                                                #
+#  Purpose:  Import molecule's data with a known property activity respect a certain protein           #
+#            (i.e, COX-2)                                                                              #
+#                                                                                                      #
+########################################################################################################
+import requests
+
+# Test query URL
+queryURL = "https://www.ebi.ac.uk/chembl/api/data/activity.json?target_chembl_id=CHEMBL4523964&standard_type=IC50&limit=5"
+
+response = requests.get(queryURL)
+
+if response.status_code == 200:
+    data = response.json()
+    print("Response keys:", data.keys())  # Check top-level keys
+    print("\nExample data:\n", data)  # Print full response (first few entries)
+else:
+    print("Request failed with status code:", response.status_code)

### 2025-02-13 Manuscript/GeneralSources/DataSplittingDiagram.tex
Procedure Writting

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, positioning}

\begin{document}

\begin{tikzpicture}[
    node distance=1.0cm and 0.5cm,
    every node/.style={draw, align=center, minimum width=3.5cm, minimum height=1.0cm},
    initialdataset/.style={rectangle},
    process/.style={rectangle, dashed},
    dataset/.style={rectangle},
    split/.style={rectangle},
    erased/.style={rectangle, dashed}
]

    % Initial dataset
    \node[initialdataset] (data) {Initial Dataset};

    % Compute Average IC50
    \node[process, below=of data] (average) {Compute Average $IC_{50}$};
    % Erased Neighborhood
    \node[erased, below=of average] (preerased) {Erase Middle Neighborhood \\ Erased proportion = percentageErased\%};

    \node[rectangle, below=of preerased] (erased) {Reduced Dataset};

    % Split into highly active and least active
    \node[split, below left=1.5cm and 2.5cm of erased] (highly) {Highly Active Molecules \\ (Low $IC_{50}$)};
    \node[split, below right=1.5cm and 2.5cm of erased] (least) {Least Active Molecules \\ (High $IC_{50}$)};

    % Training and Testing Splits
    \node[dataset, below left=1.5cm and 0cm of  highly] (high_train) {Training Set \\ Proportion :\\ (100 - testSizeProportion)\%};
    \node[dataset, below right=1.5cm and 0cm of  highly] (high_test) {Testing Set \\ Proportion :\\ testSizeProportion\%};

    \node[dataset, below left=1.5cm and 0cm of least] (low_train) {Training Set \\ Proportion :\\ (100 - testSizeProportion)\%};
    \node[dataset, below right=1.5cm and 0cm of least] (low_test) {Testing Set \\  Proportion :\\ testSizeProportion\%};

    % Arrows
    \draw[->] (data) -- (average);
    \draw[->] (average) -- (preerased);
    \draw[->] (preerased) -- (erased);
    \draw[->] (erased) -- (highly);
    \draw[->] (erased) -- (least);
    \draw[->] (highly) -- (high_train);
    \draw[->] (highly) -- (high_test);
    \draw[->] (least) -- (low_train);
    \draw[->] (least) -- (low_test);

\end{tikzpicture}

\end{document}

### 2025-02-13 Manuscript/manuscript.tex
Procedure Writting

@@
 
-\setcounter{page}{1}
 \pagestyle{fancyplain}
@@
 \headsep 1.5em
-
+\setcounter{page}{1}
 \begin{multicols}{2}[\begin{center}
@@
 Overexpression of COX-2 has been linked to various types of cancer, making it a prime target for drug development.
-COX-2 inhibitors, such as celecoxib and rofecoxib, have been widely studied for their therapeutic potential.
+COX-2 inhibitors, such as Celecoxib (Def.
+\ref{definitionCelecoxib}) and Rofecoxib (Def.
+\ref{definitionRofecoxib}), have been widely studied for their therapeutic potential.
 The scientific community has devoted an extensive research to COX-2, even before the rise of AI, due to its biomedical significance\cite{Cox2InhibitorsReview}.
@@
 \section{Methodology}
+The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.
+
 The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database.
@@
 The process is iterated until all data is extracted leading a total of 7979 molecules.
+Hence the datasheet is processed in pandas dataframes\cite{PythonPackagePandas} and encrypted into binary feather files to optimise reading-writting speed.
 By removing entries with the same canonical smiles a total of 5112 molecules remain.
@@
 However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure.
-A hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{Similar $IC_{50}$ working range have also been used in similar studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e.
+A hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e.
 molecules).
+\par
+With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $10^4$ descriptors per molecule.
+Here, the Pearson correlation coefficient between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
+
+At this stage, the average $IC_{50}$ is calculated, and the neighborhood size corresponding to the percentage defined by the hard-coded variable \emph{percentageErased} is removed.
+This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}—those with lower and higher $IC_{50}$ values, respectively.
+Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} and a \emph{testing set}, following the proportion specified by the hard-coded variable \emph{testSizeProportion}.
+This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
+\end{multicols}
+\begin{figure}[H]
+\centering
+\includegraphics[width = \textwidth]{GeneralSources/DataSplittingDiagram.pdf}
+\caption{Scheme of the splitting procedure.}
+\label{FigureDataSplittingDiagram}
+\end{figure}
+\begin{multicols}{2}
+Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google.
+This algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets.
+Later, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.
+
+Using the results, the \emph{True Positive Rate} (Def.
+\ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def.
+\ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def.
+\ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def.
+\ref{definitionMatthewsCorrelationCoeficient}) are computed.
+Based on these computational results, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to obtain the best results.
 
@@
 %%%%%%%%
+\section{Abbreviation index}
+COX-2 : cyclooxygenase-2\par
+AI : Artificial Intelligence\par
+ML : Machine Learning\par
+RD : Random Forest\par
+ID : Identification\par
+$IC_{50}$: Half maximal inhibitory concentration \par
+$IC_{90}$: 90 percent inhibitory concentration \par
+$IC_{99}$: 99 percent inhibitory concentration \par
+TP: True Positive\par
+FP: False Positive\par
+TN: True Negative\par
+FN: False Negative
 \appendix
@@
 Other quantities such as $IC_{90}$ or $IC_{99}$ are also commonly used.
-However, $IC_{90}$ is generally approximated as 10 times the $IC_{50}$ concentration in virtue of oexperimental observations\cite{BookIC50}.
+However, $IC_{90}$ is generally approximated as 10 times the $IC_{50}$ concentration in virtue of experimental observations\cite{BookIC50}.
 For this project, we aim to identify substances with the lowest possible $IC_{50}$, as our goal is to minimize the presence of foreign substances in the living organism.
@@
 \end{figure}
+\begin{definition}\label{definitionPersonCoefficient}
+Pearson correlation coefficient: Given set of pairs of data $\{(x_i,y_i)\}_{i=1}^n$ the pearson correlation factor $r_{xy}$ is defined as,
+\begin{align}
+r_{xy}=\frac{\sum_{i=1}^n(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum_{i=1}^n(x_i-\bar{x}^2)}\sqrt{\sum_{i=1}^n(y_i-\bar{y}^2)}},
+\end{align}
+where $\bar{x}$ and $\bar{y}$ stand for the average value of ${x_i}_{i=1}^n$ and ${y_i}_{i=1}^n$ respectively.
+Note that $r_{xy}\in[-1,1]$.
+Therefore the sign of $r_{xy}$ is tightly related to the sign of alinear regression, more precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
+\end{definition}
+\begin{definition}\label{definitionTruePositiveRate}
+True Positive Rate: quantity related to a Machine Learning Model's sensitivity defined as:
+\begin{align}
+\frac{TP}{TP+FN}
+\end{align}
+where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
+\end{definition}
+
+\begin{definition}\label{definitionTrueNegativeRate}
+True Negative Rate: quantity related to a Machine Learning Model's specificity defined as:
+\begin{align}
+\frac{TN}{TN+FN}
+\end{align}
+where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
+\end{definition}
+
+\begin{definition}\label{definitionClassificationAccuracy}
+Classification Accuracy: quantity related to a Machine Learning Model's efectiveness defined as:
+\begin{align}
+\frac{TP+TN}{TP+FP+TN+FN}
+\end{align}
+where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
+\end{definition}
+
+\begin{definition}\label{definitionMatthewsCorrelationCoeficient}
+Matthews Correlation Coefficient: quantity related to a Machine Learning Model's prediction capacity defined as:
+{\scriptsize
+\begin{align}
+\frac{(TP\times TN)-(FP\times FN)}{\sqrt{(TP+FP)\times(TP+FN)\times(TN+FP)\times(TN+FN)}}
+\end{align}
+}where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
+A Matthews Correlation Coefficient equal to 1 stands for a perfect prediction a Matthews Correlation Coefficient equal to 0 indicates that the classifier’s predictions are no better than random guessing, and a Matthews Correlation Coefficient equal to -1 stand for a total disagreement between predictions and actual outcomes.
+\end{definition}
 \end{multicols}
-
 \end{document}

### 2025-02-19 Manuscript/manuscript.tex
Computing Models Statistics

@@
 \par
-With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $10^4$ descriptors per molecule.
+With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule.
+Still, by deleting molecular descriptors with null values 2917 remain.
 Here, the Pearson correlation coefficient between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
@@
 At this stage, the average $IC_{50}$ is calculated, and the neighborhood size corresponding to the percentage defined by the hard-coded variable \emph{percentageErased} is removed.
-This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}—those with lower and higher $IC_{50}$ values, respectively.
+This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}, those with lower and higher $IC_{50}$ values, respectively.
 Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} and a \emph{testing set}, following the proportion specified by the hard-coded variable \emph{testSizeProportion}.
@@
 \begin{multicols}{2}
-Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google.
+Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others.
 This algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets.

### 2025-02-19 Scripts/DataFilterAndPlotsMacro.py

@@ -80,7 +80,7 @@ def ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty, lowerTargetPropert
     
     # ploting the correlation factors histogram
     if not silentMode: print(f"Ploting the correlation factors in ../Plots/{targetIDChEMBL}{dataFileName}CorrelationFactors.pdf")
-    plt.hist(correlationDataFrame, bins=40, color='purple', range = (-1,1), label=f"Number of descriptors {dataFiltered.shape[1]-1}")
+    plt.hist(correlationDataFrame, bins=100, color='purple', range = (-1,1), label=f"Number of descriptors {dataFiltered.shape[1]-1}")
     plt.title('Correlation factors of the computed chemical descriptors')
     plt.xlabel('Correlation Values')
     plt.ylabel('Frequency')
@@ -101,8 +101,8 @@ def ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty, lowerTargetPropert
     dataWithGapUpper = dataFiltered[dataFiltered['standard_value'] >= iSplitValueUpper].copy()
 
     # Assigning activity labels: low = 0, high = 1
-    dataWithGapUnder['activity_label'] = 0
-    dataWithGapUpper['activity_label'] = 1
+    dataWithGapUnder.insert(1,'activity_label', 0)
+    dataWithGapUpper.insert(1,'activity_label',1)
 
     # Combining the two datasets into one with the gap
     dataWithGapAll = pd.concat([dataWithGapUnder, dataWithGapUpper], ignore_index=True)
@@ -154,10 +154,10 @@ def ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty, lowerTargetPropert
 
     # Gathering up all the data (Features+Labels) and reseting the indexs
     dataWithGapAllTrain                   = dataWithGapAllFeaturesTrain
-    dataWithGapAllTrain['activity_label'] = dataWithGapAllLabelsTrain
+    dataWithGapAllTrain.insert(1,'activity_label', dataWithGapAllLabelsTrain)
     dataWithGapAllTrain.reset_index(drop = True, inplace = True)
     dataWithGapAllTest                    = dataWithGapAllFeaturesTest
-    dataWithGapAllTest['activity_label']  = dataWithGapAllLabelsTest
+    dataWithGapAllTest.insert(1,'activity_label', dataWithGapAllLabelsTest)
[…]

### 2025-02-19 Scripts/Main.py

@@ -18,7 +18,7 @@ mode = 'DEFAULT'
 
 ChEMBLDataExtractorMacro.ChEMBLExtractData(config[mode]['targetIDChEMBL'], config[mode]['targetProperty'])
 
-dataFile = DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(config[mode]['targetIDChEMBL'], 
+dataFile, meanStandardValue = DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(config[mode]['targetIDChEMBL'], 
                                                              config[mode]['targetProperty'],
                                                              int(config[mode]['lowerTargetProperty']), 
                                                              int(config[mode]['higherTargetProperty']), 
@@ -30,4 +30,4 @@ dataFile = DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(config[mode]['targe
                                                              float(config[mode]['correlationLimitValue']))
 
 RandomForest.RandomForest(dataFile, int(config[mode]['numberOfTrees']), float(config[mode]['percentageErased']), 
-                          float(config[mode]['testSizeProportion']), float(config[mode]['correlationLimitValue']))
+                          float(config[mode]['testSizeProportion']), float(config[mode]['correlationLimitValue']), meanStandardValue)

### 2025-02-19 Scripts/RandomForest.py

@@ -12,9 +12,10 @@ from sklearn.model_selection import train_test_split
 from sklearn.ensemble import RandomForestRegressor
 from sklearn.metrics import mean_squared_error, r2_score
 import pickle
+import numpy as np
 
 # Importing the desired files
-def RandomForest(dataFileName, NumberOfTrees, percentatgeErased, splitPercentatge, minimumCorrelationFactor, silentMode = False):
+def RandomForest(dataFileName, NumberOfTrees, percentatgeErased, splitPercentatge, minimumCorrelationFactor, SplitStandardValue, silentMode = False):
     # Importing the data 
     TrainingDataFrame = pd.read_feather(f"{dataFileName}Train.feather")
     TestingDataFrame  = pd.read_feather(f"{dataFileName}Train.feather")
@@ -23,9 +24,9 @@ def RandomForest(dataFileName, NumberOfTrees, percentatgeErased, splitPercentatg
     PredictedDataFrame = TestingDataFrame[['canonical_smiles','standard_value']].copy()
 
     # Adapting the data to the "RandomForest" format
-    ChemDescriptorsTraining     = TrainingDataFrame.drop(['standard_value','canonical_smiles'], axis=1)
+    ChemDescriptorsTraining     = TrainingDataFrame.drop(['standard_value', 'activity_label', 'canonical_smiles'], axis=1)
     InhibitionPotentialTraining = TrainingDataFrame['standard_value']
-    ChemDescriptorsTesting      = TestingDataFrame.drop(['standard_value','canonical_smiles'], axis=1)
+    ChemDescriptorsTesting      = TestingDataFrame.drop(['standard_value', 'activity_label', 'canonical_smiles'], axis=1)
     InhibitionPotentialTesting  = TestingDataFrame['standard_value']
     
     # Generating the Random Forest object
@@ -40,6 +41,27 @@ def RandomForest(dataFileName, NumberOfTrees, percentatgeErased, splitPercentatg
     
     # Adding the results to the 'PredictedDataFrame'
     PredictedDataFrame["PredictedValues"] = InhibitionPotentialPredicted
+    PredictedDataFrame["activity_label"]  = TestingDataFrame['activity_label']
+
+    # Computing the average 'predicted_activity_label'
+    MeanStandardValue = PredictedDataFrame["standard_value"].mean()
+    PredictedDataFrame['predicted_activity_label'] = (PredictedDataFrame['PredictedValues'] > SplitStandardValue).astype(int)
+
[…]

### 2025-02-19 Scripts/Testing.py

@@ -1,22 +1,0 @@
-########################################################################################################
-#                                                                                                      #
-#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
-#  Author:   Sergio Castañeiras Morales                                                                #
-#  Date:     02/10/2024                                                                                #
-#  Purpose:  Import molecule's data with a known property activity respect a certain protein           #
-#            (i.e, COX-2)                                                                              #
-#                                                                                                      #
-########################################################################################################
-import requests
-
-# Test query URL
-queryURL = "https://www.ebi.ac.uk/chembl/api/data/activity.json?target_chembl_id=CHEMBL4523964&standard_type=IC50&limit=5"
-
-response = requests.get(queryURL)
-
-if response.status_code == 200:
-    data = response.json()
-    print("Response keys:", data.keys())  # Check top-level keys
-    print("\nExample data:\n", data)  # Print full response (first few entries)
-else:
-    print("Request failed with status code:", response.status_code)

### 2025-02-26 Manuscript/manuscript.tex
Adding all photoswitches schemes

@@
 \usepackage{tikz}
+\usepackage{chemformula}
 \usepackage{forest}
@@
 \chemfig[angle increment=30]{
-H_2N-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
+H_2N-[1]S(=[4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
 }}
@@
 \end{definition}
+
+\section{Tables of molecules}
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-R_1)-(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))=-))=-=)
+}}
+\caption{Template for Celecoxib's azo-derivates with pyrazole as heterocycle.}
+\label{figureCelecoxibPyrazole}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with pyrazole as heterocycle}
+\label{tableCelecoxibPyrazole}
+\begin{tabular}{c||c|c|c}
+Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
+\ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & \ch{OCH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & \ch{OCH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.7 & \ch{H} & \ch{CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3}  & \ch{H}\\\hline
+\ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3}  & \ch{F}\\\hline
+\ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3}  & \ch{F}
+\end{tabular}
+\end{table}
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemname{\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
+}}{Pyridine derivative}}
+\par
+\vspace{0.5cm}
+\scalebox{0.8}{
+\chemname{\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
+}}{\ch{SO_2CH_3} group derivative}}
+\caption{Scheme for Celecoxib azo-derivatives based on pyridine and \ch{SO_2CH_3} groups.}
+\label{tableCelecoxibPyridine}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-O-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with furan as a heterocycle.}
+\label{figureCelecoxibFuran}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with furan as heterocycle.}
+\label{tableCelecoxibFuran}
+\begin{tabular}{c||c|c}
+Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
+\ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} \\\hline
+\ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} \\\hline
+\ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} \\\hline
+\ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} \\\hline
+\ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} \\\hline
+\ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} \\\hline
+\ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} \\\hline
+\ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} \\\hline
+\ref{figureCelecoxibFuran}.9 & \ch{F} & \ch{F} \\\hline
+\ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} \\\hline
+\ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} \\\hline
+\ref{figureCelecoxibFuran}.12 & \ch{CH_3} & \ch{F}
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-S-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with thiophene as a heterocycle.}
+\label{figureCelecoxibThiophene}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with thiophene as heterocycle.}
+\label{tableCelecoxibFuran}
+\begin{tabular}{c||c|c}
+Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
+\ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} \\\hline
+\ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} \\\hline
+\ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} 
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))-=))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with pyrrole as a heterocycle.}
+\label{figureCelecoxibPyrrole}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with pyrrole as heterocycle.}
+\label{tableCelecoxibPyrrole}
+\begin{tabular}{c||c|c|c}
+Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
+\ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} \\\hline
+\ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} 
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*6(-=(-R_1)-(-N=[2]N-[4]*6(-=-(-R_2)=-=))=-=))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with benzene in place of the original heterocycle.}
+\label{figureCelecoxibBenzene}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with benzene in place of the original heterocycle.}
+\label{tableCelecoxibBenzene}
+\begin{tabular}{c||c|c}
+Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
+\ref{figureCelecoxibBenzene}.1 & \ch{CF_3} & \ch{CH_2CH_3} \\\hline
+\ref{figureCelecoxibBenzene}.2 & \ch{CF_3} & \ch{NCH_3COCH_3} \\\hline
+\ref{figureCelecoxibBenzene}.3 & \ch{CF_3} & \ch{NHCH_3} \\\hline
+\ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} \\\hline
+\ref{figureCelecoxibBenzene}.5 & \ch{Cl} & \ch{CH_3} 
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-*6(-=-(-)=(-[3]N=[4.5]N-[6]*6(-=-(-R_1)=-=))-=)--=))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with indole ring as a heterocycle.}
+\label{figureCelecoxibIndole}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with indole ring as a heterocycle.}
+\label{tableCelecoxibIndole}
+\begin{tabular}{c||c}
+Identifier & \ch{R_1}  \\\hline\hline
+\ref{figureCelecoxibIndole}.1 & \ch{H} \\\hline
+\ref{figureCelecoxibIndole}.1 & \ch{F} 
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.7}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-\chembelow{N}{H}-*6(-=-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with indole ring as a heterocycle.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\scalebox{0.7}{
+\chemfig[angle increment=30]{
+NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-R_1-*5(-R_2-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives with two rings of five members joint as a heterocycle.}
+\label{figureCelecoxibTwoRings}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with indole ring as a heterocycle.}
+\label{tableCelecoxibTwoRings}
+\begin{tabular}{c||c|c|c}
+Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
+\ref{figureCelecoxibTwoRings}.1 & \ch{NH} & \ch{NH} & \ch{H} \\\hline
+\ref{figureCelecoxibTwoRings}.2 & \ch{NH} & \ch{O} & \ch{H} \\\hline
+\ref{figureCelecoxibTwoRings}.3 & \ch{O} & \ch{NH} & \ch{H} \\\hline
+\ref{figureCelecoxibTwoRings}.4 & \ch{O} & \ch{O} & \ch{H} \\\hline
+\ref{figureCelecoxibTwoRings}.5 & \ch{NH} & \ch{NH} & \ch{CH_3} \\\hline
+\ref{figureCelecoxibTwoRings}.6 & \ch{NH} & \ch{O} & \ch{CH_3} \\\hline
+\ref{figureCelecoxibTwoRings}.7 & \ch{O} & \ch{NH} & \ch{CH_3} \\\hline
+\ref{figureCelecoxibTwoRings}.8 & \ch{O} & \ch{O} & \ch{CH_3}
+\end{tabular}
+\end{table}
+
 \end{multicols}

### 2025-02-26 Scripts/Predictor.py

@@ -1,0 +1,69 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     25/02/2024                                                                                #
+#  Purpose:  Predict the IC_50 value of a given molecule using a previous model and the smiles file    #
+#                                                                                                      #
+########################################################################################################
+
+import pandas as pd
+import os
+import configparser
+from alvadesccliwrapper.alvadesc import AlvaDesc
+import pickle
+
+config   = configparser.ConfigParser()
+config.read('config.ini')
+mode     = 'DEFAULT'
+aDesc    = AlvaDesc(config[mode]['AlvaDescPath'])
+fileName = "Benzene"
+filePath = f"../SmilesFiles/{fileName}.smiles"
+outputDataList = []
+
+if not os.path.exists(filePath):
+    raise ValueError(f"The given file does not exist: {filePath}")
+
+with open(filePath, 'r') as smilesFile:
+    smilesList = smilesFile.read().splitlines()
+
+
+for iSmile in smilesList:
+    aDesc.set_input_SMILES(iSmile)
+    
+    if not aDesc.calculate_descriptors("ALL"):
+        print('Error: ' + aDesc.get_error())
+        pass
+    
+    outputDescriptors     = aDesc.get_output_descriptors()
+    outputValues          = aDesc.get_output()[0]
+    descriptorsDictionary = {'canonical_smiles' : iSmile} 
+    for iDescriptor in range(len(outputDescriptors)):
+        descriptorsDictionary[outputDescriptors[iDescriptor]] = outputValues[iDescriptor]
+    outputDataList.append(descriptorsDictionary)
+
+predictingDataFrame = pd.DataFrame(outputDataList)
+predictingDataFrame.fillna(0,inplace = True)
+
+if not os.path.exists(f"../Data/ChEMBL_ExtractorData_{config[mode]['targetIDChEMBL']}_{config[mode]['targetProperty']}_1000Descriptors.feather"):
[…]

### 2025-02-26 Scripts/RandomForest.py

@@ -44,7 +44,6 @@ def RandomForest(dataFileName, NumberOfTrees, percentatgeErased, splitPercentatg
     PredictedDataFrame["activity_label"]  = TestingDataFrame['activity_label']
 
     # Computing the average 'predicted_activity_label'
-    MeanStandardValue = PredictedDataFrame["standard_value"].mean()
     PredictedDataFrame['predicted_activity_label'] = (PredictedDataFrame['PredictedValues'] > SplitStandardValue).astype(int)
 
     # Analising some statistics

### 2025-03-01 Manuscript/manuscript.tex
Adding avogadro molecules

@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-R_1)-(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))=-))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-R_1)-(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))=-))=-=)
 }}
@@
 \chemname{\chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
 }}{Pyridine derivative}}
@@
 \chemname{\chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
+H_3C-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
 }}{\ch{SO_2CH_3} group derivative}}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-O-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-O-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
 }}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-S-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-S-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
 }}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))-=))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))-=))=-=)
 }}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*6(-=(-R_1)-(-N=[2]N-[4]*6(-=-(-R_2)=-=))=-=))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*6(-=(-R_1)-(-N=[2]N-[4]*6(-=-(-R_2)=-=))=-=))=-=)
 }}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-*6(-=-(-)=(-[3]N=[4.5]N-[6]*6(-=-(-R_1)=-=))-=)--=))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-*6(-=-(-)=(-[3]N=[4.5]N-[6]*6(-=-(-R_1)=-=))-=)--=))=-=)
 }}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-\chembelow{N}{H}-*6(-=-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-\chembelow{N}{H}-*6(-=-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
 }}
@@
 \chemfig[angle increment=30]{
-NH_2-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-R_1-*5(-R_2-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-R_1-*5(-R_2-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
 }}

### 2025-03-05 Scripts/DataFilterAndPlotsMacro.py
Pretty predictions

@@ -73,26 +73,27 @@ def ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty, lowerTargetPropert
         dataImported  = pd.read_feather(dataFilePath + dataFileName + ".feather")
         standardUnits = dataImported['standard_units'].iloc[0]
     
-    # Computing the correlation coefficients with the selected method
-    if not silentMode: print("Computing the correlation coefficients using", correlationMethod, "method")
-    correlationDataFrame = (dataFiltered.drop('canonical_smiles', axis = 1)).corr(method = correlationMethod)['standard_value']
-    if not silentMode: print("Deleting descriptors with correlation factors below ", correlationLimitValue)
-    
-    # ploting the correlation factors histogram
-    if not silentMode: print(f"Ploting the correlation factors in ../Plots/{targetIDChEMBL}{dataFileName}CorrelationFactors.pdf")
-    plt.hist(correlationDataFrame, bins=100, color='purple', range = (-1,1), label=f"Number of descriptors {dataFiltered.shape[1]-1}")
-    plt.title('Correlation factors of the computed chemical descriptors')
-    plt.xlabel('Correlation Values')
-    plt.ylabel('Frequency')
-    plt.legend()
-    plt.savefig(f"../Plots/{dataFileName}CorrelationFactors.pdf", format = 'pdf')
-    plt.close()
+    if correlationLimitValue != 0:
+        # Computing the correlation coefficients with the selected method
+        if not silentMode: print("Computing the correlation coefficients using", correlationMethod, "method")
+        correlationDataFrame = (dataFiltered.drop('canonical_smiles', axis = 1)).corr(method = correlationMethod)['standard_value']
+        if not silentMode: print("Deleting descriptors with correlation factors below ", correlationLimitValue)
+        
+        # ploting the correlation factors histogram
+        if not silentMode: print(f"Ploting the correlation factors in ../Plots/{targetIDChEMBL}{dataFileName}CorrelationFactors.pdf")
+        plt.hist(correlationDataFrame, bins=100, color='purple', range = (-1,1), label=f"Number of descriptors {dataFiltered.shape[1]-1}")
+        plt.title('Correlation factors of the computed chemical descriptors')
+        plt.xlabel('Correlation Values')
+        plt.ylabel('Frequency')
+        plt.legend()
+        plt.savefig(f"../Plots/{dataFileName}CorrelationFactors.pdf", format = 'pdf')
[…]

### 2025-03-05 Scripts/Predictor.py

@@ -12,23 +12,25 @@ import os
 import configparser
 from alvadesccliwrapper.alvadesc import AlvaDesc
 import pickle
+from tqdm import tqdm 
 
 config   = configparser.ConfigParser()
 config.read('config.ini')
 mode     = 'DEFAULT'
 aDesc    = AlvaDesc(config[mode]['AlvaDescPath'])
-fileName = "Benzene"
+fileName = "providedSmiles"
 filePath = f"../SmilesFiles/{fileName}.smiles"
 outputDataList = []
 
-if not os.path.exists(filePath):
+DataFramePath = f"../SmilesFiles/{fileName}.feather"
+if not os.path.exists(DataFramePath):
     raise ValueError(f"The given file does not exist: {filePath}")
 
-with open(filePath, 'r') as smilesFile:
-    smilesList = smilesFile.read().splitlines()
+importedDataFrame = pd.read_feather(DataFramePath)
 
+smilesList = importedDataFrame['canonical_smiles']
 
-for iSmile in smilesList:
+for iSmile in tqdm(smilesList,"Computating molecule's descriptors"):
     aDesc.set_input_SMILES(iSmile)
     
     if not aDesc.calculate_descriptors("ALL"):
@@ -53,17 +55,20 @@ computedpredictingDataFrame = pd.read_feather(f"../Data/ChEMBL_ExtractorData_{co
 predictingDataFrame = predictingDataFrame.loc[:, predictingDataFrame.columns.isin(computedpredictingDataFrame.columns)]
 
 
-if not os.path.exists(f"../MachineLearningModels/RandomForestChEMBL_ExtractorData_{config[mode]['targetIDChEMBL']}_{config[mode]['targetProperty']}_1000min_{config[mode]['lowerTargetProperty']}max_{config[mode]['higherTargetProperty']}FilteredGap_min_43Gap_max_43_Trees{config[mode]['numberOfTrees']}.pkl"):
-    raise ValueError(f"The given file does not exist: ../MachineLearningModels/RandomForestChEMBL_ExtractorData_{config[mode]['targetIDChEMBL']}_{config[mode]['targetProperty']}_1000min_{config[mode]['lowerTargetProperty']}max_{config[mode]['higherTargetProperty']}FilteredGap_min_43Gap_max_43_Trees{config[mode]['numberOfTrees']}.pkl")
[…]

### 2025-03-05 Scripts/testin.py

@@ -1,0 +1,61 @@
+import numpy as np
+import pandas as pd
+dictionary = [
+    {'Type': 'Pyrazole', 'Number': 1, 'R_1': 'CF_3', 'R_2': 'CH_2CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)CC)C(F)(F)F'},
+    {'Type': 'Pyrazole', 'Number': 2, 'R_1': 'CF_3', 'R_2': 'CH_2CH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)CC)C(F)(F)F'},
+    {'Type': 'Pyrazole', 'Number': 3, 'R_1': 'CF_3', 'R_2': 'CH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)C)C(F)(F)F'},
+    {'Type': 'Pyrazole', 'Number': 4, 'R_1': 'CF_3', 'R_2': 'OCH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)OC)C(F)(F)F'},
+    {'Type': 'Pyrazole', 'Number': 5, 'R_1': 'CF_3', 'R_2': 'OCH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)OC)C(F)(F)F'},
+    {'Type': 'Pyrazole', 'Number': 6, 'R_1': 'CF_3', 'R_2': 'CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)C)C(F)(F)F'},
+    {'Type': 'Pyrazole', 'Number': 7, 'R_1': 'H', 'R_2': 'CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1ncc(c1)/N=N/c1ccc(cc1)C'}, 
[…]

### 2025-03-08 Manuscript/manuscript.tex
Adding all smiles
Pretty predictions
Changing the Figures labels to Schemes

@@
 \useunder{\uline}{\ul}{}
+
+\usepackage{caption}
+\DeclareCaptionType{scheme}
 
@@
 \begin{definition}\label{definitionCelecoxib}
-Celecoxib: \footnote{UPAC name: 4-[5-(4-Methylphenyl)-3-(trifluoromethyl)pyrazol-1-yl]benzenesulfonamide} drug known to be a selective COX-2 inhibitor (currently is not \emph{highly selective} respect to newer drugs), see Figure (\ref{CelecoxibFigure}).
+Celecoxib: \footnote{UPAC name: 4-[5-(4-Methylphenyl)-3-(trifluoromethyl)pyrazol-1-yl]benzenesulfonamide} drug known to be a selective COX-2 inhibitor (currently is not \emph{highly selective} respect to newer drugs), see Scheme (\ref{CelecoxibFigure}).
 It $IC_{50}$ value is $120$ nM.
@@
 \begin{definition}\label{definitionRofecoxib}
-Rofecoxib: \footnote{UPAC name: 4-(4-methylsulfonylphenyl)-3-phenyl-5H-furan-2-one} drug known to be a selective COX-2 inhibitor, see Figure (\ref{RofecoxibFigure}). It $IC_{50}$ value is $180$ nM.
+Rofecoxib: \footnote{UPAC name: 4-(4-methylsulfonylphenyl)-3-phenyl-5H-furan-2-one} drug known to be a selective COX-2 inhibitor, see Scheme (\ref{RofecoxibFigure}). It $IC_{50}$ value is $180$ nM.
 \end{definition}
@@
 \begin{figure}[H]
+\captionsetup{type=scheme}
 \centering
@@
 \caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with thiophene as heterocycle.}
-\label{tableCelecoxibFuran}
+\label{tableCelecoxibThiophene}
 \begin{tabular}{c||c|c}
@@
 \ref{figureCelecoxibIndole}.1 & \ch{H} \\\hline
-\ref{figureCelecoxibIndole}.1 & \ch{F} 
+\ref{figureCelecoxibIndole}.2 & \ch{F} 
 \end{tabular}
@@
 \chemfig[angle increment=30]{
-H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-R_1-*5(-R_2-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-R_1-*5(-R_2-(-)=(-*6(-=-(-R_3)=-=))-=)--))=-=)
 }}
@@
 \centering
-\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with indole ring as a heterocycle.}
+\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with two rings of five members joint as a heterocycle.}
 \label{tableCelecoxibTwoRings}

### 2025-03-21 Manuscript/Plantilla memòria TFG 2024_25.tex
Plantilla chula rechula

--- 2025-03-08 Manuscript/manuscript.tex
@@
-\documentclass[12pt,letterpaper]{article}
-% \documentclass[journal=acsomega,manuscript=article]{achemso}
+\documentclass[11pt]{article}
+\usepackage[utf8]{inputenc}
+%----------FONT AND GEOMETRY DEFINITION----------%
+\usepackage[a4paper, hmargin=3.0cm, vmargin=3.0cm]{geometry}
+\voffset = -0.75cm
+\usepackage{arev}
+\usepackage{helvet}
+\renewcommand{\rmdefault}{\sfdefault}
+\usepackage[math]{blindtext}
+%---------SPACING----------%
+\usepackage{setspace}
+\setstretch{1.5}
+
+\usepackage[english]{babel}
+
+%-------------LINKS AND LOOKS-----------%
 \usepackage{fullpage}
-\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
-\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
+\usepackage{afterpage}
 \usepackage{lastpage}
-\usepackage{enumerate}
 \usepackage{fancyhdr}
-\usepackage{mathrsfs}
 \usepackage{graphicx}
-\usepackage{listings}
+\usepackage{xcolor}
 \usepackage{hyperref}
-\usepackage[english]{babel}
-\usepackage{lipsum}
-\usepackage[table,xcdraw]{xcolor}
-\usepackage{enumitem}
-\usepackage{pgfplots}
-\usepackage{float}
-\usepackage{chemfig}
-\usepackage{yfonts}
-\usepackage{tikz}
-\usepackage{chemformula}
-\usepackage{forest}
-\usepackage{pdflscape}
-\usepackage{wrapfig}
-\usepackage{url}
-\usepackage[normalem]{ulem}
-\usepackage{multicol}
-\useunder{\uline}{\ul}{}
-
+\hypersetup{%
+  colorlinks=false,
+  linkcolor=black,
+  linkbordercolor={1.0 1.0 1.0},
+  breaklinks = true,
+  citebordercolor={1.0 1.0 1.0},
+  hidelinks = true,
+}
+\usepackage{xurl}
+%-----------------FIGURES AND TABLES----------------%
+\usepackage{array}
+%\usepackage{wrapfig}
 \usepackage{caption}
 \DeclareCaptionType{scheme}
+%\usepackage{subcaption}
+\usepackage{tabularx, booktabs, makecell, multicol, multirow, bigstrut} %for excel2latex
+\usepackage{float}
 
-%%%%%%%%%%%%%%% CODELISTINGS %%%%%%%%%%%%%%%%
-\usepackage{listings}
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+%-----------------CHEMICAL FIGURES AND FORMULAS--------------------%
+\usepackage{chemfig}
+\usepackage{chemformula}
 
-\lstdefinestyle{mystyle}{
-    backgroundcolor=\color{backcolour}, 
-    commentstyle=\color{codegreen},
-    keywordstyle=\color{magenta},
-    numberstyle=\tiny\color{codegray},
-    stringstyle=\color{codepurple},
-    basicstyle=\ttfamily\footnotesize,
-    breakatwhitespace=false,         
-    breaklines=true,                 
-    captionpos=t,                    
-    keepspaces=true,                 
-    numbers=left,                    
-    numbersep=5pt,                  
-    showspaces=false,                
-    showstringspaces=false,
-    showtabs=false,                  
-    tabsize=2
+%----------BIBLIOGRAPHY----------%
+%file with extnsion .bib is required (generated by Mendeley for example) called references in the folder where the .tex file is compiled
+\usepackage[backend=bibtex, style = chem-acs]{biblatex}
+\usepackage{csquotes}
+%in case of writing the thesis in catalan or spanish:
+%\usepackage[autostyle=false, style=spanish]{csquotes}
+
+% check out the document types in the .bib file that biblatex can cite in: https://mirror.las.iastate.edu/tex-archive/macros/latex/contrib/biblatex-contrib/biblatex-chem/chem-acs.bbx
+
+%---max amount of bibliography names
+\ExecuteBibliographyOptions{maxnames=10}
+%----
+%-----article issue between parenthesis after the volume number - citation style modification
+\DeclareFieldFormat[article]{issue}{\mkbibparens{#1}}
+\renewbibmacro*{volume+number+eid}{%
+  \printfield{volume}%
+  \setunit{\space}%
+  \printfield{issue}%
+  \setunit{\addcomma\space}%
+  \printfield{eid}}
+%---------------------------------------------------------
+\addbibresource{references.bib}
+
+%----------TITLE AND PAGE FORMATTING----------%
+\newcommand\NomComplet{Sergio Castañeiras Morales}
+\newcommand\NIU{1598456}
+\newcommand\NomProfeA{Dr. Miquel Moreno Ferrer}
+\newcommand\NomProfeB{Dr. Àngels Gonzalez Lafont}
+\newcommand\CodiTFG{TFG2425\_045}
+\newcommand\TitolTFG{AI Application for Azophotoswitches Optimization with Pharmacological Interest}
+\newcommand\NomCentre{Departament de Quimica } %cal posar un espai al final
+\newcommand\NomGrau{Quimica}
+\newcommand\Mes{Juny } %cal espai al final
+\newcommand\Any{2025}
+
+\fancypagestyle{sumari}{
+\fancyhf{}
+\rhead{\TitolTFG}
+\renewcommand{\headrulewidth}{0pt}%
+\renewcommand{\footrulewidth}{0pt}%
 }
 
-\lstset{style=mystyle}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage{achemso}
-% \bibliographystyle{achemso}
-
-\usepackage{titlesec}
-\titleformat{\section}[block]{\normalfont\normalsize\bfseries\centering}{\thesection}{1em}{} % changing the "section" fontsize and centering it
-\renewcommand{\thesection}{\Roman{section}}  % Roman numerals for section numbers
-
-\newtheorem{definition}{Definition}
-\newtheorem{observation}{Observation}
-\newtheorem{reflection}{Reflection}
-\newtheorem{PyPackage}{Package}
-\newtheorem{book}{Book}
-
-\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
-\setcounter{tocdepth}{5}
-\setcounter{secnumdepth}{5}
-
-\setlength{\parindent}{0.0in}
-\setlength{\parskip}{0.05in}
-
-% Edit these as appropriate
-\newcommand\course{}
-\newcommand\subject{Final Degree Project}
-\newcommand\degree{Bachelor's Degree in Chemistry}
-\newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
-\newcommand\NetIDb{Universitat Autònoma de Barcelona}
-
-\begin{document}
-\title{\vspace{4cm} \normalsize 
-		\includegraphics[width = 0.25\textwidth]{GeneralSources/UABLogo.png}\\ [0.5cm]
-		\textsc{\NetIDb}\\ [2.0cm]
-		\HRule{0.5pt} \\
-		\LARGE \textbf{\uppercase{\documenttitle}}
-		\HRule{2pt} \\ [1.5cm]
-		\normalsize \begin{tabular}{rcl}  % Create a right-left column alignment
-        \textsc{Author} & : & \textsc{Sergio Castañeiras Morales} \\
-        \textsc{Supervisor} & : & \textsc{Miquel Moreno Ferrer} \\
-        \textsc{Co-Supervisor} & : & \textsc{Àngels Gonzalez Lafont}
-    \end{tabular}
-    \normalsize \vspace*{5\baselineskip}
+\fancypagestyle{afteres}{
+\fancyhf{}
+\headheight 0 cm
+\headsep 1.725cm
+\rhead{\TitolTFG}
+\cfoot{\thepage}
+\renewcommand{\headrulewidth}{0pt}%
+\renewcommand{\footrulewidth}{0pt}%
 }
 
-\date{2024-2025}
+\pagestyle{fancy}
+\fancyhf{}
+\headheight 0 cm
+\headsep 1.725cm
+\rhead{\TitolTFG}
+\cfoot{\thepage}
+\renewcommand{\headrulewidth}{0pt}%
+\renewcommand{\footrulewidth}{0pt}%
 
-\author{\large \textsc{\subject} \\ \textsc{\degree}}
+%----------ABBREVIATIONS LIST----------%
+\usepackage{glossaries}
+\usepackage{glossary-longragged}
 
+\makenoidxglossaries
+
+\newacronym{cox1}{COX-1}{Cyclooxygenase-1}
+\newacronym{cox2}{COX-2}{Cyclooxygenase-2}
+\newacronym{ai}{AI}{Artificial intelligence}
+\newacronym{ml}{ML}{Machine Learning}
+\newacronym{rf}{RF}{Random Forest}
+\newacronym{id}{ID}{Identificator}
+\newacronym{ic50}{IC$_{50}$}{Half maximal inhibitory concentration}
+\newacronym{ic90}{IC$_{90}$}{90 percent inhibitory concentration}
+\newacronym{ic99}{IC$_{99}$}{99 percent inhibitory concentration}
+\newacronym{tp}{TP}{True Posive}
+\newacronym{fp}{FP}{False Posive}
+\newacronym{tn}{TN}{True Negative}
+\newacronym{fn}{FN}{False Negative}
+
+\glsaddall[types=\acronymtype] % to add all the acronyms, cited or not in the text
+
+%----------ENVIRONMENTS------------------%
+\newtheorem{definition}{Definition}
+
+%----------DOCUMENT COMPILATION----------%
+\begin{document}
+\newgeometry{bottom = 1cm}
 \begin{titlepage}
-\clearpage\maketitle
+
+\center % Center everything on the page
+
+%	LOGO SECTION
+%----------------------------------------------------------------------------------------
+
+\includegraphics[width = 6.1cm]{GeneralSources/Logo_uab.png}\\[1.76cm] % Include a department/university logo - this will require the graphicx package
+
+% TITLE SECTION
+%----------------------------------------------------------------------------------------
+
+\textbf{\LARGE Facultat de Ciències}\\[3.53cm] % Major heading such as course name
+%\rule{.1pt}{5cm}
+\begin{flushright}
+\begin{tabular}{r | p{.5\textwidth}}
+  {\Large Treball de} & {\LARGE \CodiTFG}\\
+  {\LARGE fi de grau}  & {\LARGE \TitolTFG}
+\end{tabular}
+\end{flushright}\vspace{5.06cm}
+
+%----------------------------------------------------------------------------------------
+%	AUTHOR SECTION
+%----------------------------------------------------------------------------------------
+
+\begin{tabular}{p{.48\textwidth} p{.48\textwidth}}
+\large
+Direcció: & Alumne: \\
+\NomProfeA & \NomComplet\\
+\NomProfeB & NIU: \\
+ & \NIU
+\end{tabular}
+\vspace{0.5cm}
+
+%----------------------------------------------------------------------------------------
+%	DATE SECTION
+%----------------------------------------------------------------------------------------
+
+{\Large \Mes \Any}\\[0.5cm] % Date, change the \today to a set date if you want to be precise
+
+%----------------------------------------------------------------------------------------
+Treball de fi de grau realitzat al \NomCentre i presentat a la\\ Facultat de Ciancies\\ de la Universitat Autnoma de Barcelona per a l'obtenció del Grau en \NomGrau
+
+%\vfill % Fill the rest of the page with whitespace
+
+\end{titlepage}
+\restoregeometry
+\pagenumbering{Roman}
+%\afterpage{\aftergroup\restoregeometry}
 \thispagestyle{empty}
-\end{titlepage}
-
-\newpage
-\thispagestyle{empty}
-\mbox{} 
+{\centering \textcolor{white}{This page is left blank intentionally}}
+\setcounter{page}{0}
 \newpage
@@
 \end{flushright}
-\vspace*{\fill} % Balance vertical spacing
+\vspace*{\fill} 
 \newpage
 
-\pagestyle{fancyplain}
-\headheight 35pt
-\lhead{\NetIDb}    
-\rhead{\subject}
-\cfoot{\small\thepage}
-\rfoot{}
-\headsep 1.5em
+\thispagestyle{afteres}
+\section*{Resum analític}
+La intel$\cdot$ligència artificial ha esat seguirà sent una de les majors revolucions del segle fins a l'actualitat.
+
+\newpage
+
+\section*{Resumen Analítico}
+
+blebleble
+
+\newpage
+
+\section*{Analytical abstract}
+
+bliblibli
+
+\newpage
+\thispagestyle{sumari}
+%\rhead{\TitolTFG}
+\tableofcontents{}
+
+\newpage
 \setcounter{page}{1}
-\begin{multicols}{2}[\begin{center}
-\begin{abstract}
-We explore AI-based algorithms capabilities, specifically the Random Forest model, to predict a drug’s inhibition potential for cyclooxygenase-2 (COX-2), a key protein linked to cancer.
-Using molecular descriptors extracted from the ChEMBL database, AI models are trained to identify patterns correlating with inhibition potential.
-The study validates AI’s effectiveness in drug discovery and molecular analysis, proving its potential as a powerful tool in computational chemistry research.
-\end{abstract}
-\end{center}
-Keywords: \emph{COX-2, cyclooxygenase-2, Random Forest, Machine Learning, AI, Artificial Intelligence}.
-]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%&%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagenumbering{arabic}
+\rhead{\TitolTFG}
+\section{List of abbreviations}
+\renewcommand{\glsnamefont}[1]{\textbf{#1}}
+\printnoidxglossary[type=main, title={\vspace{-1cm}}, nonumberlist, nogroupskip, style=super]%nonumberlist deletes the list of links in the index to every acronym listed.
+nogroupskip deletes the extra space between letter groups
+\newpage
+
 \section{Introduction}
-The impact of Artificial Intelligence (AI) on science has been nothing but an outstanding breakthrough, with few comparable predecessors.
-The rapid advancements in AI have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry.
+The impact of \gls{ai} on science has been nothing but an outstanding breakthrough, with few comparable predecessors.
+The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry.
 Nowadays, one of the main goals of computational chemistry is to predict certain properties of unstudied substances with minimal experimental costs\cite{AlphaFold2CommumityAssesment}.
 Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive and resource-intensive.
-On the other hand, AI algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception.
-AI provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.\par
+On the other hand, \gls{ai} algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception.
+\gls{ai} provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.\par
 
@@
 Around $10^4$ descriptors are calculated\cite{DescriptorsBookClassification}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
-The resulting dataset is subsequently used to train AI models, enabling them to predict the inhibition potential of unknown compounds.
+The resulting dataset is subsequently used to train \gls{ai} models, enabling them to predict the inhibition potential of unknown compounds.
 Finally, we evaluate the reliability of each model by testing it against real experimental data.
@@
 The lack of an ultimate proof underscores the need for advanced computational techniques.
-By analysing large datasets, AI can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par
+By analysing large datasets, \gls{ai} can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par
 
-At this stage, we focus on cyclooxygenase-2 (COX-2), a protein well known for its strong association with cancer development and inflammatory diseases\cite{DefinitionCOX2CancerDictionary}.
-COX-2 plays a crucial role in the biosynthesis of prostaglandins, which mediate inflammation and pain.
+At this stage, we focus on \gls{cox2}, a protein well known for its strong association with cancer development and inflammatory diseases\cite{DefinitionCOX2CancerDictionary}.
+\gls{cox2} plays a crucial role in the biosynthesis of prostaglandins, which mediate inflammation and pain.
 Overexpression of COX-2 has been linked to various types of cancer, making it a prime target for drug development.
-COX-2 inhibitors, such as Celecoxib (Def.
+\gls{cox2} inhibitors, such as Celecoxib (Def.
 \ref{definitionCelecoxib}) and Rofecoxib (Def.
 \ref{definitionRofecoxib}), have been widely studied for their therapeutic potential.
-The scientific community has devoted an extensive research to COX-2, even before the rise of AI, due to its biomedical significance\cite{Cox2InhibitorsReview}.
-By applying AI models to COX-2, we assess their compatibility with the latest research findings, demonstrating AI’s potential as a powerful tool in computational chemistry research.
+The scientific community has devoted an extensive research to \gls{cox2}, even before the rise of \gls{ai}, due to its biomedical significance\cite{Cox2InhibitorsReview}.
+By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings, demonstrating AI’s potential as a powerful tool in computational chemistry research.
 Our approach not only validates AI’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing COX-2 interactions.\par
 
-The AI algorithm used in this study is the Random Forest algorithm\cite{MachineLearningRandomForest}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
+The AI algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
 This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting.
@@
 Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.
+\newpage
+
+\section{Objectives}
+
+\newpage
 
@@
 This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
-\end{multicols}
 \begin{figure}[H]
@@
 \includegraphics[width = \textwidth]{GeneralSources/DataSplittingDiagram.pdf}
-\caption{Scheme of the splitting procedure.}
+\caption{Splitting and processing data's scheme.}
 \label{FigureDataSplittingDiagram}
 \end{figure}
-\begin{multicols}{2}
 Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results and Discussion}
 
-\bibliography{references} 
-%%%%%%%%
-\section{Abbreviation index}
-COX-2 : cyclooxygenase-2\par
-AI : Artificial Intelligence\par
-ML : Machine Learning\par
-RD : Random Forest\par
-ID : Identification\par
-$IC_{50}$: Half maximal inhibitory concentration \par
-$IC_{90}$: 90 percent inhibitory concentration \par
-$IC_{99}$: 99 percent inhibitory concentration \par
-TP: True Positive\par
-FP: False Positive\par
-TN: True Negative\par
-FN: False Negative
+\newpage
+
+\section{Conclusions}
+Hola \cite{BookIC50}
+\newpage
+
+\section{Bibliography}
+\printbibliography[title = { \vspace{-1cm}}]
+\newpage
+
 \appendix
@@
 }where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
-A Matthews Correlation Coefficient equal to 1 stands for a perfect prediction a Matthews Correlation Coefficient equal to 0 indicates that the classifier’s predictions are no better than random guessing, and a Matthews Correlation Coefficient equal to -1 stand for a total disagreement between predictions and actual outcomes.
+A Matthews Correlation Coefficient equal to 1 stands for a perfect prediction a Matthews Correlation Coefficient equal to 0 indicates the predictions are no better than random guessing, and a Matthews Correlation Coefficient equal to -1 stand for a total disagreement between predictions and actual outcomes.
 \end{definition}
@@
 
-\end{multicols}
 \end{document}

### 2025-03-23 Manuscript/Plantilla memòria TFG 2024_25.tex
Writting abstract ans some stuff

@@
 
-\newacronym{cox1}{COX-1}{Cyclooxygenase-1}
 \newacronym{cox2}{COX-2}{Cyclooxygenase-2}
+\newacronym{ptgs2}{PTGS2}{Prostaglandin-endoperoxide synthase 2}
 \newacronym{ai}{AI}{Artificial intelligence}
@@
 %----------------------------------------------------------------------------------------
-Treball de fi de grau realitzat al \NomCentre i presentat a la\\ Facultat de Ciancies\\ de la Universitat Autnoma de Barcelona per a l'obtenció del Grau en \NomGrau
+Treball de fi de grau realitzat al \NomCentre i presentat a la\\ Facultat de Ciancies\\ de la Universitat Autnòma de Barcelona per a l'obtenció del Grau en \NomGrau
 
@@
 \thispagestyle{empty}
-{\centering \textcolor{white}{This page is left blank intentionally}}
-\setcounter{page}{0}
+\mbox{} 
 \newpage
@@
 \thispagestyle{afteres}
-\section*{Resum analític}
-La intel$\cdot$ligència artificial ha esat seguirà sent una de les majors revolucions del segle fins a l'actualitat.
+\setcounter{page}{1}
+\section*{Resum analític}\par
+L'intel·ligència artificial es presenta com una de les revolucions del segle XXI.
+En particular, el sector de la química computacional està sent profundament sacsejat per aquesta revolució.
+Aprofitant la inèrcia i l'interès creixent en aquest camp, aquest treball pretén aplicar diferents models d'intel·ligència artificial en l'estudi d'una proteïna d'especial interès per a la nostra salut, la Ciclooxigenasa-2 (COX-2).
 
+La \emph{prostaglandin-endoperoxide sinthasa 2} (PTGS2), també coneguda com COX-2, és una proteïna que, en circumstàncies normals, acostuma a romandre inactiva \cite{Cox2Location}, llevat de la seva expressió durant processos inflamatoris.
+Així mateix, la manca de retorn a nivells baixos d'expressió després de la inflamació ha estat relacionada amb l'aparició de diferents formes de càncer \cite{DefinitionCOX2CancerDictionary}.
+Aquest fet ha convertit la COX-2 en objecte d'estudi de nombroses investigacions científiques \cite{Cox2InhibitorsReview}, fet que la fa un punt de partida idoni per al desenvolupament d'algoritmes de \emph{Machine Learning}, ja que disposa d'una gran quantitat de dades per entrenar els models i contrastar els resultats.
+
+L'objectiu principal del projecte és el desenvolupament d'un programari generador d'IAs capaces de predir la concentració d'inhibició al 50\% (IC$_{50}$) per a la COX-2\footnote{En realitat, el programari funciona per a qualsevol proteïna amb entrada a la base de dades de ChEMBL \cite{ChemblDatabase}, malgrat que l'objecte d'estudi és la COX-2.} amb la màxima precisió possible.
+Per fer-ho, s'extreuen totes les dades de molècules conegudes amb un potencial d'inhibició establert per a la COX-2.
+Després d'un filtratge configurable per l'usuari, es calculen 5.900 descriptors químics per a cadascuna de les entrades amb el programari AlvaDesk \cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper}.
+Seguidament, una part de les dades s'utilitza per entrenar models de \emph{Random Forest} (RF) \cite{MachineLearningRandomForest}, mentre que la resta es reserva per validar la precisió de les prediccions.
+
+Cal remarcar la principal hipòtesi que sustenta aquest procés i el projecte en general: \emph{Existeix una combinació (o diverses combinacions) de descriptors químics directament relacionada amb el potencial d'inhibició de la proteïna}.
+Malgrat que aquesta afirmació pugui semblar natural, el cost computacional associat és immens.
+Tot i així, la precisió de les prediccions dels models apunta a la validesa d'aquesta hipòtesi, si bé continua essent una conjectura per manca d'una prova definitiva.
+
+Finalment, els models es fan servir per predir l'IC$_{50}$ de 50 \emph{azophotoswitches} dels quals es tenen dades sobre l'energia lliure d'acoblament proporcionades pel Departament de Química Computacional de la UAB \cite{UAB_ComputationalChemistry}.
+L'anàlisi estadístic de les prediccions reflecteix una clara correlació entre ambdues quantitats, fet que reforça la hipòtesi del projecte.
 \newpage
 
-\section*{Resumen Analítico}
+\section*{Resumen analítico}
+La inteligencia artificial se presenta como una de las revoluciones del siglo XXI.
+En particular, el sector de la química computacional está siendo profundamente sacudido por esta revolución.
+Aprovechando la inercia y el interés creciente en este campo, este trabajo pretende aplicar diferentes modelos de inteligencia artificial en el estudio de una proteína de especial interés para nuestra salud, la Ciclooxigenasa-2 (COX-2).
 
-blebleble
+La \emph{prostaglandin-endoperoxide sinthasa 2} (PTGS2), también conocida como COX-2, es una proteína que, en circunstancias normales, suele permanecer inactiva \cite{Cox2Location}, excepto por su expresión durante procesos inflamatorios.
+Asimismo, la falta de retorno a niveles bajos de expresión después de la inflamación ha sido relacionada con la aparición de diferentes formas de cáncer \cite{DefinitionCOX2CancerDictionary}.
+Este hecho ha convertido a la COX-2 en objeto de estudio de numerosas investigaciones científicas \cite{Cox2InhibitorsReview}, lo que la convierte en un punto de partida idóneo para el desarrollo de algoritmos de \emph{Machine Learning}, ya que dispone de una gran cantidad de datos para entrenar los modelos y contrastar los resultados.
+
+El objetivo principal del proyecto es el desarrollo de un software generador de IAs capaces de predecir la concentración de inhibición al 50\% (IC$_{50}$) para la COX-2\footnote{En realidad, el software funciona para cualquier proteína con entrada en la base de datos de ChEMBL \cite{ChemblDatabase}, aunque el objeto de estudio es la COX-2.} con la máxima precisión posible.
+Para ello, se extraen todos los datos de moléculas conocidas con un potencial de inhibición establecido para la COX-2.
+Tras un filtrado configurable por el usuario, se calculan 5.900 descriptores químicos para cada una de las entradas con el software AlvaDesk \cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper}.
+Seguidamente, una parte de los datos se utiliza para entrenar modelos de \emph{Random Forest} (RF) \cite{MachineLearningRandomForest}, mientras que el resto se reserva para validar la precisión de las predicciones.
+
+Cabe remarcar la principal hipótesis que sustenta este proceso y el proyecto en general: \emph{Existe una combinación (o varias combinaciones) de descriptores químicos directamente relacionada con el potencial de inhibición de la proteína}.
+Aunque esta afirmación pueda parecer natural, el coste computacional asociado es inmenso.
+Aun así, la precisión de las predicciones de los modelos apunta a la validez de esta hipótesis, si bien sigue siendo una conjetura por falta de una prueba definitiva.
+
+Finalmente, los modelos se utilizan para predecir el IC$_{50}$ de 50 \emph{azophotoswitches}, de los cuales se tienen datos sobre la energía libre de acoplamiento proporcionados por el Departamento de Química Computacional de la UAB \cite{UAB_ComputationalChemistry}.
+El análisis estadístico de las predicciones refleja una clara correlación entre ambas cantidades, lo que refuerza la hipótesis del proyecto.
 
@@
 \section*{Analytical abstract}
+Artificial intelligence is emerging as one of the revolutions of the 21st century.
+In particular, the field of computational chemistry is being profoundly shaken by this revolution.
+Taking advantage of the momentum and growing interest in this field, this work aims to apply different artificial intelligence models to the study of a protein of special interest to our health, Cyclooxygenase-2 (COX-2).
 
-bliblibli
+The \emph{prostaglandin-endoperoxide synthase 2} (PTGS2), also known as COX-2, is a protein that, under normal circumstances, tends to remain inactive \cite{Cox2Location}, except for its expression during inflammatory processes.
+Likewise, the failure to return to low expression levels after inflammation has been linked to the onset of various forms of cancer \cite{DefinitionCOX2CancerDictionary}.
+This fact has made COX-2 the subject of numerous scientific investigations \cite{Cox2InhibitorsReview}, making it an ideal starting point for the development of \emph{Machine Learning} algorithms, as it provides a large amount of data for training models and validating results.
+
+The main objective of the project is to develop software capable of generating AIs that can predict the 50\% inhibition concentration (IC$_{50}$) for COX-2\footnote{In reality, the software works for any protein with an entry in the ChEMBL database \cite{ChemblDatabase}, although the study focuses on COX-2.} with the highest possible accuracy.
+To achieve this, all known molecular data with an established inhibition potential for COX-2 are extracted.
+After a user-configurable filtering process, 5,900 chemical descriptors are calculated for each entry using the AlvaDesk software \cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper}.
+Subsequently, part of the data is used to train \emph{Random Forest} (RF) models \cite{MachineLearningRandomForest}, while the rest is reserved to validate the accuracy of the predictions.
+
+It is important to highlight the main hypothesis that underpins this process and the project as a whole: \emph{There exists a combination (or multiple combinations) of chemical descriptors that are directly related to the inhibition potential of the protein}.
+While this statement may seem intuitive, the computational cost associated with it is immense.
+Nevertheless, the accuracy of the model predictions supports the validity of this hypothesis, although it remains a conjecture due to the lack of definitive proof.
+
+Finally, the models are used to predict the IC$_{50}$ of 50 \emph{azophotoswitches}, for which data on the free binding energy have been provided by the Department of Computational Chemistry at UAB \cite{UAB_ComputationalChemistry}.
+The statistical analysis of the predictions shows a clear correlation between both quantities, which supports the project's hypothesis.
 
@@
 \newpage
-\setcounter{page}{1}
-\pagenumbering{arabic}
 \rhead{\TitolTFG}
@@
 \newpage
+\listoffigures{}
+\listoftables{}
+\newpage
 
+\setcounter{page}{1}
+\pagenumbering{arabic}
 \section{Introduction}
+The impact of \gls{ai} on science has been nothing short of a groundbreaking revolution, with few comparable precedents.
+The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry.
+Today, one of the primary goals of computational chemistry is to predict the properties of unstudied substances while minimizing experimental costs.
+Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive, and resource-intensive.
+In contrast, computational chemistry offers a wide range of methods capable of predicting a molecule's properties with reasonable accuracy.
+However, when \gls{ai} comes into play, predictions have demonstrated an almost surgical precision.
+
+Perhaps one of the most representative events showcasing the enormous impact of \gls{ai} on chemistry is the 2024 Nobel Prize in Chemistry.
+The winners, David Baker\cite{NobelPrizeBale}, along with Demis Hassabis and John Jumper\cite{NobelPrizeJumper}, were not traditionally trained chemists.
+Instead, their expertise lies in \gls{ai} algorithms and \gls{ml} methods applied to protein research.
+This milestone, among others, triggered a surge of chemistry researchers diving into the world of \gls{ai}, seeking applications for their respective fields.
+Today, the thrilling progress in computational chemistry has been further reinforced by these cutting-edge tools\cite{MachineLearningPaper5Lipoxygenase}, and the rapid pace of development keeps the scientific community eagerly anticipating future applications in fields such as medicine, materials science, and beyond.
+
+In this project we aim to apply the new \gls{ai} and \gls{ml} algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}. The \gls{cox2} is a protein
+
+\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
+
 The impact of \gls{ai} on science has been nothing but an outstanding breakthrough, with few comparable predecessors.
@@
 \section{Conclusions}
-Hola \cite{BookIC50}
 \newpage
@@
 \caption{Chemical graph of Celecoxib.}
+\addcontentsline{lof}{figure}{Chemical graph of Celecoxib.}
 \label{CelecoxibFigure}
@@
 \caption{Chemical graph of Rofecoxib.}
+\addcontentsline{lof}{figure}{Chemical graph of Rofecoxib.}
 \label{RofecoxibFigure}
@@
 
-\section{Tables of molecules}
+\section{Tables of azophotoswitches}\label{appendixAzophotoshiches}
 \begin{figure}[H]

### 2025-03-23 Manuscript/Plantilla memòria TFG 2024_25.tex
Writting

@@
 \usepackage{hyperref}
-\hypersetup{%
-  colorlinks=false,
-  linkcolor=black,
-  linkbordercolor={1.0 1.0 1.0},
-  breaklinks = true,
-  citebordercolor={1.0 1.0 1.0},
-  hidelinks = true,
-}
 \usepackage{xurl}
@@
 \renewcommand{\footrulewidth}{0pt}%
+
+%----------METADATA------------%
+
+\hypersetup{%
+  colorlinks=false,
+  linkcolor=black,
+  linkbordercolor={1.0 1.0 1.0},
+  breaklinks = true,
+  citebordercolor={1.0 1.0 1.0},
+  hidelinks = true,
+  pdftitle  = \TitolTFG,
+  pdfauthor = \NomComplet,
+  pdfsubject= \CodiTFG,
+  pdfcreator= \NomComplet,
+}
 
@@
 
-Finalment, els models es fan servir per predir l'IC$_{50}$ de 50 \emph{azophotoswitches} dels quals es tenen dades sobre l'energia lliure d'acoblament proporcionades pel Departament de Química Computacional de la UAB \cite{UAB_ComputationalChemistry}.
+Finalment, els models es fan servir per predir l'IC$_{50}$ de 50 \emph{azophotoswitches} dels quals es tenen dades sobre l'energia lliure d'acoblament proporcionades pel Departament de Química Física de la UAB \cite{UAB_ComputationalChemistry}.
 L'anàlisi estadístic de les prediccions reflecteix una clara correlació entre ambdues quantitats, fet que reforça la hipòtesi del projecte.
@@
 
-Finalmente, los modelos se utilizan para predecir el IC$_{50}$ de 50 \emph{azophotoswitches}, de los cuales se tienen datos sobre la energía libre de acoplamiento proporcionados por el Departamento de Química Computacional de la UAB \cite{UAB_ComputationalChemistry}.
+Finalmente, los modelos se utilizan para predecir el IC$_{50}$ de 50 \emph{azophotoswitches}, de los cuales se tienen datos sobre la energía libre de acoplamiento proporcionados por el Departamento de Química Física de la UAB \cite{UAB_ComputationalChemistry}.
 El análisis estadístico de las predicciones refleja una clara correlación entre ambas cantidades, lo que refuerza la hipótesis del proyecto.
@@
 
-Finally, the models are used to predict the IC$_{50}$ of 50 \emph{azophotoswitches}, for which data on the free binding energy have been provided by the Department of Computational Chemistry at UAB \cite{UAB_ComputationalChemistry}.
+Finally, the models are used to predict the IC$_{50}$ of 50 \emph{azophotoswitches}, for which data on the free binding energy have been provided by the Physical Chemistry Unit at UAB \cite{UAB_ComputationalChemistry}.
 The statistical analysis of the predictions shows a clear correlation between both quantities, which supports the project's hypothesis.
@@
 Today, the thrilling progress in computational chemistry has been further reinforced by these cutting-edge tools\cite{MachineLearningPaper5Lipoxygenase}, and the rapid pace of development keeps the scientific community eagerly anticipating future applications in fields such as medicine, materials science, and beyond.
+In this project we aim to apply the new \gls{ai} and \gls{ml} algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.
 
-In this project we aim to apply the new \gls{ai} and \gls{ml} algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}. The \gls{cox2} is a protein
+ Although significant advancements have been made, cancer still accounts for over 8 million deaths per year worldwide, and the scientific and medical communities remain far from achieving its complete eradication.
+Inflammation is one of the hallmarks of carcinogenesis; in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences.
+When a tissue is damaged, inflammation protects the organism from infections caused by external pathogens, a key function of the immune system to prevent the presence of invaders in the body.
+During the inflammatory process, cells proliferate under the command of the immune system to replace the damaged cells of the affected tissue.
+However, if this cell reproduction continues beyond the healing of the damaged tissue, it can potentially lead to cancer, contradicting the initial healing purpose of the inflammatory process.
+In some cases, inflammation can become chronic, leading to tumor development and uncontrolled cell proliferation.
+As a result, a wide range of drug prototypes have been designed to suppress inflammation.
+However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications.
+Consequently, the administration of these drugs is often counterproductive, and the search for a more effective and safer treatment remains ongoing.
+
+\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
+
+\textbf{Dr.Gonzalez and Dr.Lluch project}
+
+The project seeks to advance the understanding and treatment of cancer by approaching it as an inflammation-based disease and developing innovative drug design strategies.
+Unlike traditional approaches that often rely on broad-spectrum anti-inflammatory drugs, this research aims to create targeted therapies that mitigate or halt the inflammatory processes closely linked to cancer progression.
+Chronic inflammation is recognized as a key driver of tumor development, promoting immune evasion, genetic mutations, and uncontrolled cell proliferation.
+However, existing treatments such as nonsteroidal anti-inflammatory drugs (NSAIDs) and COX-2 inhibitors come with significant side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications, which limit their long-term clinical application.
+
+By adopting an interdisciplinary approach that integrates Theoretical Molecular Biology, Chemistry, Biochemistry, Physics, and Computer Science, this project will explore new molecular strategies for drug design.
+A major focus will be on targeting key inflammatory enzymes such as COX-2 and lipoxygenases, which are strongly implicated in cancer-related inflammation.
+Given the research team’s extensive experience in studying these enzymes—demonstrated through 39 published studies—the project aims to leverage Theoretical Chemistry methods, including Quantum Mechanics, Statistical Mechanics, and Biomolecular Simulations, to develop safer and more effective pharmacological interventions.
+
+One of the project’s central hypotheses is that many cancers share a fundamental inflammatory component, making inflammation control a promising therapeutic avenue.
+The research will investigate novel mechanisms to selectively inhibit or modulate the activity of COX-2 and related enzymes without causing harmful systemic effects.
+In particular, photopharmacology—using light-activated drug molecules—will be explored as a means of achieving spatial and temporal control over drug activity, potentially reducing off-target effects.
+
+Beyond cancer, the findings from this project could have far-reaching implications for other inflammation-related diseases.
+Chronic inflammation has been identified as a major underlying factor in conditions such as cardiovascular disease, diabetes, and neurodegenerative disorders like Alzheimer’s.
+As highlighted by Harvard Medical School, inflammation may be the common link among many of the world’s most prevalent and deadly diseases.
+By developing new strategies to control inflammation in cancer, this research could also contribute to broader medical advancements, ultimately benefiting patients, healthcare systems, and the pharmaceutical industry.
 

### 2025-03-24 Manuscript/Plantilla memòria TFG 2024_25.tex
Writting

@@
 \newacronym{cox2}{COX-2}{Cyclooxygenase-2}
+\newacronym{nsaid}{NSAID}{Non-Steroidal Anti-Inflammatory Drug}
 \newacronym{ptgs2}{PTGS2}{Prostaglandin-endoperoxide synthase 2}
@@
 \newacronym{id}{ID}{Identificator}
-\newacronym{ic50}{IC$_{50}$}{Half maximal inhibitory concentration}
-\newacronym{ic90}{IC$_{90}$}{90 percent inhibitory concentration}
-\newacronym{ic99}{IC$_{99}$}{99 percent inhibitory concentration}
+\newacronym{ic50}{IC$_{50}$}{Half Maximal Inhibitory Concentration}
+\newacronym{ic90}{IC$_{90}$}{90 Percent Inhibitory Concentration}
+\newacronym{ic99}{IC$_{99}$}{99 Percent Inhibitory Concentration}
 \newacronym{tp}{TP}{True Posive}
@@
 However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications.
-Consequently, the administration of these drugs is often counterproductive, and the search for a more effective and safer treatment remains ongoing.
+Consequently, the administration of these drugs is often contrindicative, and the search for a more effective and safer treatment remains ongoing.
+Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process, subsequently, a therapy based on the he chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.
+
+The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. In this project we do focus on the \gls{ic50}.
+
+Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin.
+However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
+One of the best drug candidates is
 

### 2025-03-25 Manuscript/Plantilla memòria TFG 2024_25.tex
Writting

@@
 
-The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. In this project we do focus on the \gls{ic50}.
+The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein.
+Taking advantage of the health interest and the large sets of data, we do focus on the \gls{ic50}.
+The \gls{ic50} is concentration assigned to the drug concentration required for a $50\%$ inhibition a protein, and is one of the most standard values to compute inhibition potentials as well as \gls{ic90} and \gls{ic99}.
+The lower the \gls{ic50} of a molecule the lower concentration of the molecule for suppressing the portein (i.e.\gls{cox2}) activity, ergo the molecule inhibits the protein more efficiently.
+This factor is key when it comes to drug design since a low inhibition potentials implies a low presence of external substances in the organism, a factor that helps to prevent drug's side effects\footnote{Naturally there are plently of other factors related to drug side effects}.
+
+Taking advantage of this
 
@@
 However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
-One of the best drug candidates is
+One of the best drug candidates is the Celecoxib (Def.
+(\ref{definitionCelecoxib})) and the Rofecoxib (Def.
+(\ref{definitionRofecoxib})).
+The the Physical Chemistry Unit at UAB \cite{UAB_ComputationalChemistry},
 

### 2025-04-27 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

--- 2025-03-24 Manuscript/Plantilla memòria TFG 2024_25.tex
@@
 Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive, and resource-intensive.
-In contrast, computational chemistry offers a wide range of methods capable of predicting a molecule's properties with reasonable accuracy.
+In contrast, computational chemistry offers a wide range of methods capable of predicting a molecule’s properties with reasonable accuracy.
 However, when \gls{ai} comes into play, predictions have demonstrated an almost surgical precision.
@@
 Today, the thrilling progress in computational chemistry has been further reinforced by these cutting-edge tools\cite{MachineLearningPaper5Lipoxygenase}, and the rapid pace of development keeps the scientific community eagerly anticipating future applications in fields such as medicine, materials science, and beyond.
-In this project we aim to apply the new \gls{ai} and \gls{ml} algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.
+In this project we aim to apply the new AI and ML algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.
 
 Although significant advancements have been made, cancer still accounts for over 8 million deaths per year worldwide, and the scientific and medical communities remain far from achieving its complete eradication.
-Inflammation is one of the hallmarks of carcinogenesis; in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences.
+Inflammation is one of the hallmarks of carcinogenesis, in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences.
 When a tissue is damaged, inflammation protects the organism from infections caused by external pathogens, a key function of the immune system to prevent the presence of invaders in the body.
@@
 Consequently, the administration of these drugs is often contrindicative, and the search for a more effective and safer treatment remains ongoing.
-Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process, subsequently, a therapy based on the he chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.
+Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process and responsable to convert the arachidonic acid to prostaglandin \ch{H_2} (Scheme (\ref{Cox2MainReaction})).
+Subsequently, a therapy based on the chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.
 
-The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. In this project we do focus on the \gls{ic50}.
+\begin{figure}[H]
+\captionsetup{type=scheme}
+\centering
+\schemestart
+\scalebox{0.7}{
+\chemname{\chemfig[angle increment=30, scale=0.1]{
+HO-[1](=[3]O)-[-1]-[1]-[-1]-[1]=[-1]-[-3]-[-1]=[-3]-[7]-[-3]=[7]-[-7]-[7]=[-7]-[3]-[-7]-[7]-[-7]-[7]
+}}{Arachidonic acid}
+}
+	\arrow{->[\gls{cox2}]}
+\scalebox{0.7}{
+\chemname{\chemfig[angle increment=30]{OH-[5](=[3]O)-[7]-[-3]-[7]-[-3]=[7]-[5]>:[7]*6(-(<[-3.8])-O-O-(<[3.8]C)-(<[-1]=[1]-[-1](<:[-3]OH)-[1]-[-1]-[1]-[-1]-[1])-)
+}}{Prostaglandin \chemfig{H_2}}
+}
+\schemestop
+\caption{Reaction catalysed by the COX-2 between arachidonic acid to prostaglandin H$_2$.}
+\label{Cox2MainReaction}
+\end{figure}
 
-Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin.
-However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
-One of the best drug candidates is
+The increasing interest in \gls{cox2} inhibitors has granted the scientific community with an extensive database of molecular inhibition potentials for this protein.
+In this project, we focus on the Half Maximal Inhibitory Concentration (\gls{ic50}), a standard metric representing the concentration of a drug required to inhibit 50\% of a target protein’s activity.
+Related measures include \gls{ic90} and \gls{ic99}, which correspond to 90\% and 99\% inhibition, respectively.
+The lower the \gls{ic50} value of a molecule, the lower the concentration needed to inhibit \gls{cox2}, indicating higher efficiency.
+This factor is crucial in drug design, as a lower required dosage minimizes the presence of foreign substances in the body, thereby reducing the risk of adverse effects\footnote{Naturally, multiple other factors influence drug side effects.}.
 
-\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
-
-\textbf{Dr.Gonzalez and Dr.Lluch project}
-
-The project seeks to advance the understanding and treatment of cancer by approaching it as an inflammation-based disease and developing innovative drug design strategies.
-Unlike traditional approaches that often rely on broad-spectrum anti-inflammatory drugs, this research aims to create targeted therapies that mitigate or halt the inflammatory processes closely linked to cancer progression.
-Chronic inflammation is recognized as a key driver of tumor development, promoting immune evasion, genetic mutations, and uncontrolled cell proliferation.
-However, existing treatments such as nonsteroidal anti-inflammatory drugs (NSAIDs) and COX-2 inhibitors come with significant side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications, which limit their long-term clinical application.
-
-By adopting an interdisciplinary approach that integrates Theoretical Molecular Biology, Chemistry, Biochemistry, Physics, and Computer Science, this project will explore new molecular strategies for drug design.
-A major focus will be on targeting key inflammatory enzymes such as COX-2 and lipoxygenases, which are strongly implicated in cancer-related inflammation.
-Given the research team’s extensive experience in studying these enzymes—demonstrated through 39 published studies—the project aims to leverage Theoretical Chemistry methods, including Quantum Mechanics, Statistical Mechanics, and Biomolecular Simulations, to develop safer and more effective pharmacological interventions.
-
-One of the project’s central hypotheses is that many cancers share a fundamental inflammatory component, making inflammation control a promising therapeutic avenue.
-The research will investigate novel mechanisms to selectively inhibit or modulate the activity of COX-2 and related enzymes without causing harmful systemic effects.
-In particular, photopharmacology—using light-activated drug molecules—will be explored as a means of achieving spatial and temporal control over drug activity, potentially reducing off-target effects.
-
-Beyond cancer, the findings from this project could have far-reaching implications for other inflammation-related diseases.
-Chronic inflammation has been identified as a major underlying factor in conditions such as cardiovascular disease, diabetes, and neurodegenerative disorders like Alzheimer’s.
-As highlighted by Harvard Medical School, inflammation may be the common link among many of the world’s most prevalent and deadly diseases.
-By developing new strategies to control inflammation in cancer, this research could also contribute to broader medical advancements, ultimately benefiting patients, healthcare systems, and the pharmaceutical industry.
-
-\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
-
-The impact of \gls{ai} on science has been nothing but an outstanding breakthrough, with few comparable predecessors.
-The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry.
-Nowadays, one of the main goals of computational chemistry is to predict certain properties of unstudied substances with minimal experimental costs\cite{AlphaFold2CommumityAssesment}.
-Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive and resource-intensive.
-On the other hand, \gls{ai} algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception.
-\gls{ai} provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.\par
-
-This project aims to implement artificial intelligence in computational chemistry, concretely, using AI-based algorithms to predict a drug’s inhibition potential\cite{BookIC50} for a given protein.
+Determining an experimental \gls{ic50} value can be both costly and time-consuming\footnote{Usually this parameter is computed throughout the Cheng Prusoff Equation (Def.
+(\ref{definitionChengPrusoff})) with experimental data.}.
+On the other hand, \gls{ai} provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.
+In this scenario this project aims to implement artificial intelligence in computational chemistry, concretely, using \gls{ai}-based algorithms to predict a drug’s inhibition potential\cite{BookIC50} for a given protein with a relativelly good accuracy \footnote{The accuracy of the ML models is discussed on the Results and Discussion section (\ref{sectionResultsAndDiscussion}).}.
 To achieve this, we make use of the ChEMBL database\cite{ChemblDatabase}, a vast repository of bioactive molecules with drug-like properties.
@@
 The chemical descriptors of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
-Around $10^4$ descriptors are calculated\cite{DescriptorsBookClassification}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
+Around 5000 descriptors are calculated\cite{DescriptorsBook}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
 The resulting dataset is subsequently used to train \gls{ai} models, enabling them to predict the inhibition potential of unknown compounds.
 Finally, we evaluate the reliability of each model by testing it against real experimental data.
-\par
 
@@
 The lack of an ultimate proof underscores the need for advanced computational techniques.
-By analysing large datasets, \gls{ai} can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par
+By analysing large datasets, \gls{ai} can detect hidden correlations that may not be immediately apparent through traditional statistical methods.
 
-At this stage, we focus on \gls{cox2}, a protein well known for its strong association with cancer development and inflammatory diseases\cite{DefinitionCOX2CancerDictionary}.
-\gls{cox2} plays a crucial role in the biosynthesis of prostaglandins, which mediate inflammation and pain.
-Overexpression of COX-2 has been linked to various types of cancer, making it a prime target for drug development.
-\gls{cox2} inhibitors, such as Celecoxib (Def.
-\ref{definitionCelecoxib}) and Rofecoxib (Def.
-\ref{definitionRofecoxib}), have been widely studied for their therapeutic potential.
-The scientific community has devoted an extensive research to \gls{cox2}, even before the rise of \gls{ai}, due to its biomedical significance\cite{Cox2InhibitorsReview}.
-By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings, demonstrating AI’s potential as a powerful tool in computational chemistry research.
-Our approach not only validates AI’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing COX-2 interactions.\par
-
-The AI algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
+The \gls{ai} algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}\cite{UAB_ComputationalChemistry}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
 This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting.
@@
 
-Moreover, the choice of the Random Forest algorithm is motivated by the presence of decision trees in various chemistry-related fields.
+Moreover, the choice of the Random Forest (\gls{rf}) algorithm is motivated by the presence of decision trees in various chemistry-related fields.
 In spectroscopy, for instance, decision trees are used in group theory to classify molecular symmetry.
-Similarly, in analytical chemistry, decision trees assist in substance separation techniques, while in organic chemistry, they are used to model reaction pathways.\par
+Similarly, in analytical chemistry, decision trees assist in substance separation techniques, while in organic chemistry, they are used to model reaction pathways.
 
-This study aims to bridge the gap between artificial intelligence and computational chemistry, proving AI’s potential to revolutionise drug discovery and molecular research.
+By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings\cite{Cox2InhibitorsReview}, demonstrating \gls{ai}’s potential as a powerful tool in computational chemistry research.
+Our approach not only validates \gls{ai}’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing \gls{cox2} interactions.Additionaly, this study aims to bridge the gap between \gls{ai} and computational chemistry, reinforcing the \gls{ai}’s potential to revolutionise drug discovery and molecular research.
 The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process.
 Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.
+
+Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin.
+However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
+One of the best drug candidates is the Celecoxib (Def.
+(\ref{definitionCelecoxib})) and the Rofecoxib (Def.
+(\ref{definitionRofecoxib})).
+The the Physical Chemistry Unit at UAB\cite{UAB_ComputationalChemistry}, is experimenting with azophotoswitches as COX-2 inhibitos.
+
 \newpage
-
 \section{Objectives}
@@
 \newpage
-
 \section{Methodology}
@@
 
-\section{Results and Discussion}
+\newpage
+\section{Results and Discussion}\label{sectionResultsAndDiscussion}
+In Figure (\ref{figureGraphicGbindingIC50}) we present the results bla bla bla the data is stored in appendix \ref{appendixTableOfResults}
 
-\newpage
+\begin{figure}[H]
+	\centering
+	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
+	\caption{Graphic of the azophotoswitches from appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
+	\label{figureGraphicGbindingIC50}
+\end{figure}
 
@@
 \end{figure}
+\begin{definition}\label{definitionChengPrusoff}
+Cheng Prusoff equation: standard equation used for the experimental computation of the IC50.
+	\begin{align*}
+		K_i=\frac{IC_{50}}{1+\frac{[S]}{K_m}}
+	\end{align*}
+\end{definition}
+where $K_i$ is the binding affinity, $[S]$ is the substrate concentration, $K_m$ is the Michaelis constant and \gls{ic50} the half maximal inhibitory concentration.
+
 \begin{definition}\label{definitionPersonCoefficient}
@@
 
+\section{Table of results}\label{appendixTableOfResults}
+
+\begin{table}[H]
+    \centering
+	\begin{tabular}{c|c|c|c|c|c|c}
+		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
+        Pyrazole & 1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145.893274 \\ \hline
+        Pyrazole & 2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160.715075 \\ \hline
+        Pyrazole & 3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192.302751 \\ \hline
+        Pyrazole & 4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306.280176 \\ \hline
+        Pyrazole & 5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238.028688 \\ \hline
+        Pyrazole & 6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142.842111 \\ \hline
+        Pyrazole & 8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240.476605 \\ \hline
+        Pyrazole & 9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171.543375 \\ \hline
+        Pyrazole & 10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247.718353 \\ \hline
+        Pyrazole & 11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215.242455 \\ \hline
+        Pyrazole & 12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196.189309 \\ \hline
+        Pyrazole & 13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220.685948 \\ \hline
+        Pyrazole & 14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231.70988 \\ \hline
+        Pyrazole & 15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235.929591 \\ \hline
+        Pyrazole & 16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149.258659 \\ \hline
+        Furan & 1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171.3118 \\ \hline
+        Furan & 2 & \ch{H} & \ch{H} &  & 0.193 & 189.723234 \\ \hline
+        Furan & 3 & \ch{F} & \ch{H} &  & -4.8383 & 133.666586 \\ \hline
+        Furan & 4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158.679542 \\ \hline
+        Furan & 5 & \ch{Br} & \ch{H} &  & -3.4217 & 144.849203 \\ \hline
+        Furan & 6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139.974502 \\ \hline
+        Furan & 7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148.510406 \\ \hline
+        Furan & 8 & \ch{H} & \ch{F} &  & -6.55 & 122.352426 \\ \hline
+        Furan & 9 & \ch{F} & F &  & -0.1311 & 189.013485 \\ \hline
+        Furan & 10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127.541229 \\ \hline
+        Furan & 11 & \ch{Br} & \ch{F} &  & 6.1474 & 241.164891 
+            \end{tabular}
+\end{table}
+
+\begin{table}[H]
+    \centering
+	\begin{tabular}{c|c|c|c|c|c|c}
+		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
+        Thiophene & 1 & \ch{F} & \ch{H} &  & 1.2724 & 192.519195 \\ \hline
+        Thiophene & 2 & \ch{H} & \ch{F} &  & -2.7842 & 152.750403 \\ \hline
+        Thiophene & 3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120.103107 \\ \hline
+        Pyrrole & 1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151.424098 \\ \hline
+        Pyrrole & 2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164.211081 \\ \hline
+        Benzene & 1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168.708238 \\ \hline
+        Benzene & 2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208.784609 \\ \hline
+        Benzene & 3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232.955871 \\ \hline
+        Benzene & 4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155.416193 \\ \hline
+        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
+        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
+        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
+        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
+        Indole & 3 &  &  &  & -5.532 & 111.153348 \\ \hline
+        TwoRings & 2 & \ch{NH} & O & \ch{H} & -2.2146 & 165.648426 \\ \hline
+        TwoRings & 3 & O & \ch{NH} & \ch{H} & -0.7334 & 178.354687 \\ \hline
+        TwoRings & 6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235.15246 \\ \hline
+        TwoRings & 7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77.7978863 \\ \hline
+        TwoRings & 8 & O & O & \ch{CH_3} & -3.5413 & 142.268104 
+    \end{tabular}
+\end{table}
+
 \end{document}

### 2025-04-27 Scripts/ProvidedSmiles.py

@@ -1,0 +1,61 @@
+import numpy as np
+import pandas as pd
+dictionary = [
+    {'Type': 'Pyrazole', 'Number': 1, 'R_1': 'CF_3', 'R_2': 'CH_2CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)CC)C(F)(F)F', 'Gbinding': -4.3505},
+    {'Type': 'Pyrazole', 'Number': 2, 'R_1': 'CF_3', 'R_2': 'CH_2CH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)CC)C(F)(F)F', 'Gbinding': -3.6190},
+    {'Type': 'Pyrazole', 'Number': 3, 'R_1': 'CF_3', 'R_2': 'CH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)C)C(F)(F)F',  'Gbinding': -0.5452},
+    {'Type': 'Pyrazole', 'Number': 4, 'R_1': 'CF_3', 'R_2': 'OCH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)OC)C(F)(F)F',  'Gbinding':  9.9793},
+    {'Type': 'Pyrazole', 'Number': 5, 'R_1': 'CF_3', 'R_2': 'OCH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)OC)C(F)(F)F', 'Gbinding':  1.5591},
+    {'Type': 'Pyrazole', 'Number': 6, 'R_1': 'CF_3', 'R_2': 'CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)C)C(F)(F)F', 'Gbinding':  -5.3292},
[…]

### 2025-04-27 Scripts/plotAzophotoSwitches.py

@@ -1,0 +1,27 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     27/04/2024                                                                                #
+#  Purpose:  Plot main results for the Azophotoswitches                                                #
+#                                                                                                      #
+########################################################################################################
+
+import pandas as pd
+import matplotlib.pyplot as plt
+
+Prediction = pd.read_csv("../Predictions/MainPredictions.csv")
+Prediction = Prediction.drop('Unnamed: 8', axis=1)
+
+for i in range(7):
+    Prediction = Prediction.drop(52-i, axis=0)
+
+plt.figure(figsize=(10, 7))
+plt.scatter(Prediction['Gbinding'],Prediction['Predictions'], color = 'purple')
+plt.xlabel('$\Delta G_{binding}$')
+plt.ylabel('Predicted $IC_{50}$')
+# plt.xlim(-12,12)
+# plt.ylim(80,320)
+# plt.show()
+plt.savefig("../Plots/GbindingVSIC50.pdf")
+plt.close()

### 2025-04-27 Scripts/testin.py

@@ -1,61 +1,0 @@
-import numpy as np
-import pandas as pd
-dictionary = [
-    {'Type': 'Pyrazole', 'Number': 1, 'R_1': 'CF_3', 'R_2': 'CH_2CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)CC)C(F)(F)F'},
-    {'Type': 'Pyrazole', 'Number': 2, 'R_1': 'CF_3', 'R_2': 'CH_2CH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)CC)C(F)(F)F'},
-    {'Type': 'Pyrazole', 'Number': 3, 'R_1': 'CF_3', 'R_2': 'CH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)C)C(F)(F)F'},
-    {'Type': 'Pyrazole', 'Number': 4, 'R_1': 'CF_3', 'R_2': 'OCH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)OC)C(F)(F)F'},
-    {'Type': 'Pyrazole', 'Number': 5, 'R_1': 'CF_3', 'R_2': 'OCH_3', 'R_3': 'F', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(c(c1)F)OC)C(F)(F)F'},
-    {'Type': 'Pyrazole', 'Number': 6, 'R_1': 'CF_3', 'R_2': 'CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1nc(c(c1)/N=N/c1ccc(cc1)C)C(F)(F)F'},
-    {'Type': 'Pyrazole', 'Number': 7, 'R_1': 'H', 'R_2': 'CH_3', 'R_3': 'H', 'canonical_smiles' : 'c1cc(ccc1S(=O)(=O)N)n1ncc(c1)/N=N/c1ccc(cc1)C'}, 
[…]

### 2025-04-28 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

@@
 By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings\cite{Cox2InhibitorsReview}, demonstrating \gls{ai}’s potential as a powerful tool in computational chemistry research.
-Our approach not only validates \gls{ai}’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing \gls{cox2} interactions.Additionaly, this study aims to bridge the gap between \gls{ai} and computational chemistry, reinforcing the \gls{ai}’s potential to revolutionise drug discovery and molecular research.
+Our approach not only validates \gls{ai}’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing \gls{cox2} interactions.
+Additionaly, this study aims to bridge the gap between \gls{ai} and computational chemistry, reinforcing the \gls{ai}’s potential to revolutionise drug discovery and molecular research.
 The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process.
@@
 However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
-One of the best drug candidates is the Celecoxib (Def.
+Still some alternative therapies related with \gls{nsaid}s are being explored, in particular, one of the most revolutionary ideas is the application of azophotoswitches in drug design.
+
+We say a molecule to be an azophotoswitch have an azo-bond (\ch{N=N}) sensitive to configurational transformations via photo-excitation.
+For instance let us consider the example of \textcolor{blue}{insert molecule's name}.
+\begin{figure}[H]
+\captionsetup{type=scheme}
+\centering
+\schemestart
+\scalebox{0.8}{
+	\chemname{\chemfig[angle increment=30]{
+	*6(-=-(-[1]N=[-1]N-*6(-=-=-=))=-=)
+	}}{trans-}}
+	\arrow{<=>[$h\nu$]}
+\scalebox{0.8}{
+	\chemname{\chemfig[angle increment=30]{
+	N(-[-4]*6(-=-=-=))=[0]N-[-2]*6(-=-=-=)
+	}}{cis-}}
+\schemestop
+\caption{\textcolor{blue}{insert molecule's name} as an example of an azophotoswitch.}
+\label{AzophotoswitchExampleFigure}
+\end{figure}
+the conversion between cis-/trans- configurations with photo-excitation leds to different bioactivities for each isomer.
+The key difference relies in the high molecules' estereochemical requirements in order to bind with a protein.
+In other words, given protein, the binding regions typically describe an specific shape such that the possible binding molecules must fit in this region.
+Then, for an azophotoswitch we might observe one configurational isomer to perfectly fit in de capidity whereas the other does not fit.
+Subsequently, the conformer that fits the best will interact the most with the protein\footnote{In what this project concerns this interaction will be an inhibition of the protein's activity} and we denote this isomer to be the \emph{active configuration}, similarly, we will refere to the other isomer as the \emph{inactive configuration}.\footnote{Typically, the active configuration is the trans- isomer whereas the inactive configuration referes to the cis- isomer although we still can find some exceptions.}
+
+The main application of azophotoswitches in drug design comes with the idea of the subministration of the inactive configuration, a priori an inocu substance for the organism, to a patient.
+Afterwards, the interchange of the configurations is archived by photo-excitation of the target area avoiding the presence of the subministred drug in non-wished organs and reducing possible side effects.
+With this procedure higher dossis can be provided to the patient by focussing the presence of the active configuration in the affected cells/organs.
+Still this therapies remain in an experimental and I+D mark.
+
+One of the best drug candidates for the \gls{cox2} inhibition is the Celecoxib (Def.
 (\ref{definitionCelecoxib})) and the Rofecoxib (Def.
-(\ref{definitionRofecoxib})).
-The the Physical Chemistry Unit at UAB\cite{UAB_ComputationalChemistry}, is experimenting with azophotoswitches as COX-2 inhibitos.
+(\ref{definitionRofecoxib}))\footnote{This drugs are also known as \emph{coxib} drus due to the \emph{-coxib} sufix.}.
+The the Physical Chemistry Unit at UAB\cite{UAB_ComputationalChemistry}, is experimenting with azophotoswitches as COX-2 inhibitos, the prototypes are molecular structures based on the Celecoxib (Def.
+(\ref{definitionCelecoxib})) structures.
+Different computations have been made, in particular we focus on the free binding energy denoted as $\Delta G_{binding}$\footnote{Some of this results are presented in the Appendix \ref{appendixTableOfResults}.}.
+
+Hence, as an applications for the \gls{ml} trained models we pretend to predeict the \gls{ic50} values for the azophotoswitches prototypes\footnote{This values are predictions per se since we do not dispose from experimental or simulations data.} and compare the results with the $\Delta G_{binding}$ computations since both quantities are related with the inhibition of the \gls{cox2}.
+Although a linear correlation is not expected, the intuition points that lower values of \gls{ic50} should lead to lower values of $\Delta G_{binding}$ and vice versa.
+This results will be deeply discussed in Results and Discussion section (\ref{sectionResultsAndDiscussion}).
+
+All in all, this project pretends to show \gls{ai} potential in accelarating drug desing and bridge computational chemistry and Artificial Intelligence, two cutting-edge fields, in order to open the door to new ideas and evolve both disciplines to the next level.
 
@@
 \appendix
-\section{Relevant definitions}
+\section{Rellevant definitions}
 \begin{definition}\label{definitionIC50}
@@
 		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
-        Pyrazole & 1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145.893274 \\ \hline
-        Pyrazole & 2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160.715075 \\ \hline
-        Pyrazole & 3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192.302751 \\ \hline
-        Pyrazole & 4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306.280176 \\ \hline
-        Pyrazole & 5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238.028688 \\ \hline
-        Pyrazole & 6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142.842111 \\ \hline
-        Pyrazole & 8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240.476605 \\ \hline
-        Pyrazole & 9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171.543375 \\ \hline
-        Pyrazole & 10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247.718353 \\ \hline
-        Pyrazole & 11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215.242455 \\ \hline
-        Pyrazole & 12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196.189309 \\ \hline
-        Pyrazole & 13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220.685948 \\ \hline
-        Pyrazole & 14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231.70988 \\ \hline
-        Pyrazole & 15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235.929591 \\ \hline
-        Pyrazole & 16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149.258659 \\ \hline
-        Furan & 1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171.3118 \\ \hline
-        Furan & 2 & \ch{H} & \ch{H} &  & 0.193 & 189.723234 \\ \hline
-        Furan & 3 & \ch{F} & \ch{H} &  & -4.8383 & 133.666586 \\ \hline
-        Furan & 4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158.679542 \\ \hline
-        Furan & 5 & \ch{Br} & \ch{H} &  & -3.4217 & 144.849203 \\ \hline
-        Furan & 6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139.974502 \\ \hline
-        Furan & 7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148.510406 \\ \hline
-        Furan & 8 & \ch{H} & \ch{F} &  & -6.55 & 122.352426 \\ \hline
-        Furan & 9 & \ch{F} & F &  & -0.1311 & 189.013485 \\ \hline
-        Furan & 10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127.541229 \\ \hline
-        Furan & 11 & \ch{Br} & \ch{F} &  & 6.1474 & 241.164891 
+		Pyrazole & \ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145.893274 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160.715075 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192.302751 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306.280176 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238.028688 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142.842111 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240.476605 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171.543375 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247.718353 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215.242455 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196.189309 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220.685948 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231.70988 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235.929591 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149.258659 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171.3118 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} &  & 0.193 & 189.723234 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} &  & -4.8383 & 133.666586 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158.679542 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} &  & -3.4217 & 144.849203 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139.974502 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148.510406 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} &  & -6.55 & 122.352426 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.9 & \ch{F} & F &  & -0.1311 & 189.013485 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127.541229 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241.164891 
             \end{tabular}
@@
 		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
-        Thiophene & 1 & \ch{F} & \ch{H} &  & 1.2724 & 192.519195 \\ \hline
-        Thiophene & 2 & \ch{H} & \ch{F} &  & -2.7842 & 152.750403 \\ \hline
-        Thiophene & 3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120.103107 \\ \hline
-        Pyrrole & 1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151.424098 \\ \hline
-        Pyrrole & 2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164.211081 \\ \hline
-        Benzene & 1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168.708238 \\ \hline
-        Benzene & 2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208.784609 \\ \hline
-        Benzene & 3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232.955871 \\ \hline
-        Benzene & 4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155.416193 \\ \hline
-        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
-        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
-        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
-        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
-        Indole & 3 &  &  &  & -5.532 & 111.153348 \\ \hline
-        TwoRings & 2 & \ch{NH} & O & \ch{H} & -2.2146 & 165.648426 \\ \hline
-        TwoRings & 3 & O & \ch{NH} & \ch{H} & -0.7334 & 178.354687 \\ \hline
-        TwoRings & 6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235.15246 \\ \hline
-        TwoRings & 7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77.7978863 \\ \hline
-        TwoRings & 8 & O & O & \ch{CH_3} & -3.5413 & 142.268104 
+        Thiophene & \ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} &  & 1.2724 & 192.519195 \\ \hline
+        Thiophene & \ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} &  & -2.7842 & 152.750403 \\ \hline
+        Thiophene & \ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120.103107 \\ \hline
+        Pyrrole & \ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151.424098 \\ \hline
+        Pyrrole & \ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164.211081 \\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168.708238 \\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208.784609 \\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232.955871 \\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155.416193 \\ \hline
+        Indole & \ref{figureCelecoxibIndole}.1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
+        Indole & \ref{figureCelecoxibIndole}.2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
+        Indole & \ref{figureCelecoxibIndole}.3 &  &  &  & -5.532 & 111.153348 \\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.2 & \ch{NH} & O & \ch{H} & -2.2146 & 165.648426 \\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.3 & O & \ch{NH} & \ch{H} & -0.7334 & 178.354687 \\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235.15246 \\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77.7978863 \\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.8 & O & O & \ch{CH_3} & -3.5413 & 142.268104 
     \end{tabular}

### 2025-04-29 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

--- 2025-04-27 Manuscript/Plantilla memòria TFG 2024_25.tex
@@
 \usepackage[math]{blindtext}
+\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
 %---------SPACING----------%
@@
 However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
-One of the best drug candidates is the Celecoxib (Def.
-(\ref{definitionCelecoxib})) and the Rofecoxib (Def.
-(\ref{definitionRofecoxib})).
-The the Physical Chemistry Unit at UAB\cite{UAB_ComputationalChemistry}, is experimenting with azophotoswitches as COX-2 inhibitos.
+Still some alternative therapies related with \gls{nsaid}s are being explored, in particular, one of the most revolutionary ideas is the application of azophotoswitches in drug design.
 
+We define a molecule as an azophotoswitch if it contains an azo bond (\ch{N=N}) that is sensitive to configurational transformations upon photo-excitation.
+For instance, let us consider the case of (E/Z)-N,1-diphenylmethanimine,
+\begin{figure}[H]
+\captionsetup{type=scheme}
+\centering
+\schemestart
+\scalebox{0.8}{
+	\chemfig[angle increment=30]{*6(-=-(-[1]N=[-1]N-*6(-=-=-=))=-=)}}
+	\arrow{<=>[$h\nu$]}
+\scalebox{0.8}{
+	\chemfig[angle increment=30]{
+	N(-[-4]*6(-=-=-=))=[0]N-[-2]*6(-=-=-=)
+	}}
+\schemestop
+	\caption{(E/Z)-N,1-diphenylmethanimine conversion as an example of an azophotoswitch.}
+\label{AzophotoswitchExampleFigure}
+\end{figure}
+The photo-induced E/Z isomerization leads to distinct bioactivities for each configuration.
+This variation arises from the stereochemical constraints required for a molecule to bind to a target protein.
+Typically, a protein’s binding site has a specific shape, and only molecules whose conformation matches this shape can interact effectively.
+In the context of an azophotoswitch, one isomer may fit precisely into the binding pocket, leading to strong interactions, while the other may not.
+Accordingly, we refer to the isomer that interacts most effectively with the protein as the active configuration, and the other as the inactive configuration.\footnote{In the context of this project, interaction refers to inhibition of the protein’s activity.} \footnote{Generally, the trans-isomer is considered the active configuration, while the cis-isomer is considered inactive.
+However, exceptions exist.}
+
+The primary application of azophotoswitches in drug design is the administration of the inactive isomer, which is assumed to be non-toxic to the organism.
+Later, the active configuration is generated through selective photo-excitation at the target site.
+This strategy minimizes drug activity in unintended tissues, thereby reducing side effects.
+As a result, higher dosages may be administered safely by localizing the therapeutic effect to the desired area.
+These therapies are still in the experimental stage and remain primarily within research and development.
+
+Among the most promising drug candidates for \gls{cox2} inhibition are Celecoxib (Definition \ref{definitionCelecoxib}) and Rofecoxib (Definition \ref{definitionRofecoxib}).\footnote{These compounds are often referred to as coxib drugs due to the common suffix -coxib.} At the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}, researchers are investigating azophotoswitches as potential COX-2 inhibitors, using molecular structures inspired by Celecoxib.
+Various computational analyses have been conducted, with particular attention to the binding free energy ($\Delta G_{\text{binding}}$).\footnote{Additional results are provided in Appendix \ref{appendixTableOfResults}.}
+
+As an application of our \gls{ml}-based predictive models, we aim to estimate the \gls{ic50} values of azophotoswitch prototypes.\footnote{These values are predictions, as no experimental or simulated data are currently available.} We will then compare these predictions with the computed $\Delta G_{\text{binding}}$ values, as both metrics are indicative of inhibition efficacy.
+While a direct linear correlation is not expected, we hypothesize that lower \gls{ic50} values should correspond to lower (more negative) $\Delta G_{\text{binding}}$ values, reflecting stronger binding affinities.
+These relationships will be explored in detail in Section \ref{sectionResultsAndDiscussion}.
+
+In conclusion, this study seeks to bridge the gap between Artificial Intelligence and computational chemistry, demonstrating AI’s potential to revolutionize drug discovery and molecular research.
+Accurate predictions of inhibition potential could accelerate the development of new pharmaceuticals, reduce the need for costly laboratory experiments, and streamline the drug screening process.
+Furthermore, identifying key molecular descriptors linked to inhibition may provide valuable insights into chemical interactions, opening new directions for research in medicinal chemistry and bioinformatics.
 \newpage
@@
 \newpage
-\section{Methodology}
+\section{Methodology}\label{sectionMethodology}
 The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.
@@
 However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure.
-A hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e.
+Since we are interested in testing azophotoswitches with presumably low \gls{ic50}, training \gls{ml} models with data of the order of $10^{8}$ or $10^{3}$ nM can be counterproductive since the model might misinterpret the data.\footnote{Typically the range of the azophotoswitches \gls{ic50} is arround the Celecoxib's \gls{ic50}, i.e.
+arround $120$ nM}.
+Consecutivelly, a hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e.
 molecules).
-\par
+
 With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule.
-Still, by deleting molecular descriptors with null values 2917 remain.
-Here, the Pearson correlation coefficient between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
+Still, some chemical descriptor need from the presence of a certain atom, for instance a chemical descriptor related to presence of a metal in the molecule, or active gorup, for example chemical descriptor related to the presence of a carboxilic acid, or chemical descriptor related triple bound among other possiblities.
+The computation of this chemical descriptors appear as \emph{null values}.
+By deleting molecular descriptors with null values 2917 chemical descriptors remain.
+Here, the Pearson correlation coefficient (Def.
+(\ref{definitionPersonCoefficient})) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
+This relationship will be discussed in the Results and Discussion Section (\ref{sectionResultsAndDiscussion}).
 
@@
 This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}, those with lower and higher $IC_{50}$ values, respectively.
-Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} and a \emph{testing set}, following the proportion specified by the hard-coded variable \emph{testSizeProportion}.
+By doing so, it is possible to compute the classification accuracy statistics of the model from the cluster association of each prediction.
+Thus we can compare each prediction of each molecules to experimental data, i.e.
+the model predicts a molecule to be highly active molecule to a highly active molecule this will be denoted as a \gls{tp}.
+Similarly we can define a \gls{tn}, \gls{fp} and \gls{fn} .
+This procedure is an standard for evaluating a \gls{ml} model realiability.
+
+Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} for training the \gls{rf} algorithm and a \emph{testing set} for testing the statistics and realiability of the \gls{rf} model, following the proportion specified by the hard-coded variable \emph{testSizeProportion}.
 This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
@@
 This algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets.
+Typically the more trees the model is trained with the best accuracy in the predictions, nevertheless the computational cost for each model training also increases with the number of trees.
+It is key to remark that the predictions' accuracy can not be arbitrarily improved by only increasing the number of trees of the \gls{rf} model.
+The predictions' accuracy is bonded to the data the model is trained with, thus if the data does not provide enough information about the insight of the protein, more accurate predictions can not be archived independently of the number of trees of the model.
+As a general criteria we can affirm that,
+\begin{align*}
+	\uparrow\text{Data}\quad+\uparrow\text{Number of trees}\implies\uparrow\text{Predictions' accuracy}\\
+	\downarrow\text{Data}\quad+\downarrow\text{Number of trees}\implies\downarrow\text{Predictions' accuracy}
+\end{align*}
+but more data or more number of trees independently will not lead to better accuracy,
+\begin{align*}
+	\uparrow\text{Number of trees}\nrightarrow\uparrow\text{Predictions' accuracy}\\
+	\uparrow\text{Data}\nRightarrow \uparrow\text{Predictions' accuracy}
+\end{align*}
+
 Later, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.
-
 Using the results, the \emph{True Positive Rate} (Def.
@@
 
+Finally, the \gls{rf} algorithm with best statistics\footnote{The ruling criteria used to classify one model to have "better statistics" than other is discussed in section (\ref{sectionResultsAndDiscussion})} are used to predict the \gls{ic50} of the azophotoswitch prototipes classified in Appendix (\ref{appendixAzophotoshiches}).
+This procedure begins with the computation of the chemical descriptors with AlvaDesk software \cite{MauriMolecularDescriptorsBook}, then the pertinent chemical descriptor are erased in order to match the ones th
+
 \newpage
 \section{Results and Discussion}\label{sectionResultsAndDiscussion}
-In Figure (\ref{figureGraphicGbindingIC50}) we present the results bla bla bla the data is stored in appendix \ref{appendixTableOfResults}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width = \textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
+	\caption{\gls{ic50} values }
+	\label{figureGraphicRecurrecyIC50}
+\end{figure}
 
@@
 	\centering
+	\includegraphics[width = \textwidth, trim={0.6cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/ChEMBL_ExtractorData_CHEMBL230_IC50_1000CorrelationFactors.pdf}
+	\caption{Pearson correlation coefficient for each chemical descriptor.}
+	\label{figureGraphicCorrelationFactor}
+\end{figure}
+
+In Figure (\ref{figureGraphicGbindingIC50}) we present the results for the predicted \gls{ic50} in terms of the $\Delta G_{binding}$ provided by the Physical Chemistry Unit of the UAB.
+The exact results are stored in Appendix \ref{appendixTableOfResults} in Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}), additionall the conditions under which the Random Forest (\gls{rf}) algorithm has been trained and the statistics analysis of its predictions is stored in Table (\ref{TableConditionsMainResults}).
+\begin{figure}[H]
+	\centering
 	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
-	\caption{Graphic of the azophotoswitches from appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
+	\caption{Graphic of the azophotoswitches from Appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
 	\label{figureGraphicGbindingIC50}
 \end{figure}
+
+Furthermore, we may also show the statistics and reliability of this results in Table (\ref{TableStatisitcsMainResults}).
+\begin{table}[H]
+    \centering	
+	\caption{Statistics for the computation of the results from tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
+	\label{TableStatisitcsMainResults}
+	\begin{tabular}{c|c}
+		Mean Squared Error       & 1202.70\\\hline
+		R-squared                & 0.89\\\hline
+		ClassificationAcuracy    & 0.94\\\hline
+		MatthewsCorrelationFactor& 0.87
+    \end{tabular}
+\end{table}
 
@@
 \section{Table of results}\label{appendixTableOfResults}
-
 \begin{table}[H]
     \centering
+	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
+	\label{TableMainResults1}
 	\begin{tabular}{c|c|c|c|c|c|c}
-		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
-        Pyrazole & 1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145.893274 \\ \hline
-        Pyrazole & 2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160.715075 \\ \hline
-        Pyrazole & 3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192.302751 \\ \hline
-        Pyrazole & 4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306.280176 \\ \hline
-        Pyrazole & 5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238.028688 \\ \hline
-        Pyrazole & 6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142.842111 \\ \hline
-        Pyrazole & 8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240.476605 \\ \hline
-        Pyrazole & 9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171.543375 \\ \hline
-        Pyrazole & 10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247.718353 \\ \hline
-        Pyrazole & 11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215.242455 \\ \hline
-        Pyrazole & 12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196.189309 \\ \hline
-        Pyrazole & 13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220.685948 \\ \hline
-        Pyrazole & 14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231.70988 \\ \hline
-        Pyrazole & 15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235.929591 \\ \hline
-        Pyrazole & 16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149.258659 \\ \hline
-        Furan & 1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171.3118 \\ \hline
-        Furan & 2 & \ch{H} & \ch{H} &  & 0.193 & 189.723234 \\ \hline
-        Furan & 3 & \ch{F} & \ch{H} &  & -4.8383 & 133.666586 \\ \hline
-        Furan & 4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158.679542 \\ \hline
-        Furan & 5 & \ch{Br} & \ch{H} &  & -3.4217 & 144.849203 \\ \hline
-        Furan & 6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139.974502 \\ \hline
-        Furan & 7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148.510406 \\ \hline
-        Furan & 8 & \ch{H} & \ch{F} &  & -6.55 & 122.352426 \\ \hline
-        Furan & 9 & \ch{F} & F &  & -0.1311 & 189.013485 \\ \hline
-        Furan & 10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127.541229 \\ \hline
-        Furan & 11 & \ch{Br} & \ch{F} &  & 6.1474 & 241.164891 
+		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
+		Pyrazole & \ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235 \\ \hline
+        Pyrazole & \ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} &  & 0.193 & 189 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} &  & -4.8383 & 133 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} &  & -3.4217 & 144 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} &  & -6.55 & 122 \\ \hline
+        Furan & \ref{figureCelecoxibFuran}.9 & \ch{F} & F &  & -0.1311 & 189\\ \hline
+        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
+        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241
             \end{tabular}
@@
     \centering	
+	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
+	\label{TableMainResults2}
 	\begin{tabular}{c|c|c|c|c|c|c}
-		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
-        Thiophene & 1 & \ch{F} & \ch{H} &  & 1.2724 & 192.519195 \\ \hline
-        Thiophene & 2 & \ch{H} & \ch{F} &  & -2.7842 & 152.750403 \\ \hline
-        Thiophene & 3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120.103107 \\ \hline
-        Pyrrole & 1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151.424098 \\ \hline
-        Pyrrole & 2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164.211081 \\ \hline
-        Benzene & 1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168.708238 \\ \hline
-        Benzene & 2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208.784609 \\ \hline
-        Benzene & 3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232.955871 \\ \hline
-        Benzene & 4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155.416193 \\ \hline
-        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
-        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
-        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
-        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
-        Indole & 3 &  &  &  & -5.532 & 111.153348 \\ \hline
-        TwoRings & 2 & \ch{NH} & O & \ch{H} & -2.2146 & 165.648426 \\ \hline
-        TwoRings & 3 & O & \ch{NH} & \ch{H} & -0.7334 & 178.354687 \\ \hline
-        TwoRings & 6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235.15246 \\ \hline
-        TwoRings & 7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77.7978863 \\ \hline
-        TwoRings & 8 & O & O & \ch{CH_3} & -3.5413 & 142.268104 
+		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
+        Thiophene & \ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} &  & 1.2724 & 192\\ \hline
+        Thiophene & \ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} &  & -2.7842 & 152\\ \hline
+        Thiophene & \ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120\\ \hline
+        Pyrrole & \ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151\\ \hline
+        Pyrrole & \ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164\\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168\\\hline
+        Benzene & \ref{figureCelecoxibBenzene}.2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208\\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232\\ \hline
+        Benzene & \ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155\\ \hline
+        Indole & \ref{figureCelecoxibIndole}.1 & \ch{H} &  &  & -9.7543 & 74\\ \hline
+        Indole & \ref{figureCelecoxibIndole}.2 & \ch{F} &  &  & -6.3397 & 108\\ \hline
+        Indole & \ref{figureCelecoxibIndole}.3 &  &  &  & -5.532 & 111\\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.2 & \ch{NH} & O & \ch{H} & -2.2146 & 165\\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.3 & O & \ch{NH} & \ch{H} & -0.7334 & 178\\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235\\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77\\ \hline
+        TwoRings & \ref{figureCelecoxibTwoRings}.8 & O & O & \ch{CH_3} & -3.5413 & 142
+    \end{tabular}
+\end{table}
+
+\begin{table}[H]
+    \centering	
+	\caption{Conditions and statistics for the computation of the results from tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
+	\label{TableConditionsMainResults}
+	\begin{tabular}{c|c}
+		NumberOfTrees            & 250\\\hline
+		Erased Percentatge       & 0.0\%\\\hline
+		Splitting proportion     & 10.0\% for testing \\\hline
+		minimumCorrelationFactor & 0.0\\\hline
+		Number of descriptors    & 3040\\\hline
+		Mean Squared Error       & 1202.70\\\hline
+		R-squared                & 0.89\\\hline
+		True Positive            & 994\\\hline
+		False Positive           & 8\\\hline
+		True Negative            & 1015\\\hline
+		False Negative           & 101\\\hline
+		True Positive Rate       & 0.91\\\hline
+		True Negative Rate       & 0.99\\\hline
+		ClassificationAcuracy    & 0.94\\\hline
+		MatthewsCorrelationFactor& 0.87
     \end{tabular}

### 2025-04-29 Scripts/plotAzophotoSwitches.py

@@ -18,8 +18,8 @@ for i in range(7):
 
 plt.figure(figsize=(10, 7))
 plt.scatter(Prediction['Gbinding'],Prediction['Predictions'], color = 'purple')
-plt.xlabel('$\Delta G_{binding}$')
-plt.ylabel('Predicted $IC_{50}$')
+plt.xlabel('$\Delta G_{binding}$ (Kcal/mol)')
+plt.ylabel('Predicted $IC_{50}$ (nM)')
 # plt.xlim(-12,12)
 # plt.ylim(80,320)
 # plt.show()

### 2025-04-29 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

@@
 \usepackage{fancyhdr}
+\usepackage{forest}
 \usepackage{graphicx}
@@
 Today, the thrilling progress in computational chemistry has been further reinforced by these cutting-edge tools\cite{MachineLearningPaper5Lipoxygenase}, and the rapid pace of development keeps the scientific community eagerly anticipating future applications in fields such as medicine, materials science, and beyond.
-In this project we aim to apply the new AI and ML algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.
+In this project we aim to apply the new AI and ML algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, depicted in Figure (\ref{FigureCox2ChimeraX}), a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.
 
@@
 Subsequently, a therapy based on the chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.
+\begin{figure}[t]
+	\centering
+	\includegraphics[width = \textwidth, trim={10cm 0cm 10cm 0cm}, clip]{GeneralSources/Cox2ChimeraX.jpg}
+	\caption{Structural representation of the \gls{cox2} generated by the ChimeraX software\cite{ChimeraX}.}
+	\label{FigureCox2ChimeraX}
+\end{figure}
+
+The increasing interest in \gls{cox2} inhibitors has granted the scientific community with an extensive database of molecular inhibition potentials for this protein.
+In this project, we focus on the Half Maximal Inhibitory Concentration (\gls{ic50}), a standard metric representing the concentration of a drug required to inhibit 50\% of a target protein’s activity.
+Related measures include \gls{ic90} and \gls{ic99}, which correspond to 90\% and 99\% inhibition, respectively.
+The lower the \gls{ic50} value of a molecule, the lower the concentration needed to inhibit \gls{cox2}, indicating higher efficiency.
+This factor is crucial in drug design, as a lower required dosage minimizes the presence of foreign substances in the body, thereby reducing the risk of adverse effects\footnote{Naturally, multiple other factors influence drug side effects.}.
 
@@
 \end{figure}
-
-The increasing interest in \gls{cox2} inhibitors has granted the scientific community with an extensive database of molecular inhibition potentials for this protein.
-In this project, we focus on the Half Maximal Inhibitory Concentration (\gls{ic50}), a standard metric representing the concentration of a drug required to inhibit 50\% of a target protein’s activity.
-Related measures include \gls{ic90} and \gls{ic99}, which correspond to 90\% and 99\% inhibition, respectively.
-The lower the \gls{ic50} value of a molecule, the lower the concentration needed to inhibit \gls{cox2}, indicating higher efficiency.
-This factor is crucial in drug design, as a lower required dosage minimizes the presence of foreign substances in the body, thereby reducing the risk of adverse effects\footnote{Naturally, multiple other factors influence drug side effects.}.
 
@@
 
-The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database.
+The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database\cite{ChemblDatabase}.
 Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Def.
@@
 \end{figure}
-Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others.
-This algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets.
+Afterwards, a Random Forest (\gls{rf}) algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others.
+Although the project’s primary focus is not the detailed workings of Machine Learning (\gls{ml}) algorithms but its applications in computational chemestry, it is natural to ponder the essence of what the machine is doing.
+The name “Random Forest” is directly tied to the analogy between a tree and a decision tree.
+\par
+
+As described in Definition (\ref{definitionDecisionTree}), the Random Forest algorithm generates a collection of random decision trees.
+The number of trees in the forest is a configurable parameter of the algorithm.
+More specifically, the Random Forest algorithm produces a set of decision trees, each trained on a random subset of the training data.
+The structure of each tree adjusts during training to make predictions that closely approximate the true target values.
+The final output of the Random Forest is typically an aggregate of the predictions from all the individual trees, such as a majority vote for classification tasks or an average for regression tasks.
+\par
+
+One notable characteristic of this method is its inherent randomness.
+Each Random Forest model is unique, even if configured with the same parameters and initialized under identical conditions.
+However, experimental evidence suggests that this randomness does not significantly impact the results.
+If two Random Forest algorithms are trained on the same dataset using identical parameters, their outputs will converge, even if the internal structures of their decision trees differ.
+
+The \gls{rf} algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets.
 Typically the more trees the model is trained with the best accuracy in the predictions, nevertheless the computational cost for each model training also increases with the number of trees.
-It is key to remark that the predictions' accuracy can not be arbitrarily improved by only increasing the number of trees of the \gls{rf} model.
+It is key to remark the predictions' accuracy can not be arbitrarily improved by only increasing the number of trees of the \gls{rf} model.
 The predictions' accuracy is bonded to the data the model is trained with, thus if the data does not provide enough information about the insight of the protein, more accurate predictions can not be archived independently of the number of trees of the model.
@@
 \begin{align*}
-	\uparrow\text{Data}\quad+\uparrow\text{Number of trees}\implies\uparrow\text{Predictions' accuracy}\\
-	\downarrow\text{Data}\quad+\downarrow\text{Number of trees}\implies\downarrow\text{Predictions' accuracy}
+	\uparrow\text{Data}\quad+\uparrow\text{Trees}\implies\uparrow\text{Predictions' accuracy}\\
+	\downarrow\text{Data}\quad+\downarrow\text{Trees}\implies\downarrow\text{Predictions' accuracy}
 \end{align*}
-but more data or more number of trees independently will not lead to better accuracy,
-\begin{align*}
-	\uparrow\text{Number of trees}\nrightarrow\uparrow\text{Predictions' accuracy}\\
-	\uparrow\text{Data}\nRightarrow \uparrow\text{Predictions' accuracy}
-\end{align*}
+but more data or more trees independently will not lead to better accuracy. Then, for the data we dispose, predictions with 500 trees are the same as the ones with $300$ trees.
 
@@
 
-Finally, the \gls{rf} algorithm with best statistics\footnote{The ruling criteria used to classify one model to have "better statistics" than other is discussed in section (\ref{sectionResultsAndDiscussion})} are used to predict the \gls{ic50} of the azophotoswitch prototipes classified in Appendix (\ref{appendixAzophotoshiches}).
-This procedure begins with the computation of the chemical descriptors with AlvaDesk software \cite{MauriMolecularDescriptorsBook}, then the pertinent chemical descriptor are erased in order to match the ones th
+Finally, the \gls{rf} model with best statistics\footnote{The ruling criteria used to classify one model to have "better statistics" than other is discussed in section (\ref{sectionResultsAndDiscussion})} are used to predict the \gls{ic50} of the azophotoswitch prototipes classified in Appendix (\ref{appendixAzophotoshiches}).
+This procedure begins with the computation of the chemical descriptors with AlvaDesk software \cite{MauriMolecularDescriptorsBook}, then the pertinent chemical descriptors are droped and remaining only the ones the algorithm is trained with.
+Then, by inputing the computed descriptors to the \gls{rf} model the predicted \gls{ic50} pop out as an outcome and are analyzed.
 
@@
 \section{Results and Discussion}\label{sectionResultsAndDiscussion}
+
+In Figure (\ref{figureGraphicRecurrecyIC50}) we present the extracted \gls{ic50} data extracted from the ChEMBL database under the target ID \emph{CHEMBL230}.
+Figure (\ref{figureGraphicRecurrecyIC50}) clearly shows multiples of 10 are significantly overrepresented respect to other values.
+Additionally, by analyzing data from other proteins we can confirm this is not an exception but rather the norm.
+It looks like experimental chemists have a preference for multiples of 10, often rounding their results to the nearest value in this category.
+Consequently, an inherent error associated with these values will always be present, and we will have to deal with it.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+Once the chemical descriptors are computed, we proceed to calculate the Pearson correlation coefficients as defined in Definition (\ref{definitionPersonCoefficient}).
+The results are subsequently plotted in Figure (\ref{figureGraphicCorrelationFactor}).
+From the plot, we observe a “Gaussian bell” shape centered around zero, which aligns with our expectations.
+This suggests that there is no inherently preferred set of chemical descriptors for the protein, a finding that may initially seem at odds with the project’s goals.
+
+However, our hypothesis states that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
+This observation does not contradict that statement.
+Intuitively, we believe that filtering out descriptors with the lowest  $r^2$  values might lead to improved results.
+This possibility will be explored in subsequent discussions.
 
@@
 The exact results are stored in Appendix \ref{appendixTableOfResults} in Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}), additionall the conditions under which the Random Forest (\gls{rf}) algorithm has been trained and the statistics analysis of its predictions is stored in Table (\ref{TableConditionsMainResults}).
+
 \begin{figure}[H]
@@
 Furthermore, we may also show the statistics and reliability of this results in Table (\ref{TableStatisitcsMainResults}).
+
 \begin{table}[H]
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width = \textwidth, trim={0cm 0cm 0cm 0cm}, clip]{GeneralSources/LastFrameDockingTwoRingsFiveMembers.jpg}
+	\caption{Structural ilustration of the molecule identied as \ref{figureCelecoxibTwoRings}.7 and \gls{cox2} docking generated by the ChimeraX software[15].}
+	\label{figureDockingBestResult}
+\end{figure}
+
+\newpage
 \section{Conclusions}
+
 \newpage
+\section{Acknowledgements}
+I am grateful to Dr.
+Josep Maria Lluch, Dr.
+Miquel Moreno Ferrer and Dra.
+Àngels Gonzalez Lafont for allowing me to be one of his pupils and for presenting this project.
+I am also deeply grateful to PhD Alex Perez Sanchez and PhD Pedro Martínez Zaragoza for sharing their ideas and fruitful conversations
 
+I would like to acknowledge my mother and sister for their unconditional support, and my father for the values he taught me.
+Additionally, I would like to thank my friends Francisco Montaño, David Muñoz and Manel Martin for listening to my monologues about my excitement for the \gls{cox2} and azophotoswitches.
+
+Molecular graphics and analyses performed with UCSF ChimeraX, developed by the Resource for Biocomputing, Visualization, and Informatics at the University of California, San Francisco, with support from National Institutes of Health R01-GM129325 and the Office of Cyber Infrastructure and Computational Biology, National Institute of Allergy and Infectious Diseases.
+
+\newpage
 \section{Bibliography}
@@
 \end{definition}
+
+\begin{definition}\label{definitionDecisionTree}
+A decision tree is a classification algorithm based on a series of ordered \emph{if} statements.
+The algorithm begins at the top of the tree, where a question is posed to the data.
+Depending on the answer, the data follows different branches, each corresponding to a subsequent question.
+This process is repeated at each node until the data reaches the bottom of the tree, where the path it has followed determines the classification of the given data.
+
+This kind of algorithm is vividly present in the chemical landscape, for instance in the spectroscopy realm the determination of a molecule's symmetry group is provided by a decision tree such as Figure (\ref{figExScpectroDecisionTree}).
+\begin{figure}[H]
+\centering
+\includegraphics[width = 0.5\textwidth]{GeneralSources/Point_group_determination_flowchart_v2.png}
+\caption{Decision tree for determining the point group of a molecule}
+\label{figExScpectroDecisionTree}
+\end{figure}
+\end{definition}
+
 \begin{definition}\label{definitionTruePositiveRate}

### 2025-04-30 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

@@
 \usepackage{hyperref}
+\usepackage{pgfplots}
 \usepackage{xurl}
+\usepackage{pdflscape}
 %-----------------FIGURES AND TABLES----------------%
@@
 \newcommand\NomProfeA{Dr. Miquel Moreno Ferrer}
-\newcommand\NomProfeB{Dr. Àngels Gonzalez Lafont}
+\newcommand\NomProfeB{Dr. Àngels González Lafont}
 \newcommand\CodiTFG{TFG2425\_045}
@@
 \newpage
+\thispagestyle{empty}
+\mbox{} 
+\newpage
 
@@
 
-In Figure (\ref{figureGraphicRecurrecyIC50}) we present the extracted \gls{ic50} data extracted from the ChEMBL database under the target ID \emph{CHEMBL230}.
+\subsection{Available data}
+In Figure (\ref{figureGraphicRecurrecyIC50}) we present the extracted \gls{ic50} data extracted from the ChEMBL database under the target ID \emph{CHEMBL230} for the interval $[0,200]$ nM.
 Figure (\ref{figureGraphicRecurrecyIC50}) clearly shows multiples of 10 are significantly overrepresented respect to other values.
@@
 Consequently, an inherent error associated with these values will always be present, and we will have to deal with it.
+This observation will be one of the cornerstones of our ultimate results.
 
@@
 	\includegraphics[width = \textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
-	\caption{\gls{ic50} values }
+	\caption{\gls{ic50} values from our dataset and generation of a 20\% gap.}
 	\label{figureGraphicRecurrecyIC50}
@@
 
-Once the chemical descriptors are computed, we proceed to calculate the Pearson correlation coefficients as defined in Definition (\ref{definitionPersonCoefficient}).
+Additionally in Figure (\ref{figureGraphicRecurrecyIC50}) we can also observe the procedure of the generation of a gap in the data.
+Giving a set of data the average \gls{ic50} is computed, for this case it is arround $47$ nM.
+Then, a percentage of the data is erased ruled by the \emph{percentageErased} hard-coded variable in a way that the average \gls{ic50} is located in the middle of the interval.
+In Figure (\ref{figureGraphicRecurrecyIC50}) all the data is presented in color blue + orange, then the gap is performed by the delation of the blue region centered around $47$ nM.
+For this case this gap comprehend the 20\% of the data.
+
+\subsection{Correlation of individual descriptors and \gls{ic50}}
+
+Afterwards the chemical descriptors are computed with AlvaDesk software.
+Hence, we proceed to calculate the Pearson Correlation Coefficients\footnote{The Pearson Correlation Coefficient is also denoted as $r^2$} as defined in Definition (\ref{definitionPersonCoefficient}) between the descriptors values and the \gls{ic50} of each molecule.
 The results are subsequently plotted in Figure (\ref{figureGraphicCorrelationFactor}).
-From the plot, we observe a “Gaussian bell” shape centered around zero, which aligns with our expectations.
-This suggests that there is no inherently preferred set of chemical descriptors for the protein, a finding that may initially seem at odds with the project’s goals.
-
-However, our hypothesis states that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
-This observation does not contradict that statement.
-Intuitively, we believe that filtering out descriptors with the lowest  $r^2$  values might lead to improved results.
-This possibility will be explored in subsequent discussions.
+From the plot, we observe a‚ Gaussian bell shape centered around zero, which aligns with our expectations.
+This suggests that there is no inherently preferred set of chemical descriptors for the protein, a finding that may initially seem at odds with the project's goals.
 
@@
 
+This results is entirely natural, if a preferred descriptors would exist the implementation of \gls{ai}s would not be necessary and major advancedments would already be archived.
+Still our hypothesis holds, since it states that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
+This observation does not contradict that statement.
+Intuitively, we may believe that filtering out descriptors with the lowest  $r^2$  values might lead to improved results.
+This possibility will be explored in subsequent discussions.
+
+\subsection{Pearson correlation factor and mean squared error}
+
+Once the models are generated, i.e.
+the pertinent variables are set up, predictions can been.
+Thus, we can compute the Pearson Correlation Factors (Def.
+(\ref{definitionPersonCoefficient})) and Mean Squared Error (Def.
+(\ref{definitionMeanSquaredError})) for the predictions versus the experimental \gls{ic50} data.
+In Figure (\ref{FigPlotErasedPercentageVSRSquare}) we present two plots of the Pearson Correlation Factors and Mean Squared Error in terms of the erased percentage.
+
+\begin{figure}[H]
+\begin{tikzpicture}
+\begin{axis}[
+    width=0.45\textwidth,
+    height=8cm,
+    xlabel={$\%_{\text{Erased}}$},
+    ylabel={$r^2$},
+    xmin=0, xmax=100,
+    ymin=0.94, ymax=1.0,
+    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
+    ytick={0.9, 0.92, 0.94, 0.96, 0.98, 1.0},
+    legend pos=south east,
+    legend style={font=\small},
+    tick label style={font=\small},
+    label style={font=\small},
+]
+\addplot[
+    color=magenta,
+    mark=diamond*,
+    thick
+] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSRSquare.txt};
+\end{axis}
+\end{tikzpicture}
+\begin{tikzpicture}
+\begin{axis}[
+    width=0.45\textwidth,
+    height=8cm,
+    xlabel={$\%_{\text{Erased}}$},
+	ylabel={Mean Squared Error (nM$^2$)},
+    xmin=0, xmax=100,
+    ymin=0, ymax=200,
+    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
+    legend pos=north east,
+    legend style={font=\small},
+    tick label style={font=\small},
+    label style={font=\small}
+]
+\addplot[
+    color=magenta,
+    mark=diamond*,
+    thick
+] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSMeanSquaredError.txt};
+\end{axis}
+\end{tikzpicture}
+\caption{Plots of $\%_{\text{Erased}}$ vs $r^2$ and $\%_{\text{Erased}}$ vs Mean Squared Error.
+For a maximum $IC_{50}$ = 200 nM and a minimum of 0 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+\label{FigPlotErasedPercentageVSRSquare}
+\end{figure}
+
+From Figure (\ref{figureGraphicRecurrecyIC50}), we know the data has an inherent precision problem, especially when approaching higher  $IC_{50}$  values, additionally we do not now the precision of some measurements.
+Since our working models do not account for the lack of precision in each molecule's data, the values of  $r^2$  and mean squared error are not expected to be exactly 1 and 0, respectively.
+In fact, some variance and uncertainty are inevitable.
+Therefore, discarding more than 50\% of our data would be a critical mistake, even if statistical measures suggest otherwise.
+However, these values still serve as a good reflection of our method's reliability up to a certain threshold.
+
+In this work, we will arbitrarily set this threshold at  $r^2 = 0.90$ .
+This hard-coded decision is purely conventional, as we need to establish a point beyond which  $r^2$  values become meaningless (i.e., obtaining  $r^2$  values above 0.90 is unnecessary, given that such variance is inherent to our data).
+The justification for this choice is that, in some areas of chemistry\footnote{Particularly in analytical chemistry} two data sets are generally considered correlated if their  $r^2$  value exceeds 0.90.
+However, it is important to emphasize that this convention is purely subjective and should not be regarded as an inviolable rule.
+The reliable statistics will come from the \emph{True Positive Rate} (Def.
+\ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def.
+\ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def.
+\ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def.
+\ref{definitionMatthewsCorrelationCoeficient}), the standard quantities for rating a \gls{ml} model.
+
+\subsection{Azophotoswitches analysis}
+
 In Figure (\ref{figureGraphicGbindingIC50}) we present the results for the predicted \gls{ic50} in terms of the $\Delta G_{binding}$ provided by the Physical Chemistry Unit of the UAB.
@@
 	\centering
-	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
+	\includegraphics[width = 0.7\textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
 	\caption{Graphic of the azophotoswitches from Appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
@@
 		Mean Squared Error       & 1202.70\\\hline
-		R-squared                & 0.89\\\hline
+		$r^2$ 	                 & 0.90\\\hline
 		ClassificationAcuracy    & 0.94\\\hline
@@
 \end{table}
+
+In Figure (\ref{figureGraphicGbindingIC50}) we can see a clear correlation between our initial intuition.
+Lower values of free eneregy (the most negative ones) correspond to low \gls{ic50} values i.e.
+highly active molecules
+
+\subsection{Azophotoswitches analysis}
 
@@
 Miquel Moreno Ferrer and Dra.
-Àngels Gonzalez Lafont for allowing me to be one of his pupils and for presenting this project.
-I am also deeply grateful to PhD Alex Perez Sanchez and PhD Pedro Martínez Zaragoza for sharing their ideas and fruitful conversations
+Àngels González Lafont for allowing me to be one of his pupils and for presenting this project.
+I am also deeply grateful to PhD Álex Pérez Sánchez and PhD Pedro Martínez Zaragoza for sharing their ideas and fruitful conversations.
 
@@
 \begin{align}
-r_{xy}=\frac{\sum_{i=1}^n(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum_{i=1}^n(x_i-\bar{x}^2)}\sqrt{\sum_{i=1}^n(y_i-\bar{y}^2)}},
+r_{xy}=\frac{\sum_{i=1}^n(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum_{i=1}^n(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^n(y_i-\bar{y})^2}},
 \end{align}
@@
 Therefore the sign of $r_{xy}$ is tightly related to the sign of alinear regression, more precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
+\end{definition}
+
+\begin{definition}\label{definitionMeanSquaredError}
+Mean Squared Error: Given set of pairs of data $\{(x_i,y_i)\}_{i=1}^n$ the Mean Squared Error is the quantity defined as,
+\begin{align}
+	MSE=\frac{1}{n}\sum_{i=1}^n(X_i-Y_i)^2
+\end{align}
+The name of this quantity is self-descriptive, since $X_i-Y_i$ is the error associated to the i-th prediction and the MSE is the mean of the squares of this erros.
 \end{definition}
@@
 		Mean Squared Error       & 1202.70\\\hline
-		R-squared                & 0.89\\\hline
+		$r^2$	                 & 0.90\\\hline
 		True Positive            & 994\\\hline

### 2025-05-01 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

@@
 \usepackage{pdflscape}
+\usepackage{overpic}
 %-----------------FIGURES AND TABLES----------------%
@@
 We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset.
-The chemical descriptors of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
+The chemical descriptors (Def.
+(\ref{definitionChemicalDescriptors})) of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
 Around 5000 descriptors are calculated\cite{DescriptorsBook}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
@@
 	\centering
-	\includegraphics[width = \textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
+		\begin{overpic}[width = \textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
+		\put(10,55){Highly active}
+		\put(30,55){Gap}
+		\put(55,55){Least active}
+	\end{overpic}
 	\caption{\gls{ic50} values from our dataset and generation of a 20\% gap.}
@@
     xmin=0, xmax=100,
-    ymin=0.94, ymax=1.0,
+    ymin=0.75, ymax=1.0,
     xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
-    ytick={0.9, 0.92, 0.94, 0.96, 0.98, 1.0},
     legend pos=south east,
@@
 Furthermore, we may also show the statistics and reliability of this results in Table (\ref{TableStatisitcsMainResults}).
+In the statistics we can see how all values surpass 0.9.
+In particular the model is capable of predicting when a molecules is not a highly active inhibitor in the 99\% of the times, since the True Negative Rate (Def.(\ref{definitionTrueNegativeRate})) is 0.99.
+The classification accuracy (Def.
+\ref{definitionClassificationAccuracy}) and the Matthews Correlation Factors take values close to 1, remarking thes particular model as a quite reliabile \gls{rf} model.
 
@@
 		$r^2$ 	                 & 0.90\\\hline
-		ClassificationAcuracy    & 0.94\\\hline
-		MatthewsCorrelationFactor& 0.87
+		True Positive            & 994\\\hline
+		False Positive           & 8\\\hline
+		True Negative            & 1015\\\hline
+		False Negative           & 101\\\hline
+		True Positive Rate       & 0.90\\\hline
+		True Negative Rate       & 0.99\\\hline
+		ClassificationAcuracy    & 0.95\\\hline
+		MatthewsCorrelationFactor& 0.90
     \end{tabular}
@@
 
-In Figure (\ref{figureGraphicGbindingIC50}) we can see a clear correlation between our initial intuition.
+At this stage, we must point out the model is unable to distinguish between the active and unactive configurations.
+This problem is not related cased by the model or the descriptors computation but the database the model is trained with.
+The lack of existence of -cis/-trans configurations in the ChEMBL database \cite{ChemblDatabase} makes it impossible for the model to know the -cis conformation to be different from the -trans conformation.
+In other words, the model is unable to generate information, if it is not told to distinguish between -cis and -trans configurations, then it will not distinguish between them.
+Therefore the model will also provide the \gls{ic50} predictions for the active configuration, i.e.
+the -cis configuration.
+Our hypothesis holds, since in Figure (\ref{figureGraphicGbindingIC50}) we can see a clearly a correlation between the \gls{ic50} and $\Delta G_{binding}$ matching with our initial intuition.
 Lower values of free eneregy (the most negative ones) correspond to low \gls{ic50} values i.e.
-highly active molecules
+highly active molecules.
+
+However, the hipothesis of the existence of a combination of chemical descriptors that is directly related with a molecule's inhibition power for a given protein seems correct.
+Although, finding this combination of chemical descriptors is not an easy task for a chemist.
+At first glace, we might hypothesize that since this combination must be encoded into the \gls{rf} models unencripting this models would help us to understand the insights of the \gls{cox2}\footnote{Or any other protein since the code is through to be applied to any protein with an entrance in the ChEMBL database\cite{ChemblDatabase}.}.
+
+Still this procedure is almost impossible, since the nature of the \gls{rf} is similar to check weather a pasword is correct or not.
+In other words, computationally speaking, predicting a molecules \gls{ic50} as well as checking an username and a pasword is an easy task for the computer.
+Nevertheless, reathriving a password and highlight the chemical descriptors with higher dependecy on the \gls{ic50} is another story.
+
+For instance, one could think making predictions of random molecules \gls{ic50} by varying one molecular descriptor and holding the resest constant could give us information on this dependecy\footnote{This would be a desencriptation by brute force.}.
+However, we encounter several unsortable incoherences in this procedure.
+For example, let us think we want to observe the dependecy of the \gls{ic50} on a molecules' average bond distance.
+Molecules that, at first, would not fit into the binding cavity of the \gls{cox2} could happend to fit after this streaching, but this molecules are not real, i.e.
+non-stable, lossing any chemical coherence.
+Additionaly there are some chemical descriptors that integers by nature, for istance the number of carbons in a molecule, but this procedure would point out the ideal number of carbons to be a good inhibitor is 25.5 carbons, and absurd outcome.
+Furthermore a set arbitrarly generated chemical descriptors it is not necessarily correlated to a molecule, in the majority of the cases there will not be any molecule to have the specified chemical descriptors, thus we would be trying to predict the \gls{ic50} of imaginary molecules.
+
+It is important to remark this observations does not deny the power of \gls{ai} for computational chemistry, but points out at some limitations of the technology.
 
 \subsection{Azophotoswitches analysis}
+
+After the predictions have been computed a docking has been performed of one of the most promising azophotoswitches.
+In particular the docking of the  \ref{figureCelecoxibTwoRings}.7 molecule depicted in Scheme (\ref{figureCelecoxibTwoRingsDoking}), this molecule has a computed $\Delta G_{binding}$ of 10.6712 Kcal/mol and a predicted \gls{ic50} of 77 nM.
+An image of the last frame of the docking procedure is provided in Figure (\ref{figureDockingBestResult}).
+\begin{figure}[H]
+\captionsetup{type=scheme}
+\centering
+\scalebox{0.7}{
+\chemfig[angle increment=30]{
+	H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-O-*5(-N(-[-3]H)-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives highly active molecule.}
+\label{figureCelecoxibTwoRingsDoking}
+\end{figure}
 
@@
 \end{figure}
+Hence we can see the fitting of the azophotoswitch in the -cis configuration inside the \gls{cox2} cavity.
+Although the -trans configuration has been seen to fit into the binding site\footnote{With few problems} it is impossible for this isomer to access to the binding site due to stereochemical problems, i.e.
+the -trans conformation colides with the outer layers of the \gls{cox2} and cannot access to the binding cavity.
+Still this molecule could interact with undesired proteins in both configurations (E)/(Z) which could lead to enormous side effects if it is administered as a drug, then further investigations must be done.
 
@@
 \section{Conclusions}
+We have proved Artificial Intelligence's potential for computational and theorical chemistry.
+Furthermore, we have developed a totally functional Machine Learning software capable of predicting \gls{ic50} values for any protein in the ChEMBL database.
+Also the software is capable of generating the statistics for each \gls{ml} model generated defined by the hard-coded variables that define the data the model is trained with.
+Thus the user is capable of playing arround with the variables in order to obtain the best predictions possible.
+
+Additionaly we have proved our intuition on the \gls{ic50} direct relationship with the provided $\Delta G_{binding}$ values to be correct.
+Furthermore, a docking of one of the most promising azophotoswitches as been performed matching our expectations and reinforcing the \gls{ai}'s potential.
 
@@
 For this project, we aim to identify substances with the lowest possible $IC_{50}$, as our goal is to minimize the presence of foreign substances in the living organism.
+\end{definition}
+
+\begin{definition}\label{definitionChemicalDescriptors}
+Molecular descriptor: "A molecular descriptor is the final result of a logical and mathematical procedure which transforms chemical information encoded within a symbolic representation of a molecule into a useful number or the result of some standardized experiment."\cite{DescriptorsBook}
 \end{definition}
@@
 		False Negative           & 101\\\hline
-		True Positive Rate       & 0.91\\\hline
+		True Positive Rate       & 0.90\\\hline
 		True Negative Rate       & 0.99\\\hline
-		ClassificationAcuracy    & 0.94\\\hline
-		MatthewsCorrelationFactor& 0.87
+		ClassificationAcuracy    & 0.95\\\hline
+		MatthewsCorrelationFactor& 0.90
     \end{tabular}

### 2025-05-01 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

--- 2025-04-29 Manuscript/Plantilla memòria TFG 2024_25.tex
@@
 \usepackage{hyperref}
+\usepackage{pgfplots}
 \usepackage{xurl}
+\usepackage{pdflscape}
+\usepackage{overpic}
 %-----------------FIGURES AND TABLES----------------%
@@
 
-The \gls{rf} algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets.
-Typically the more trees the model is trained with the best accuracy in the predictions, nevertheless the computational cost for each model training also increases with the number of trees.
-It is key to remark the predictions' accuracy can not be arbitrarily improved by only increasing the number of trees of the \gls{rf} model.
-The predictions' accuracy is bonded to the data the model is trained with, thus if the data does not provide enough information about the insight of the protein, more accurate predictions can not be archived independently of the number of trees of the model.
-As a general criteria we can affirm that,
+The \gls{rf} algorithm generates a large number of random decision trees (as defined by the hard-coded variable \emph{numberOfTrees}), which are trained on subsets of the training data.
+Typically, increasing the number of trees enhances the model’s predictive accuracy; however, this comes at the cost of greater computational complexity.
+Importantly, prediction accuracy cannot be arbitrarily improved simply by increasing the number of trees.
+The model’s performance is fundamentally limited by the quality and quantity of the training data.
+If the data lacks sufficient information about the underlying protein-related phenomena, higher accuracy cannot be achieved regardless of how many trees are used.
+
+In general, the relationship between data quality/quantity and the number of trees can be summarized as:
 \begin{align*}
-	\uparrow\text{Data}\quad+\uparrow\text{Trees}\implies\uparrow\text{Predictions' accuracy}\\
-	\downarrow\text{Data}\quad+\downarrow\text{Trees}\implies\downarrow\text{Predictions' accuracy}
+\uparrow\text{Data} + \uparrow\text{Trees} &\Rightarrow \uparrow\text{Prediction Accuracy} \\
+\downarrow\text{Data} + \downarrow\text{Trees} &\Rightarrow \downarrow\text{Prediction Accuracy}
 \end{align*}
-but more data or more trees independently will not lead to better accuracy. Then, for the data we dispose, predictions with 500 trees are the same as the ones with $300$ trees.
-
-Later, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.
-Using the results, the \emph{True Positive Rate} (Def.
+However, increasing either component in isolation—more data or more trees—does not necessarily lead to better accuracy.
+For the available dataset in this work, we observed that training with 500 trees yields similar results to training with 300 trees.
+
+Subsequently, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.
+Using the predictions, we compute the \emph{True Positive Rate} (Def.
 \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def.
@@
 \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def.
-\ref{definitionMatthewsCorrelationCoeficient}) are computed.
-Based on these computational results, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to obtain the best results.
-
-Finally, the \gls{rf} model with best statistics\footnote{The ruling criteria used to classify one model to have "better statistics" than other is discussed in section (\ref{sectionResultsAndDiscussion})} are used to predict the \gls{ic50} of the azophotoswitch prototipes classified in Appendix (\ref{appendixAzophotoshiches}).
-This procedure begins with the computation of the chemical descriptors with AlvaDesk software \cite{MauriMolecularDescriptorsBook}, then the pertinent chemical descriptors are droped and remaining only the ones the algorithm is trained with.
-Then, by inputing the computed descriptors to the \gls{rf} model the predicted \gls{ic50} pop out as an outcome and are analyzed.
+\ref{definitionMatthewsCorrelationCoeficient}).
+Based on these metrics, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to optimize model performance.
+
+Finally, the \gls{rf} model with the best performance\footnote{The criteria for determining the model with “better statistics” is discussed in Section \ref{sectionPersonCorrelationFactor} since this term references \gls{ai} statistics rather than the usual statistics.} is used to predict the \gls{ic50} values of the azophotoswitch prototypes listed in Appendix \ref{appendixAzophotoshiches}.
+This process begins with computing the chemical descriptors using AlvaDesc software \cite{MauriMolecularDescriptorsBook}.
+Irrelevant descriptors are then removed, retaining only those used during training.
+By inputting the selected descriptors into the trained \gls{rf} model, the predicted \gls{ic50} values are obtained and subsequently analyzed.
+
+Finally a docking is performed using \textcolor{blue}{Add stuff}!
 
@@
 
-In Figure (\ref{figureGraphicRecurrecyIC50}) we present the extracted \gls{ic50} data extracted from the ChEMBL database under the target ID \emph{CHEMBL230}.
-Figure (\ref{figureGraphicRecurrecyIC50}) clearly shows multiples of 10 are significantly overrepresented respect to other values.
-Additionally, by analyzing data from other proteins we can confirm this is not an exception but rather the norm.
-It looks like experimental chemists have a preference for multiples of 10, often rounding their results to the nearest value in this category.
-Consequently, an inherent error associated with these values will always be present, and we will have to deal with it.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width = \textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
-	\caption{\gls{ic50} values }
+\subsection{Available Data}\label{sectionAvailableData}
+Figure (\ref{figureGraphicRecurrecyIC50}) presents the \gls{ic50} values extracted from the ChEMBL database under target ID \emph{CHEMBL230}, limited to the interval $[0, 200]$ nM.
+The figure clearly shows that multiples of 10 are significantly overrepresented compared to other values.
+Upon analyzing data from additional proteins, we observe that this pattern is not unique to this target but appears to be a general trend.
+This suggests that experimental chemists tend to round their results to the nearest multiple of 10, introducing a systematic bias.
+As a result, a certain degree of inherent error will always be present in the dataset, and this limitation must be acknowledged and accounted for in subsequent analyses.
+This observation forms a key foundation for our later results.
+
+\begin{figure}[H]
+	\centering
+	\begin{overpic}[width=\textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
+		\put(10,55){Highly active}
+		\put(30,55){Gap}
+		\put(55,55){Least active}
+	\end{overpic}
+	\caption{\gls{ic50} values from our dataset and the creation of a 20\% gap.}
 	\label{figureGraphicRecurrecyIC50}
@@
 
-Once the chemical descriptors are computed, we proceed to calculate the Pearson correlation coefficients as defined in Definition (\ref{definitionPersonCoefficient}).
-The results are subsequently plotted in Figure (\ref{figureGraphicCorrelationFactor}).
-From the plot, we observe a “Gaussian bell” shape centered around zero, which aligns with our expectations.
-This suggests that there is no inherently preferred set of chemical descriptors for the protein, a finding that may initially seem at odds with the project’s goals.
-
-However, our hypothesis states that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}.
-This observation does not contradict that statement.
-Intuitively, we believe that filtering out descriptors with the lowest  $r^2$  values might lead to improved results.
-This possibility will be explored in subsequent discussions.
+Figure (\ref{figureGraphicRecurrecyIC50}) also illustrates the process of generating a gap in the data.
+Given a dataset, the average \gls{ic50} is first computed—approximately 47 nM in this case.
+A proportion of the data, defined by the hard-coded variable \emph{percentageErased}, is then removed to create a gap centered around the average value.
+In the figure, the full dataset is represented in blue and orange, while the blue region, centered at 47 nM, has been deleted to introduce the gap.
+In this specific example, the gap accounts for 20\% of the total data.
+
+\subsection{Correlation of Individual Descriptors with \gls{ic50}}
+
+Next, chemical descriptors were calculated using the AlvaDesc software.
+Subsequently, we computed the Pearson Correlation Coefficients\footnote{The Pearson Correlation Coefficient is sometimes denoted as $r^2$, though strictly speaking $r^2$ refers to the coefficient of determination, which is the square of the correlation coefficient.} as defined in Definition (\ref{definitionPersonCoefficient}), measuring the linear relationship between each descriptor and the corresponding \gls{ic50} value for every molecule.
+The results are visualized in Figure (\ref{figureGraphicCorrelationFactor}).
 
@@
 
-In Figure (\ref{figureGraphicGbindingIC50}) we present the results for the predicted \gls{ic50} in terms of the $\Delta G_{binding}$ provided by the Physical Chemistry Unit of the UAB.
-The exact results are stored in Appendix \ref{appendixTableOfResults} in Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}), additionall the conditions under which the Random Forest (\gls{rf}) algorithm has been trained and the statistics analysis of its predictions is stored in Table (\ref{TableConditionsMainResults}).
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
-	\caption{Graphic of the azophotoswitches from Appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
+The distribution of correlation values resembles a Gaussian bell curve centered around zero, as expected.
+This suggests that there is no dominant or inherently preferred chemical descriptor strongly associated with \gls{ic50} variation for this protein.
+While this may seem to conflict with the project's objective, it actually reinforces the importance of using ensemble methods—such as \gls{rf}, which leverage the collective contribution of weak predictors.
+
+This result is entirely expected.
+If a universally preferred descriptor existed, the use of \gls{ai} methods would be largely unnecessary, and significant advancements would likely have already been achieved through simpler statistical models.
+Nonetheless, our central hypothesis remains valid: \emph{there exists at least one combination of chemical descriptors that correlates directly with the inhibition of the target protein}.
+The observed distribution of correlation values does not contradict this hypothesis; rather, it highlights the need for models that can identify and exploit subtle multivariate relationships.
+
+It might be tempting to assume that discarding descriptors with the lowest $r^2$ values would improve model performance. This idea will be further explored in later sections.
+
+\subsection{Pearson Correlation Coefficient and Mean Squared Error}\label{sectionPersonCorrelationFactor}
+
+Once the models have been generated, i.e., once the relevant hyperparameters are set, we proceed with prediction.
+At this stage, we compute the Pearson Correlation Coefficient (Def.
+(\ref{definitionPersonCoefficient})) and the Mean Squared Error (Def.
+(\ref{definitionMeanSquaredError})) between the predicted and experimental \gls{ic50} values.
+
+Figure (\ref{FigPlotErasedPercentageVSRSquare}) presents two plots showing how both the Pearson Correlation Coefficient and the Mean Squared Error vary as a function of the erased percentage.
+These metrics provide insight into the model’s performance under different levels of data availability.
+
+From the discussion in Section \ref{sectionAvailableData}, we understand that the dataset suffers from inherent precision issues, particularly at higher $IC_{50}$ values.
+Additionally, the precision of several measurements remains unknown.
+Since our models do not incorporate uncertainty estimates for each individual data point, it is unrealistic to expect $r^2$ and mean squared error values of exactly 1 and 0, respectively.
+Some degree of variance is inevitable due to the nature of the data.
+As such, discarding more than 50\% of the dataset, regardless of what statistical metrics may suggest, would be a critical error, as it would lead to substantial information loss.
+Still, the computed values of $r^2$ and mean squared error remain useful indicators of the model's performance up to a certain threshold.
+
+\begin{figure}[H]
+\begin{tikzpicture}
+\begin{axis}[
+    width=0.45\textwidth,
+    height=8cm,
+    xlabel={$\%_{\text{Erased}}$},
+    ylabel={$r^2$},
+    xmin=0, xmax=100,
+    ymin=0.75, ymax=1.0,
+    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
+    legend pos=south east,
+    legend style={font=\small},
+    tick label style={font=\small},
+    label style={font=\small},
+]
+\addplot[
+    color=magenta,
+    mark=diamond*,
+    thick
+] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSRSquare.txt};
+\end{axis}
+\end{tikzpicture}
+\begin{tikzpicture}
+\begin{axis}[
+    width=0.45\textwidth,
+    height=8cm,
+    xlabel={$\%_{\text{Erased}}$},
+	ylabel={Mean Squared Error (nM$^2$)},
+    xmin=0, xmax=100,
+    ymin=0, ymax=200,
+    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
+    legend pos=north east,
+    legend style={font=\small},
+    tick label style={font=\small},
+    label style={font=\small}
+]
+\addplot[
+    color=magenta,
+    mark=diamond*,
+    thick
+] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSMeanSquaredError.txt};
+\end{axis}
+\end{tikzpicture}
+\caption{Plots of $\%_{\text{Erased}}$ vs $r^2$ and $\%_{\text{Erased}}$ vs Mean Squared Error.
+For a maximum $IC_{50}$ = 200 nM and a minimum of 0 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+The training is done with 200 trees.}
+\label{FigPlotErasedPercentageVSRSquare}
+\end{figure}
+
+In this work, we arbitrarily define this threshold at $r^2 = 0.90$.
+This hard-coded value is a conventional choice, established to determine the point beyond which further improvements in $r^2$ become statistically irrelevant, given the underlying noise in the data.
+This convention is loosely inspired by standards in analytical chemistry,\footnote{Particularly in analytical chemistry, two datasets are typically considered significantly correlated if their $r^2$ value exceeds 0.90.} where correlations above 0.90 are often deemed acceptable.
+However, it is important to emphasize that this threshold is subjective and should not be treated as an absolute rule.
+
+More reliable indicators of model performance are provided by the \emph{True Positive Rate} (Def.
+(\ref{definitionTruePositiveRate})), \emph{True Negative Rate} (Def.
+(\ref{definitionTrueNegativeRate})), \emph{Classification Accuracy} (Def.
+(\ref{definitionClassificationAccuracy})), and \emph{Matthews Correlation Coefficient} (Def.
+(\ref{definitionMatthewsCorrelationCoeficient})), the standard metrics used to evaluate the performance of a \gls{ml} model.
+
+Moreover, we can hypothesize that creating a larger gap in the data facilitates the model’s ability to distinguish between highly active and weakly active inhibitors.
+This intuition is reflected in the boundary cases illustrated in Figure (\ref{FigPlotErasedPercentageVSRSquare}).
+As the erased percentage approaches 100\%, the $r^2$ value tends to zero and the mean squared error approaches one.
+This indicates that, in such extreme cases, the \gls{rf} model is able to classify only the most distinct molecules, those with \gls{ic50} values near the extremes of the interval.
+However, this is not a desirable scenario, as a significant portion of intermediate data is lost, limiting the model’s capacity to generalize across the full spectrum of inhibitor activity.
+
+\subsection{Azophotoswitches Analysis}
+
+Figure \ref{figureGraphicGbindingIC50} shows the predicted \gls{ic50} values of azophotoswitch compounds as a function of their binding free energy ($\Delta G_{binding}$), as provided by the Physical Chemistry Unit of the UAB.
+Detailed prediction results can be found in Appendix \ref{appendixTableOfResults}, specifically in Tables \ref{TableMainResults1} and \ref{TableMainResults2}.
+The training conditions for the Random Forest (\gls{rf}) model, along with a comprehensive statistical analysis of its predictions, are presented in Table~\ref{TableConditionsMainResults}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
+	\caption{Predicted \gls{ic50} values for azophotoswitches from Appendix \ref{appendixAzophotoshiches}. The x-axis represents $\Delta G_{binding}$, and the y-axis represents the predicted \gls{ic50}.}
 	\label{figureGraphicGbindingIC50}
@@
 
-Furthermore, we may also show the statistics and reliability of this results in Table (\ref{TableStatisitcsMainResults}).
+Furthermore, the performance metrics for this prediction are summarized in Table (\ref{TableStatisitcsMainResults}).
+All key statistical indicators exceed the 0.90 threshold.
+Notably, the model achieves a \emph{True Negative Rate} of 0.99 (Def.
+(\ref{definitionTrueNegativeRate})), indicating that it correctly identifies non-active inhibitors 99\% of the time.
+The \emph{Classification Accuracy} (Def.
+(\ref{definitionClassificationAccuracy})) and \emph{Matthews Correlation Coefficient} both approach 1, reinforcing the reliability of this particular \gls{rf} model in distinguishing between active and inactive azophotoswitches.
 
@@
 		Mean Squared Error       & 1202.70\\\hline
-		R-squared                & 0.89\\\hline
-		ClassificationAcuracy    & 0.94\\\hline
-		MatthewsCorrelationFactor& 0.87
+		$r^2$ 	                 & 0.90\\\hline
+		True Positive            & 994\\\hline
+		False Positive           & 8\\\hline
+		True Negative            & 1015\\\hline
+		False Negative           & 101\\\hline
+		True Positive Rate       & 0.90\\\hline
+		True Negative Rate       & 0.99\\\hline
+		ClassificationAcuracy    & 0.95\\\hline
+		MatthewsCorrelationFactor& 0.90
     \end{tabular}
 \end{table}
+At this stage, it is important to note that the model is currently unable to distinguish between the active and inactive conformations of a molecule—specifically, between the \emph{cis} and \emph{trans} isomers.
+This limitation is not due to the model architecture or the way chemical descriptors are computed, but rather to a deficiency in the training data.
+The ChEMBL database \cite{ChemblDatabase} does not explicitly include \emph{cis}/\emph{trans} annotations for molecular configurations.
+Consequently, the model cannot learn to differentiate them if this distinction is not encoded in the dataset.
+As a result, the model provides \gls{ic50} predictions corresponding to the conformation it has implicitly learned, the more active configuration, which in our context is the \emph{cis} form.
+
+Nevertheless, our hypothesis is supported.
+In Figure~\ref{figureGraphicGbindingIC50}, we observe a clear correlation between the predicted \gls{ic50} values and the corresponding binding free energies ($\Delta G_{binding}$), consistent with our initial intuition: molecules with more negative free energy values tend to exhibit lower \gls{ic50} values, and are therefore more active inhibitors.
+
+The broader hypothesis—that a combination of chemical descriptors exists which correlates directly with the inhibitory power of a molecule toward a specific protein—also appears to be valid.
+However, identifying this combination manually remains a significant challenge for chemists.
+At first glance, one might believe that since this information is encoded within the \gls{rf} models, analyzing or "decrypting" the models could reveal valuable biochemical insights into the binding behavior of \gls{cox2},\footnote{Or any other protein, since the method is designed to be generalizable to any protein entry available in the ChEMBL database \cite{ChemblDatabase}.} or similar targets.
+
+Yet this decryption process is computationally infeasible.
+The internal logic of a \gls{rf} model is akin to verifying a password: it can efficiently determine whether an input is valid (e.g., predict an \gls{ic50}), but reverse-engineering the logic—such as determining which chemical descriptors most strongly influence inhibition—is significantly more complex.
+In essence, it is easy for the model to make predictions, but very difficult to extract interpretable rules or patterns from its internal structure.
+
+One might consider a brute-force approach: varying one descriptor at a time while holding all others constant, and observing the effect on the predicted \gls{ic50}.
+However, this strategy quickly runs into chemical and conceptual limitations.
+For example, altering the average bond length of a molecule could make it unrealistically large or physically unstable—resulting in a structure that is chemically invalid.
+Similarly, descriptors that are inherently discrete, such as the number of carbon atoms, could yield nonsensical results.
+A model might indicate that 25.5 carbon atoms yields optimal inhibition, which is clearly an unphysical outcome.
+In addition, arbitrarily generated sets of descriptor values may not correspond to any real molecule, making the predictions scientifically meaningless.
+
+It is important to emphasize that these limitations do not undermine the value of \gls{ai} in computational chemistry.
+Rather, they highlight the boundaries of current methods and the importance of careful dataset design, descriptor selection, and model interpretation.
+
+\subsection{Azophotoswitches Analysis}
+
+Following the prediction phase, molecular docking was performed on one of the most promising azophotoswitch candidates.
+Specifically, the molecule labeled \ref{figureCelecoxibTwoRings}.7 in Scheme(\ref{figureCelecoxibTwoRingsDoking}) was selected.
+This molecule exhibited a predicted $\Delta G_{binding}$ of $-10.6712$ kcal/mol and a \gls{ic50} prediction of 77 nM.
+An image of the final frame from the docking simulation is shown in Figure (\ref{figureDockingBestResult}).
+
+\begin{figure}[H]
+\captionsetup{type=scheme}
+\centering
+\scalebox{0.7}{
+\chemfig[angle increment=30]{
+	H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-O-*5(-N(-[-3]H)-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
+}}
+\caption{Template for Celecoxib azo-derivatives highly active molecule.}
+\label{figureCelecoxibTwoRingsDoking}
+\end{figure}
 
@@
 \end{figure}
+We observe that the azophotoswitch in the \emph{cis} configuration fits well within the \gls{cox2} binding cavity.
+Although the \emph{trans} isomer can, in theory, occupy the binding site,\footnote{With minor steric hindrances.} it is unlikely to access it in practice due to stereochemical constraints.
+Specifically, the extended structure of the \emph{trans} configuration results in steric clashes with the outer regions of \gls{cox2}, preventing entry into the binding pocket.
+
+It is also important to note that the molecule, in both \emph{E}/\emph{Z} isomeric forms, could potentially interact with unintended proteins.
+Such off-target effects could lead to significant side effects if the compound is administered as a drug.
+Therefore, further investigation is needed to evaluate its selectivity and pharmacological safety.
 
@@
 \section{Conclusions}
+
+In this work, we have demonstrated the potential of Artificial Intelligence in the fields of theoretical and computational chemistry.
+We developed a fully functional machine learning software capable of predicting \gls{ic50} values for any protein listed in the ChEMBL database.
+Moreover, the software automatically computes performance statistics for each \gls{ml} model based on a set of hard-coded parameters that define the training dataset.
+This flexibility enables users to experiment with different variable configurations to optimize predictive performance.
+
+Additionally, our results confirm the hypothesized correlation between predicted \gls{ic50} values and the experimentally or computationally derived binding free energy ($\Delta G_{binding}$).
+This relationship aligns with our chemical intuition and reinforces the validity of our methodology.
+To further validate our approach, we performed a molecular docking study of one of the most promising azophotoswitch candidates.
+The docking results were consistent with model predictions, providing additional support for the application of AI techniques in rational drug design.
+
+\newpage
+\section{Bibliography}
+\printbibliography[title = { \vspace{-1cm}}]
 
@@
 Miquel Moreno Ferrer and Dra.
-Àngels Gonzalez Lafont for allowing me to be one of his pupils and for presenting this project.
-I am also deeply grateful to PhD Alex Perez Sanchez and PhD Pedro Martínez Zaragoza for sharing their ideas and fruitful conversations
+Àngels González Lafont for allowing me to be one of his pupils and for presenting this project.
+I am also deeply grateful to PhD Àlex Pérez Sánchez and PhD Pedro Martínez Zaragoza for sharing their ideas and fruitful conversations.
 
@@
 \newpage
-\section{Bibliography}
-\printbibliography[title = { \vspace{-1cm}}]
-\newpage
-
 \appendix
@@
 
+\begin{definition}\label{definitionChemicalDescriptors}
+Molecular descriptor: "A molecular descriptor is the final result of a logical and mathematical procedure which transforms chemical information encoded within a symbolic representation of a molecule into a useful number or the result of some standardized experiment."\cite{DescriptorsBook}
+\end{definition}
+
 \begin{definition}\label{definitionCelecoxib}
@@
 		Mean Squared Error       & 1202.70\\\hline
-		R-squared                & 0.89\\\hline
+		$r^2$ 	                 & 0.90\\\hline
 		True Positive            & 994\\\hline

### 2025-05-02 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

@@
 arround $120$ nM}.
-Consecutivelly, a hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e.
-molecules).
+Consecutivelly, a hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,300]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries, i.e.
+molecules.
 
@@
 Here, the Pearson correlation coefficient (Def.
-(\ref{definitionPersonCoefficient})) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
+\ref{definitionPersonCoefficient}) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
 This relationship will be discussed in the Results and Discussion Section (\ref{sectionResultsAndDiscussion}).
@@
 This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
+
 \begin{figure}[H]
@@
 \end{figure}
+
 Afterwards, a Random Forest (\gls{rf}) algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others.
@@
 
-As described in Definition (\ref{definitionDecisionTree}), the Random Forest algorithm generates a collection of random decision trees.
+As described in definition (\ref{definitionDecisionTree}), the Random Forest algorithm generates a collection of random decision trees.
 The number of trees in the forest is a configurable parameter of the algorithm.
@@
 Each Random Forest model is unique, even if configured with the same parameters and initialized under identical conditions.
-However, experimental evidence suggests that this randomness does not significantly impact the results.
+However, experimental evidence suggests this randomness does not significantly impact the results.
 If two Random Forest algorithms are trained on the same dataset using identical parameters, their outputs will converge, even if the internal structures of their decision trees differ.
@@
 The \gls{rf} algorithm generates a large number of random decision trees (as defined by the hard-coded variable \emph{numberOfTrees}), which are trained on subsets of the training data.
-Typically, increasing the number of trees enhances the model’s predictive accuracy; however, this comes at the cost of greater computational complexity.
+Typically, increasing the number of trees enhances the model’s predictive accuracy, however, this comes at the cost of greater computational complexity.
 Importantly, prediction accuracy cannot be arbitrarily improved simply by increasing the number of trees.
 The model’s performance is fundamentally limited by the quality and quantity of the training data.
-If the data lacks sufficient information about the underlying protein-related phenomena, higher accuracy cannot be achieved regardless of how many trees are used.
-
-In general, the relationship between data quality/quantity and the number of trees can be summarized as:
+If the data lacks from information about the underlying protein-related phenomena, higher accuracy cannot be achieved regardless of how many trees are used.
+
+In general, the relationship between data quality/quantity and the number of trees can be summarized as the following
 \begin{align*}
@@
 \end{align*}
-However, increasing either component in isolation—more data or more trees—does not necessarily lead to better accuracy.
-For the available dataset in this work, we observed that training with 500 trees yields similar results to training with 300 trees.
+However, increasing either component in isolation, i.e.
+add more data or more trees, does not necessarily lead to better accuracy.
+For the available dataset in this work, we observed training with 500 trees yields similar results to training with 300 trees.
 
@@
 The figure clearly shows that multiples of 10 are significantly overrepresented compared to other values.
-Upon analyzing data from additional proteins, we observe that this pattern is not unique to this target but appears to be a general trend.
-This suggests that experimental chemists tend to round their results to the nearest multiple of 10, introducing a systematic bias.
+Upon analyzing data from additional proteins, we can confirm this is not an exception but rather the norm.
+This suggests experimental chemists tend to round their results to the nearest multiple of 10, introducing a systematic bias.
 As a result, a certain degree of inherent error will always be present in the dataset, and this limitation must be acknowledged and accounted for in subsequent analyses.
@@
 Figure (\ref{figureGraphicRecurrecyIC50}) also illustrates the process of generating a gap in the data.
-Given a dataset, the average \gls{ic50} is first computed—approximately 47 nM in this case.
+Given a dataset, the average \gls{ic50} is first computed, approximately 47 nM in this case.
 A proportion of the data, defined by the hard-coded variable \emph{percentageErased}, is then removed to create a gap centered around the average value.
-In the figure, the full dataset is represented in blue and orange, while the blue region, centered at 47 nM, has been deleted to introduce the gap.
+In Figure (\ref{figureGraphicRecurrecyIC50}), the full dataset is represented in blue and orange, while the blue region, centered at 47 nM, has been deleted to introduce the gap.
 In this specific example, the gap accounts for 20\% of the total data.
@@
 
-Next, chemical descriptors were calculated using the AlvaDesc software.
-Subsequently, we computed the Pearson Correlation Coefficients\footnote{The Pearson Correlation Coefficient is sometimes denoted as $r^2$, though strictly speaking $r^2$ refers to the coefficient of determination, which is the square of the correlation coefficient.} as defined in Definition (\ref{definitionPersonCoefficient}), measuring the linear relationship between each descriptor and the corresponding \gls{ic50} value for every molecule.
+Afterwards, chemical descriptors are calculated using the AlvaDesc software.
+Subsequently, we compute the Pearson Correlation Coefficients\footnote{The Pearson Correlation Coefficient is sometimes denoted as $r^2$, though strictly speaking $r^2$ refers to the coefficient of determination, which is the square of the correlation coefficient.} as defined in Definition (\ref{definitionPersonCoefficient}), measuring the linear relationship between each descriptor and the corresponding \gls{ic50} value for every molecule.
 The results are visualized in Figure (\ref{figureGraphicCorrelationFactor}).
@@
 This suggests that there is no dominant or inherently preferred chemical descriptor strongly associated with \gls{ic50} variation for this protein.
-While this may seem to conflict with the project's objective, it actually reinforces the importance of using ensemble methods—such as \gls{rf}, which leverage the collective contribution of weak predictors.
+While this may seem to conflict with the project's objective, it actually reinforces the importance of using ensemble methods.
 
@@
 If a universally preferred descriptor existed, the use of \gls{ai} methods would be largely unnecessary, and significant advancements would likely have already been achieved through simpler statistical models.
-Nonetheless, our central hypothesis remains valid: \emph{there exists at least one combination of chemical descriptors that correlates directly with the inhibition of the target protein}.
-The observed distribution of correlation values does not contradict this hypothesis; rather, it highlights the need for models that can identify and exploit subtle multivariate relationships.
+Nonetheless, our central hypothesis remains valid: "\emph{there exists at least one combination of chemical descriptors that correlates directly with the inhibition of the target protein}".
+The observed distribution of correlation values does not contradict this hypothesis, rather, it highlights the need for models that can identify and exploit subtle multivariate relationships.
 
@@
 
-Once the models have been generated, i.e., once the relevant hyperparameters are set, we proceed with prediction.
+Once the models have been generated, i.e., once the relevant hyperparameters are set, we proceed with generating predictions.
 At this stage, we compute the Pearson Correlation Coefficient (Def.
@@
 
-From the discussion in Section \ref{sectionAvailableData}, we understand that the dataset suffers from inherent precision issues, particularly at higher $IC_{50}$ values.
+From the discussion in Section \ref{sectionAvailableData}, we understand the dataset suffers from inherent precision issues, particularly at higher $IC_{50}$ values.
 Additionally, the precision of several measurements remains unknown.
@@
 This convention is loosely inspired by standards in analytical chemistry,\footnote{Particularly in analytical chemistry, two datasets are typically considered significantly correlated if their $r^2$ value exceeds 0.90.} where correlations above 0.90 are often deemed acceptable.
-However, it is important to emphasize that this threshold is subjective and should not be treated as an absolute rule.
-
-More reliable indicators of model performance are provided by the \emph{True Positive Rate} (Def.
-(\ref{definitionTruePositiveRate})), \emph{True Negative Rate} (Def.
-(\ref{definitionTrueNegativeRate})), \emph{Classification Accuracy} (Def.
-(\ref{definitionClassificationAccuracy})), and \emph{Matthews Correlation Coefficient} (Def.
-(\ref{definitionMatthewsCorrelationCoeficient})), the standard metrics used to evaluate the performance of a \gls{ml} model.
-
-Moreover, we can hypothesize that creating a larger gap in the data facilitates the model’s ability to distinguish between highly active and weakly active inhibitors.
+However, it is important to emphasize this threshold is subjective and should not be treated as an absolute rule.
+
+Moreover, we can hypothesize creating a larger gap in the data facilitates the model’s ability to distinguish between highly active and weakly active inhibitors.
 This intuition is reflected in the boundary cases illustrated in Figure (\ref{FigPlotErasedPercentageVSRSquare}).
@@
 
+More reliable indicators of model's performance are provided by the \emph{True Positive Rate} (Def.
+\ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def.
+\ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def.
+\ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def.
+\ref{definitionMatthewsCorrelationCoeficient}), the standard metrics used to evaluate the performance of a \gls{ml} model.
+Generally speaking, we define a method A to have "better statisitcs" than other method B if the computed quantities: \emph{True Positive Rate}, \emph{True Negative Rate}, \emph{Classification Accuracy}, and \emph{Matthews Correlation Coefficient}, for A take higher values than the same quantities for B.\footnote{Since all quantities are highly bounded by 1 we might also affirm, the closer to 1 the statistics values are the more reliable the method is.} Specifically, if this procedure for the method A and B lead to incoherences, i.e.
+some statistics of A are better than B while other are worst, we take the Matthews Correlation Factor as the most reliable statistical outcome.\footnote{This is the usual procedure in the analysis of \gls{ml} predictions\cite{MachineLearningPaper5Lipoxygenase}.}
+
 \subsection{Azophotoswitches Analysis}
 
-Figure \ref{figureGraphicGbindingIC50} shows the predicted \gls{ic50} values of azophotoswitch compounds as a function of their binding free energy ($\Delta G_{binding}$), as provided by the Physical Chemistry Unit of the UAB.
+Figure \ref{figureGraphicGbindingIC50} shows the predicted \gls{ic50} values of azophotoswitch compounds as a function of their binding free energy ($\Delta G_{binding}$), as provided by the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}.
 Detailed prediction results can be found in Appendix \ref{appendixTableOfResults}, specifically in Tables \ref{TableMainResults1} and \ref{TableMainResults2}.
@@
 \end{table}
-At this stage, it is important to note that the model is currently unable to distinguish between the active and inactive conformations of a molecule—specifically, between the \emph{cis} and \emph{trans} isomers.
+At this stage, it is important to note that the model is currently unable to distinguish between the active and inactive conformations of a molecule, i.e, between the \emph{cis} and \emph{trans} isomers.
 This limitation is not due to the model architecture or the way chemical descriptors are computed, but rather to a deficiency in the training data.
-The ChEMBL database \cite{ChemblDatabase} does not explicitly include \emph{cis}/\emph{trans} annotations for molecular configurations.
-Consequently, the model cannot learn to differentiate them if this distinction is not encoded in the dataset.
+The ChEMBL database \cite{ChemblDatabase} does not explicitly include \emph{cis}/\emph{trans} comparable molecular configurations.
+In other words, if (Z)/(E) isomerization appears we can only find one of the two conformations in the database, typically the one with higher inhibition potential.
+Consequently, the model cannot learn to differentiate them since this distinction is not encoded in the dataset.
 As a result, the model provides \gls{ic50} predictions corresponding to the conformation it has implicitly learned, the more active configuration, which in our context is the \emph{cis} form.
@@
 Nevertheless, our hypothesis is supported.
-In Figure~\ref{figureGraphicGbindingIC50}, we observe a clear correlation between the predicted \gls{ic50} values and the corresponding binding free energies ($\Delta G_{binding}$), consistent with our initial intuition: molecules with more negative free energy values tend to exhibit lower \gls{ic50} values, and are therefore more active inhibitors.
-
-The broader hypothesis—that a combination of chemical descriptors exists which correlates directly with the inhibitory power of a molecule toward a specific protein—also appears to be valid.
+In Figure~\ref{figureGraphicGbindingIC50}, we observe a clear correlation between the predicted \gls{ic50} values and the corresponding binding free energies ($\Delta G_{binding}$), consistent with our initial intuition that molecules with more negative free energy values tend to exhibit lower \gls{ic50} values, and are, therefore, more active inhibitors.
+
+The broader hypothesis that a combination of chemical descriptors exists which correlates directly with the inhibitory power of a molecule toward a specific protein also appears to be valid.
 However, identifying this combination manually remains a significant challenge for chemists.
@@
 Yet this decryption process is computationally infeasible.
-The internal logic of a \gls{rf} model is akin to verifying a password: it can efficiently determine whether an input is valid (e.g., predict an \gls{ic50}), but reverse-engineering the logic—such as determining which chemical descriptors most strongly influence inhibition—is significantly more complex.
+The internal logic of a \gls{rf} model is akin to verifying a password.
+It can efficiently determine whether an input is valid (e.g., predict an \gls{ic50} from a molecule's descriptors or checking a username and a password), but reverse-engineering (e.g., determining which chemical descriptors most strongly influence inhibition or cracking a user password) is significantly more complex.
 In essence, it is easy for the model to make predictions, but very difficult to extract interpretable rules or patterns from its internal structure.
 
-One might consider a brute-force approach: varying one descriptor at a time while holding all others constant, and observing the effect on the predicted \gls{ic50}.
-However, this strategy quickly runs into chemical and conceptual limitations.
-For example, altering the average bond length of a molecule could make it unrealistically large or physically unstable—resulting in a structure that is chemically invalid.
+One might consider a brute-force approach, varying one descriptor at a time while holding all others constant, and observing the effect on the predicted \gls{ic50}.
+However, this strategy quickly runs into chemical contradictions and incoherences.
+For example, altering the average bond length of a molecule could make it unrealistically large or physically unstable, resulting in a structure that is chemically invalid although this hypothetic molecule might perfectly fit in the \gls{cox2} binding site.
 Similarly, descriptors that are inherently discrete, such as the number of carbon atoms, could yield nonsensical results.
@@
 
-It is important to emphasize that these limitations do not undermine the value of \gls{ai} in computational chemistry.
-Rather, they highlight the boundaries of current methods and the importance of careful dataset design, descriptor selection, and model interpretation.
+It is important to emphasize these limitations do not undermine the value of \gls{ai} in computational chemistry.
+Rather, they highlight the boundaries of current methods and the importance of careful dataset design, descriptor selection, model interpretation and understanding the machine's workflow.
 
@@
 \end{figure}
-We observe that the azophotoswitch in the \emph{cis} configuration fits well within the \gls{cox2} binding cavity.
+We observe the azophotoswitch in the \emph{cis} configuration happens to fit well within the \gls{cox2} binding cavity.
 Although the \emph{trans} isomer can, in theory, occupy the binding site,\footnote{With minor steric hindrances.} it is unlikely to access it in practice due to stereochemical constraints.
@@
 
-It is also important to note that the molecule, in both \emph{E}/\emph{Z} isomeric forms, could potentially interact with unintended proteins.
+It is also important to note the molecule, in both \emph{E}/\emph{Z} isomeric forms, could potentially interact with unintended proteins.
 Such off-target effects could lead to significant side effects if the compound is administered as a drug.
@@
 
-Additionally, our results confirm the hypothesized correlation between predicted \gls{ic50} values and the experimentally or computationally derived binding free energy ($\Delta G_{binding}$).
+Despite their usefulness, the models exhibit several limitations.
+They are entirely dependent on the training dataset, therefore, any lack of information or approximations in the data can lead to systematic errors in their predictions.
+Furthermore, the models are inherently unable to generate new knowledge.
+For instance, the distinction between cis and trans conformations is not represented in the ChEMBL \gls{cox2} database.
+As a result, our models are unable to provide different \gls{ic50} predictions for these two configurations.
+Nonetheless, we have demonstrated that the predictions are reliable within a certain threshold, as determined by the statistical analysis of each case.
+
+Additionally, our results confirm the hypothesized correlation between predicted \gls{cox2}'s \gls{ic50} values and the experimentally or computationally derived binding free energy ($\Delta G_{binding}$).
 This relationship aligns with our chemical intuition and reinforces the validity of our methodology.

### 2025-05-03 Manuscript/GeneralSources/decisionTree.tex
writting

\documentclass{standalone}
\usepackage[edges]{forest}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shadows.blur,arrows.meta}

\begin{document}

\begin{forest}
%for tree={
%  grow=east,
%  draw,
%  rounded corners,
%  text width=4.5cm,
%  align=flush center,
%  parent anchor=east,
%  child anchor=west,
%  edge={->, thick},
%  l sep=10mm,
%  s sep=10mm
%}
[Does the molecule have no symmetry elements other than $E$?
  [Yes\\\textbf{Point group: } $C_1$]
  [No
    [Does the molecule have only a mirror plane?
      [Yes\\\textbf{Point group: } $C_s$]
      [No
        [Does the molecule have only an inversion center?
          [Yes\\\textbf{Point group: } $C_i$]
          [No
            [Does the molecule have a proper rotation axis $C_n$?
              [No\\\textbf{Unclassified: recheck symmetry elements}]
              [Yes
                [Does it have $n$ vertical mirror planes ($\sigma_v$)?
                  [Yes\\\textbf{Point group: } $C_{nv}$]
                  [No
                    [Does it have a horizontal mirror plane ($\sigma_h$)?
                      [Yes\\\textbf{Point group: } $C_{nh}$]
                      [No\\\textbf{Point group: } $C_n$]
                    ]
                  ]
                ]
              ]
            ]
          ]
        ]
      ]
    ]
  ]
]
\end{forest}

\end{document}

### 2025-05-03 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

@@
 %-------------LINKS AND LOOKS-----------%
+\usepackage{siunitx}
 \usepackage{fullpage}
@@
 \pagenumbering{arabic}
-\section{Introduction}
+\section{Introduction}\label{sectionIntroduction}
 The impact of \gls{ai} on science has been nothing short of a groundbreaking revolution, with few comparable precedents.
@@
 
+All in all, this project demonstrates the application of \gls{ai} in drug design, promoting its integration into chemical computations as an initial step prior to experimental investigations.
+Such tools can help avoid time-consuming and costly unproductive experiments, assisting both theoretical and experimental chemists by providing fast computational insights into molecular properties, thus offering valuable intuition before proceeding to laboratory work.
+
+\newpage
+\section{Objectives}
+
+This project aims to develop a fully functional software tool capable of accurately predicting a molecule’s inhibition potential (\gls{ic50}), leveraging existing data from the ChEMBL database \cite{ChemblDatabase}.
+The software is thoroughly documented and available in the GitHub repository: \href{https://github.com/SirSergi0/Repository—AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI Application for Azophotoswitches Optimization with Pharmacological Interest}} \cite{GitHub}.
+
+The project specifically focuses on the \gls{cox2} protein.
+Thanks to the availability of a large \gls{ic50} dataset for this target, the model’s predictive reliability can be effectively validated.
+The prediction process is powered by an \gls{ai} tool designed to deliver high-quality results, taking into account relevant molecular descriptors.
+The software also serves to cross-check computational results previously obtained by the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}.
+The application centers on azophotoswitches—molecules of particular pharmacological interest discussed in Section \ref{sectionIntroduction}.
+Additionally, a molecular docking study is performed on one of the most promising azophotoswitch candidates.
+
 In conclusion, this study seeks to bridge the gap between Artificial Intelligence and computational chemistry, demonstrating AI’s potential to revolutionize drug discovery and molecular research.
@@
 Furthermore, identifying key molecular descriptors linked to inhibition may provide valuable insights into chemical interactions, opening new directions for research in medicinal chemistry and bioinformatics.
-\newpage
-\section{Objectives}
 
@@
 
-Finally a docking is performed using \textcolor{blue}{Add stuff}!
+Finally, a docking study was performed using GOLD2022 \cite{GoldReference}.
+This software employs a genetic algorithm, along with molecular modeling techniques, to predict the optimal binding pose of the ligand within the \gls{cox2} binding site.
+The genetic nature of the algorithm allows for a broad exploration of the conformational and positional space between the ligand and the protein.
+By evaluating and ranking ligand poses based on predicted interactions, such as hydrogen bonding, van der Waals forces, and metal coordination, unstable or energetically unfavorable conformations are discarded, resulting in a set of plausible, energetically stable binding orientations.
+The docking calculations were carried out within a 26 Å radius sphere centered at Arg513.
 
@@
 \caption{Chemical graph of Celecoxib.}
-\addcontentsline{lof}{figure}{Chemical graph of Celecoxib.}
 \label{CelecoxibFigure}
@@
 \caption{Chemical graph of Rofecoxib.}
-\addcontentsline{lof}{figure}{Chemical graph of Rofecoxib.}
 \label{RofecoxibFigure}

### 2025-05-25 Manuscript/Plantilla memòria TFG 2024_25.tex
Adding license

@@
 
-\includegraphics[width = 6.1cm]{GeneralSources/Logo_uab.png}\\[1.76cm] % Include a department/university logo - this will require the graphicx package
+\includegraphics[width = 6.1cm]{GeneralSources/Logo_uab.pdf}\\[1.76cm] % Include a department/university logo - this will require the graphicx package
 
@@
 The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.
+The consultace of this repository is highly recommended in order to comprehended the insights in the workflow of the project.
+By the time this project is presented, it remains as a open-source repository for the Computational Chemistry UAB unit \cite{UAB_ComputationalChemistry}.
 

### 2025-05-28 Manuscript/Plantilla memòria TFG 2024_25.tex
miquel's moreno corrections

@@
 \newacronym{fn}{FN}{False Negative}
+\newglossaryentry{smiles}{name={SMILES},description={\mbox{Simplified Molecular Input Line Entry System}}}
+%!TEX encoding = UTF-8 Unicode\newacronym{smiles}{SMILES}{Simplified Molecular Input Line Entry System}
 
@@
 
-The main objective of the project is to develop software capable of generating AIs that can predict the 50\% inhibition concentration (IC$_{50}$) for COX-2\footnote{In reality, the software works for any protein with an entry in the ChEMBL database \cite{ChemblDatabase}, although the study focuses on COX-2.} with the highest possible accuracy.
+The main objective of the project is to develop software capable of generating AIs that can predict the 50\% inhibition concentration (IC$_{50}$) for COX-2\footnote{Actually, the software works for any protein with an entry in the ChEMBL database \cite{ChemblDatabase}, although the study focuses on COX-2.} with the highest possible accuracy.
 To achieve this, all known molecular data with an established inhibition potential for COX-2 are extracted.
@@
 However, if this cell reproduction continues beyond the healing of the damaged tissue, it can potentially lead to cancer, contradicting the initial healing purpose of the inflammatory process.
-In some cases, inflammation can become chronic, leading to tumor development and uncontrolled cell proliferation.
+In some cases, inflammation can become chronic, leading to tumour development and uncontrolled cell proliferation.
 As a result, a wide range of drug prototypes have been designed to suppress inflammation.
 However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications.
-Consequently, the administration of these drugs is often contrindicative, and the search for a more effective and safer treatment remains ongoing.
-Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process and responsable to convert the arachidonic acid to prostaglandin \ch{H_2} (Scheme (\ref{Cox2MainReaction})).
+Consequently, the administration of these drugs is often contraindicative, and the search for a more effective and safer treatment remains ongoing.
+Plenty of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process and responsible to convert the arachidonic acid to prostaglandin \ch{H_2} (Scheme (\ref{Cox2MainReaction})).
 Subsequently, a therapy based on the chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.
@@
 
-Determining an experimental \gls{ic50} value can be both costly and time-consuming\footnote{Usually this parameter is computed throughout the Cheng Prusoff Equation (Def.
-(\ref{definitionChengPrusoff})) with experimental data.}.
+Determining an experimental \gls{ic50} value can be both costly and time-consuming\footnote{Usually this parameter is computed throughout the Cheng Prusoff Equation (Definition (\ref{definitionChengPrusoff})) with experimental data.}.
 On the other hand, \gls{ai} provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.
@@
 We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset.
-The chemical descriptors (Def.
-(\ref{definitionChemicalDescriptors})) of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
+The chemical descriptors (Definition (\ref{definitionChemicalDescriptors})) \footnote{All the definitions are stored in the Appendix (\ref{appendixRellevantDefinitions}) \emph{Relevant definitions}.
+We recommend its consultance for further information.}  of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
 Around 5000 descriptors are calculated\cite{DescriptorsBook}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour.
@@
 
-Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin.
+Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{DefinitionCOX2CancerDictionary} such as the popular ibuprofen or aspirin.
 However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others.
@@
 
-We define a molecule as an azophotoswitch if it contains an azo bond (\ch{N=N}) that is sensitive to configurational transformations upon photo-excitation.
-For instance, let us consider the case of (E/Z)-N,1-diphenylmethanimine,
+We define a molecule as a \emph{photoswitch} if it contains a bond that undergoes a configurational transformation upon photoexcitation.
+In particular, we take \emph{azophotoswitches} as a class of photoswitches in which the photo-sensitive bond responsible for isomerization is an azo group (i.e.
+\ch{N=N}).
+Azophotoswitches represent the most common and widely studied type of photoswitches due to their robust and tunable photochemical properties.
+For instance, consider the case of \emph{(cis/trans)-N,1-diphenylmethanimine},
 \begin{figure}[H]
@@
 \schemestop
-	\caption{(E/Z)-N,1-diphenylmethanimine conversion as an example of an azophotoswitch.}
+	\caption{(cis/trans)-N,1-diphenylmethanimine conversion as an example of an azophotoswitch.}
 \label{AzophotoswitchExampleFigure}
 \end{figure}
-The photo-induced E/Z isomerization leads to distinct bioactivities for each configuration.
+The photo-induced cis/trans isomerization leads to distinct bioactivities for each configuration.
 This variation arises from the stereochemical constraints required for a molecule to bind to a target protein.
@@
 The software also serves to cross-check computational results previously obtained by the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}.
-The application centers on azophotoswitches—molecules of particular pharmacological interest discussed in Section \ref{sectionIntroduction}.
+The application centers on azophotoswitches, molecules of particular pharmacological interest as discussed in Section \ref{sectionIntroduction}.
 Additionally, a molecular docking study is performed on one of the most promising azophotoswitch candidates.
@@
 \section{Methodology}\label{sectionMethodology}
-The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.
-The consultace of this repository is highly recommended in order to comprehended the insights in the workflow of the project.
-By the time this project is presented, it remains as a open-source repository for the Computational Chemistry UAB unit \cite{UAB_ComputationalChemistry}.
+The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project.
+The consultace of this repository is highly recommended in order to comprehended the insights and the workflow of the project.
+By the time this project is presented, it remains as an open-source repository of the MolBioMed research group \cite{molbiomed}.
 
 The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database\cite{ChemblDatabase}.
-Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Def.
-\ref{definitionIC50}) with a limit of 1000 entries per request.
+Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Definition \ref{definitionIC50}) with a limit of 1000 entries per request.
 The process is iterated until all data is extracted leading a total of 7979 molecules.
 Hence the datasheet is processed in pandas dataframes\cite{PythonPackagePandas} and encrypted into binary feather files to optimise reading-writting speed.
-By removing entries with the same canonical smiles a total of 5112 molecules remain.
-Among this entries well known drugs such as Celecoxib (Def.
-\ref{definitionCelecoxib}), Rofecoxib (Def.
-\ref{definitionRofecoxib}) or even Ibuprofen can be found.
+By removing entries with the same canonical \gls{smiles} (Definition \ref{definitionSMILES})  a total of 5112 molecules remain.
+Among this entries well known drugs such as Celecoxib (Definition \ref{definitionCelecoxib}), Rofecoxib (Definition \ref{definitionRofecoxib}) or even Ibuprofen can be found.
 However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure.
@@
 With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule.
-Still, some chemical descriptor need from the presence of a certain atom, for instance a chemical descriptor related to presence of a metal in the molecule, or active gorup, for example chemical descriptor related to the presence of a carboxilic acid, or chemical descriptor related triple bound among other possiblities.
+Still, some chemical descriptor need from the presence of a certain atom, for instance a chemical descriptor related to the presence of a metal in the molecule, or active gorup, for example chemical descriptor related to the presence of a carboxilic acid, or chemical descriptor related triple bound among other possiblities.
 The computation of this chemical descriptors appear as \emph{null values}.
 By deleting molecular descriptors with null values 2917 chemical descriptors remain.
-Here, the Pearson correlation coefficient (Def.
-\ref{definitionPersonCoefficient}) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
+Here, the Pearson correlation coefficient (Definition \ref{definitionPersonCoefficient}) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
 This relationship will be discussed in the Results and Discussion Section (\ref{sectionResultsAndDiscussion}).
@@
 By doing so, it is possible to compute the classification accuracy statistics of the model from the cluster association of each prediction.
-Thus we can compare each prediction of each molecules to experimental data, i.e.
-the model predicts a molecule to be highly active molecule to a highly active molecule this will be denoted as a \gls{tp}.
-Similarly we can define a \gls{tn}, \gls{fp} and \gls{fn} .
+Thus we can compare each prediction of each molecules with experimental data.
+For instance, for an experimentally proved highly active molecule if the model predicts this molecule to be highly active (has a low \gls{ic50} precition) we consider this as \gls{tp}.
+Similarly we define a \gls{tn}, \gls{fp} and \gls{fn} .
 This procedure is an standard for evaluating a \gls{ml} model realiability.
@@
 
-As described in definition (\ref{definitionDecisionTree}), the Random Forest algorithm generates a collection of random decision trees.
+As described in Definition (\ref{definitionDecisionTree}), the Random Forest algorithm generates a collection of random decision trees.
 The number of trees in the forest is a configurable parameter of the algorithm.
@@
 The \gls{rf} algorithm generates a large number of random decision trees (as defined by the hard-coded variable \emph{numberOfTrees}), which are trained on subsets of the training data.
-Typically, increasing the number of trees enhances the model’s predictive accuracy, however, this comes at the cost of greater computational complexity.
+Typically, increasing the number of trees enhances the model’s predictive accuracy.
+However, this comes at the cost of greater computational complexity.
 Importantly, prediction accuracy cannot be arbitrarily improved simply by increasing the number of trees.
@@
 However, increasing either component in isolation, i.e.
-add more data or more trees, does not necessarily lead to better accuracy.
-For the available dataset in this work, we observed training with 500 trees yields similar results to training with 300 trees.
+adding more data or more trees, does not necessarily lead to better accuracy.
+For the available dataset in this work, we observed training with 500 trees yields similar results respect the ones obtained by training with 300 trees.
 
 Subsequently, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.
-Using the predictions, we compute the \emph{True Positive Rate} (Def.
-\ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def.
-\ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def.
-\ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def.
-\ref{definitionMatthewsCorrelationCoeficient}).
+Using the predictions, we compute the \emph{True Positive Rate} (Definition \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Definition \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Definition \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Definition \ref{definitionMatthewsCorrelationCoeficient}).
 Based on these metrics, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to optimize model performance.
@@
 Irrelevant descriptors are then removed, retaining only those used during training.
-By inputting the selected descriptors into the trained \gls{rf} model, the predicted \gls{ic50} values are obtained and subsequently analyzed.
+By introducing the selected descriptors into the trained \gls{rf} model, the predicted \gls{ic50} values are obtained and subsequently analyzed.
 
@@
 The genetic nature of the algorithm allows for a broad exploration of the conformational and positional space between the ligand and the protein.
-By evaluating and ranking ligand poses based on predicted interactions, such as hydrogen bonding, van der Waals forces, and metal coordination, unstable or energetically unfavorable conformations are discarded, resulting in a set of plausible, energetically stable binding orientations.
+By evaluating and ranking ligand interactions, such as hydrogen bonding, van der Waals forces, and metal coordination, unstable or energetically unfavorable conformations are discarded, resulting in a set of plausible, energetically stable binding orientations.
 The docking calculations were carried out within a 26 Å radius sphere centered at Arg513.
@@
 Once the models have been generated, i.e., once the relevant hyperparameters are set, we proceed with generating predictions.
-At this stage, we compute the Pearson Correlation Coefficient (Def.
-(\ref{definitionPersonCoefficient})) and the Mean Squared Error (Def.
-(\ref{definitionMeanSquaredError})) between the predicted and experimental \gls{ic50} values.
+At this stage, we compute the Pearson Correlation Coefficient (Definition (\ref{definitionPersonCoefficient})) and the Mean Squared Error (Definition (\ref{definitionMeanSquaredError})) between the predicted and experimental \gls{ic50} values.
 
@@
 
-More reliable indicators of model's performance are provided by the \emph{True Positive Rate} (Def.
-\ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def.
-\ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def.
-\ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def.
-\ref{definitionMatthewsCorrelationCoeficient}), the standard metrics used to evaluate the performance of a \gls{ml} model.
+More reliable indicators of model's performance are provided by the \emph{True Positive Rate} (Definition \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Definition \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Definition \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Definition \ref{definitionMatthewsCorrelationCoeficient}), the standard metrics used to evaluate the performance of a \gls{ml} model.
 Generally speaking, we define a method A to have "better statisitcs" than other method B if the computed quantities: \emph{True Positive Rate}, \emph{True Negative Rate}, \emph{Classification Accuracy}, and \emph{Matthews Correlation Coefficient}, for A take higher values than the same quantities for B.\footnote{Since all quantities are highly bounded by 1 we might also affirm, the closer to 1 the statistics values are the more reliable the method is.} Specifically, if this procedure for the method A and B lead to incoherences, i.e.
@@
 	\centering
-	\includegraphics[width=0.7\textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
+	\includegraphics[width=0.7\textwidth, trim={1.5cm 0.6cm 2.4cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
 	\caption{Predicted \gls{ic50} values for azophotoswitches from Appendix \ref{appendixAzophotoshiches}. The x-axis represents $\Delta G_{binding}$, and the y-axis represents the predicted \gls{ic50}.}
@@
 
-Furthermore, the performance metrics for this prediction are summarized in Table (\ref{TableStatisitcsMainResults}).
+Furthermore, the performance metrics of the \gls{rf} model for this predictions are summarized in Table (\ref{TableStatisitcsMainResults}) that yield the results of Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}) from the appendix (\ref{appendixTableOfResults}) \emph{Tables of results}.
 All key statistical indicators exceed the 0.90 threshold.
-Notably, the model achieves a \emph{True Negative Rate} of 0.99 (Def.
-(\ref{definitionTrueNegativeRate})), indicating that it correctly identifies non-active inhibitors 99\% of the time.
-The \emph{Classification Accuracy} (Def.
-(\ref{definitionClassificationAccuracy})) and \emph{Matthews Correlation Coefficient} both approach 1, reinforcing the reliability of this particular \gls{rf} model in distinguishing between active and inactive azophotoswitches.
+Notably, the model achieves a \emph{True Negative Rate} of 0.99 (Definition (\ref{definitionTrueNegativeRate})), indicating that it correctly identifies non-active inhibitors 99\% of the time.
+The \emph{Classification Accuracy} (Definition (\ref{definitionClassificationAccuracy})) and \emph{Matthews Correlation Coefficient} both approach 1, reinforcing the reliability of this particular \gls{rf} model in distinguishing between active and inactive azophotoswitches.
 
@@
     \centering	
-	\caption{Statistics for the computation of the results from tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
+	\caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
 	\label{TableStatisitcsMainResults}
@@
 The ChEMBL database \cite{ChemblDatabase} does not explicitly include \emph{cis}/\emph{trans} comparable molecular configurations.
-In other words, if (Z)/(E) isomerization appears we can only find one of the two conformations in the database, typically the one with higher inhibition potential.
+In other words, if cis/trans isomerization appears we can only find one of the two conformations in the database, typically the one with higher inhibition potential.
 Consequently, the model cannot learn to differentiate them since this distinction is not encoded in the dataset.
@@
 
-It is important to emphasize these limitations do not undermine the value of \gls{ai} in computational chemistry.
+It is important to emphasize that these limitations do not undermine the value of \gls{ai} in computational chemistry.
 Rather, they highlight the boundaries of current methods and the importance of careful dataset design, descriptor selection, model interpretation and understanding the machine's workflow.
@@
 
-Following the prediction phase, molecular docking was performed on one of the most promising azophotoswitch candidates.
-Specifically, the molecule labeled \ref{figureCelecoxibTwoRings}.7 in Scheme(\ref{figureCelecoxibTwoRingsDoking}) was selected.
+Following the prediction phase, molecular docking is performed on one of the most promising azophotoswitch candidates.
+Specifically, we select the molecule labeled as "\emph{\ref{figureCelecoxibTwoRings}.7}" in appendix \ref{appendixAzophotoshiches} \emph{Tables of azophotoswitches}, which is depicted in Scheme(\ref{figureCelecoxibTwoRingsDoking}).
 This molecule exhibited a predicted $\Delta G_{binding}$ of $-10.6712$ kcal/mol and a \gls{ic50} prediction of 77 nM.
@@
 
-It is also important to note the molecule, in both \emph{E}/\emph{Z} isomeric forms, could potentially interact with unintended proteins.
+It is also important to note that the molecule, in both cis/trans isomeric forms, could potentially interact with unintended proteins.
 Such off-target effects could lead to significant side effects if the compound is administered as a drug.
@@
 Miquel Moreno Ferrer and Dra.
-Àngels González Lafont for allowing me to be one of his pupils and for presenting this project.
+Àngels González Lafont for allowing me to be one of thei pupils and for presenting this project.
 I am also deeply grateful to PhD Àlex Pérez Sánchez and PhD Pedro Martínez Zaragoza for sharing their ideas and fruitful conversations.
@@
 
-Molecular graphics and analyses performed with UCSF ChimeraX, developed by the Resource for Biocomputing, Visualization, and Informatics at the University of California, San Francisco, with support from National Institutes of Health R01-GM129325 and the Office of Cyber Infrastructure and Computational Biology, National Institute of Allergy and Infectious Diseases.
-
+Molecular graphics and analyses were performed with UCSF ChimeraX, developed by the Resource for Biocomputing, Visualization, and Informatics at the University of California, San Francisco, with support from National Institutes of Health R01-GM129325 and the Office of Cyber Infrastructure and Computational Biology, National Institute of Allergy and Infectious Diseases.
+
+\newpage
+\thispagestyle{empty}
+\mbox{} 
 \newpage
 \appendix
-\section{Rellevant definitions}
+\section*{\huge Appendices}
+\addcontentsline{toc}{section}{Appendices}
+\section{Rellevant definitions}\label{appendixRellevantDefinitions}
 \begin{definition}\label{definitionIC50}
@@
 Note that $r_{xy}\in[-1,1]$.
-Therefore the sign of $r_{xy}$ is tightly related to the sign of alinear regression, more precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
+Therefore the sign of $r_{xy}$ is tightly related to the sign of a linear regression.
+More precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
 \end{definition}
@@
 \end{align}
-The name of this quantity is self-descriptive, since $X_i-Y_i$ is the error associated to the i-th prediction and the MSE is the mean of the squares of this erros.
+The name of this quantity is self-descriptive, since $X_i-Y_i$ is the error associated to the i-th prediction and the MSE is the mean of the squares of this error.
 \end{definition}
@@
 \begin{definition}\label{definitionDecisionTree}
-A decision tree is a classification algorithm based on a series of ordered \emph{if} statements.
+A decision tree is a classification algorithm based on a series of ordered "\texttt{if}" statements.
 The algorithm begins at the top of the tree, where a question is posed to the data.
@@
 
-This kind of algorithm is vividly present in the chemical landscape, for instance in the spectroscopy realm the determination of a molecule's symmetry group is provided by a decision tree such as Figure (\ref{figExScpectroDecisionTree}).
+This kind of algorithm is vividly present in the chemical landscape, for instance in the spectroscopy realm the determination of a molecule's symmetry group is provided by a decision tree depicted in Figure (\ref{figExScpectroDecisionTree}).
 \begin{figure}[H]
@@
 \end{figure}
+\end{definition}
+
+\begin{definition}\label{definitionSMILES}
+Canonical Simplified Molecular Input Line Entry System (SMILES): A text-based notation that encodes a molecule’s structure as a linear string, containing all the essential information needed to reconstruct its 3D representation \cite{smiles}.
+SMILES files typically use the extensions \texttt{.smi} or \texttt{.smiles}.
 \end{definition}
@@
 \end{table}
-\begin{figure}[H]
-\captionsetup{type=scheme}
-\centering
-\scalebox{0.8}{
-\chemname{\chemfig[angle increment=30]{
-H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
-}}{Pyridine derivative}}
-\par
-\vspace{0.5cm}
-\scalebox{0.8}{
-\chemname{\chemfig[angle increment=30]{
-H_3C-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
-}}{\ch{SO_2CH_3} group derivative}}
-\caption{Scheme for Celecoxib azo-derivatives based on pyridine and \ch{SO_2CH_3} groups.}
-\label{tableCelecoxibPyridine}
-\end{figure}
+%\begin{figure}[H]
+%\captionsetup{type=scheme}
+%\centering
+%\scalebox{0.8}{
+%\chemname{\chemfig[angle increment=30]{
+%H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
+%}}{Pyridine derivative}}
+%\par
+%\vspace{0.5cm}
+%\scalebox{0.8}{
+%\chemname{\chemfig[angle increment=30]{
+%H_3C-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
+%}}{\ch{SO_2CH_3} group derivative}}
+%\caption{Scheme for Celecoxib azo-derivatives based on pyridine and \ch{SO_2CH_3} groups.}
+%\label{tableCelecoxibPyridine}
+%\end{figure}
 
@@
 \caption{Template for Celecoxib azo-derivatives with indole ring as a heterocycle.}
+\label{figureCelecoxibIndole2}
 \end{figure}
@@
 
-\section{Table of results}\label{appendixTableOfResults}
+\section{Tables of results}\label{appendixTableOfResults}
+
+Notice some molecules data do not appear in Table \ref{TableMainResults1}. This is due to inconclusives results of the $\Delta G_{binding}$ conputations.
+
 \begin{table}[H]
@@
         Indole & \ref{figureCelecoxibIndole}.2 & \ch{F} &  &  & -6.3397 & 108\\ \hline
-        Indole & \ref{figureCelecoxibIndole}.3 &  &  &  & -5.532 & 111\\ \hline
+        Indole & \ref{figureCelecoxibIndole2} &  &  &  & -5.532 & 111\\ \hline
         TwoRings & \ref{figureCelecoxibTwoRings}.2 & \ch{NH} & O & \ch{H} & -2.2146 & 165\\ \hline
@@
     \centering	
-	\caption{Conditions and statistics for the computation of the results from tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
+	\caption{Conditions and statistics for the machine's learning models for the computation of the \gls{ic50} from Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
 	\label{TableConditionsMainResults}

### 2025-05-28 Scripts/plotAzophotoSwitches.py

@@ -16,10 +16,12 @@ Prediction = Prediction.drop('Unnamed: 8', axis=1)
 for i in range(7):
     Prediction = Prediction.drop(52-i, axis=0)
 
+Fontisze = 16
+
 plt.figure(figsize=(10, 7))
 plt.scatter(Prediction['Gbinding'],Prediction['Predictions'], color = 'purple')
-plt.xlabel('$\Delta G_{binding}$ (Kcal/mol)')
-plt.ylabel('Predicted $IC_{50}$ (nM)')
+plt.xlabel('$\Delta G_{binding}$ (Kcal/mol)', fontsize=Fontisze)
+plt.ylabel('Predicted $IC_{50}$ (nM)', fontsize=Fontisze)
 # plt.xlim(-12,12)
 # plt.ylim(80,320)
 # plt.show()

### 2025-06-02 Manuscript/Plantilla memòria TFG 2024_25.tex
Stuff

@@
 %----------FONT AND GEOMETRY DEFINITION----------%
-\usepackage[a4paper, hmargin=3.0cm, vmargin=3.0cm]{geometry}
+\usepackage[a4paper, top=3.0cm, bottom=3.0cm, left = 3.0cm, right = 3.0cm]{geometry}
 \voffset = -0.75cm
@@
 \setstretch{1.5}
+\usepackage[table]{xcolor}
 
@@
 This project aims to develop a fully functional software tool capable of accurately predicting a molecule’s inhibition potential (\gls{ic50}), leveraging existing data from the ChEMBL database \cite{ChemblDatabase}.
-The software is thoroughly documented and available in the GitHub repository: \href{https://github.com/SirSergi0/Repository—AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI Application for Azophotoswitches Optimization with Pharmacological Interest}} \cite{GitHub}.
+The software is thoroughly documented and available in the GitHub repository: \href{https://github.com/SirSergi0/Repository—AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI Application for Azophotoswitches Optimization with Pharmacological Interest}} \cite{GitHub}\cite{azophotoswitches2025}.
 
@@
 \section{Methodology}\label{sectionMethodology}
-The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project.
+The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project\cite{azophotoswitches2025}.
 The consultace of this repository is highly recommended in order to comprehended the insights and the workflow of the project.
@@
 
+%\begin{table}[H]
+%    \centering	
+%	\caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
+%	\label{TableStatisitcsMainResults}
+%	\begin{tabular}{c|c}
+%		Mean Squared Error       & 1202.70\\\hline
+%		$r^2$ 	                 & 0.90\\\hline
+%		True Positive            & 994\\\hline
+%		False Positive           & 8\\\hline
+%		True Negative            & 1015\\\hline
+%		False Negative           & 101\\\hline
+%		True Positive Rate       & 0.90\\\hline
+%		True Negative Rate       & 0.99\\\hline
+%		ClassificationAcuracy    & 0.95\\\hline
+%		MatthewsCorrelationFactor& 0.90
+%    \end{tabular}
+%\end{table}
+
 \begin{table}[H]
     \centering
-	\caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
+    \caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables~\ref{TableMainResults1} and~\ref{TableMainResults2}.}
     \label{TableStatisitcsMainResults}
-	\begin{tabular}{c|c}
-		Mean Squared Error       & 1202.70\\\hline
-		$r^2$ 	                 & 0.90\\\hline
-		True Positive            & 994\\\hline
-		False Positive           & 8\\\hline
-		True Negative            & 1015\\\hline
-		False Negative           & 101\\\hline
-		True Positive Rate       & 0.90\\\hline
-		True Negative Rate       & 0.99\\\hline
-		ClassificationAcuracy    & 0.95\\\hline
-		MatthewsCorrelationFactor& 0.90
+    \setlength{\tabcolsep}{12pt}
+    \renewcommand{\arraystretch}{1.3}
+    \begin{tabular}{|>{\columncolor{gray!20}}c||c|}
+        \hline
+        \rowcolor{gray!20}
+        \textbf{Metric} & \textbf{Value} \\
+        \hline\hline
+        Mean Squared Error        & 1202.70 \\
+        $r^2$                     & 0.90 \\
+        True Positive             & 994 \\
+        False Positive            & 8 \\
+        True Negative             & 1015 \\
+        False Negative            & 101 \\
+        True Positive Rate        & 0.90 \\
+        True Negative Rate        & 0.99 \\
+        Classification Accuracy   & 0.95 \\
+        Matthews Correlation Coefficient & 0.90 \\
+        \hline
     \end{tabular}
 \end{table}
+
 At this stage, it is important to note that the model is currently unable to distinguish between the active and inactive conformations of a molecule, i.e, between the \emph{cis} and \emph{trans} isomers.
@@
 \label{tableCelecoxibPyrazole}
-\begin{tabular}{c||c|c|c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|}
+        \hline
+        \rowcolor{gray!20}
 Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
@@
 \ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3}  & \ch{F}\\\hline
-\ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3}  & \ch{F}
+\ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3}  & \ch{F}\\\hline
 \end{tabular}
@@
 \label{tableCelecoxibFuran}
-\begin{tabular}{c||c|c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|}
+\hline
+\rowcolor{gray!20}
 Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
@@
 \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} \\\hline
-\ref{figureCelecoxibFuran}.12 & \ch{CH_3} & \ch{F}
+\ref{figureCelecoxibFuran}.12 & \ch{CH_3} & \ch{F}\\\hline
 \end{tabular}
@@
 \label{tableCelecoxibThiophene}
-\begin{tabular}{c||c|c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|}
+\hline
+\rowcolor{gray!20}
 Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
@@
 \ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} \\\hline
-\ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} 
+\ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} \\\hline
 \end{tabular}
@@
 \label{tableCelecoxibPyrrole}
-\begin{tabular}{c||c|c|c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|}
+\hline
+\rowcolor{gray!20}
 Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
 \ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} \\\hline
-\ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} 
+\ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} \\\hline
 \end{tabular}
@@
 \label{tableCelecoxibBenzene}
-\begin{tabular}{c||c|c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|}
+\hline
+\rowcolor{gray!20}
 Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
@@
 \ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} \\\hline
-\ref{figureCelecoxibBenzene}.5 & \ch{Cl} & \ch{CH_3} 
+\ref{figureCelecoxibBenzene}.5 & \ch{Cl} & \ch{CH_3} \\\hline
 \end{tabular}
@@
 \label{tableCelecoxibIndole}
-\begin{tabular}{c||c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|}
+\hline
+\rowcolor{gray!20}
 Identifier & \ch{R_1}  \\\hline\hline
 \ref{figureCelecoxibIndole}.1 & \ch{H} \\\hline
-\ref{figureCelecoxibIndole}.2 & \ch{F} 
+\ref{figureCelecoxibIndole}.2 & \ch{F} \\\hline
 \end{tabular}
@@
 \label{tableCelecoxibTwoRings}
-\begin{tabular}{c||c|c|c}
+\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|}
+\hline
+\rowcolor{gray!20}
 Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
@@
 \ref{figureCelecoxibTwoRings}.7 & \ch{O} & \ch{NH} & \ch{CH_3} \\\hline
-\ref{figureCelecoxibTwoRings}.8 & \ch{O} & \ch{O} & \ch{CH_3}
+\ref{figureCelecoxibTwoRings}.8 & \ch{O} & \ch{O} & \ch{CH_3}\\\hline
 \end{tabular}
@@
 
+\newpage
 \section{Tables of results}\label{appendixTableOfResults}
@@
 	\label{TableMainResults1}
-	\begin{tabular}{c|c|c|c|c|c|c}
+	\begin{tabular}{|>{\columncolor{gray!20}}c|c|c|c|c|c|c|}
+	\hline
+\rowcolor{gray!20}
 		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
@@
         Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
-        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241
+        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241\\ \hline
             \end{tabular}
@@
 	\label{TableMainResults2}
-	\begin{tabular}{c|c|c|c|c|c|c}
+	\begin{tabular}{|>{\columncolor{gray!20}}c|c|c|c|c|c|c|}
+	\hline
+\rowcolor{gray!20}		
 Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
@@
         TwoRings & \ref{figureCelecoxibTwoRings}.7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77\\ \hline
-        TwoRings & \ref{figureCelecoxibTwoRings}.8 & O & O & \ch{CH_3} & -3.5413 & 142
+        TwoRings & \ref{figureCelecoxibTwoRings}.8 & O & O & \ch{CH_3} & -3.5413 & 142 \\\hline
     \end{tabular}
@@
 	\label{TableConditionsMainResults}
-	\begin{tabular}{c|c}
+	\begin{tabular}{|>{\columncolor{gray!20}}c|c|}
+	\hline
+\rowcolor{gray!20}
+		\textbf{Metric}			& \textbf{Value} \\\hline\hline
 		NumberOfTrees            & 250\\\hline
@@
 		ClassificationAcuracy    & 0.95\\\hline
-		MatthewsCorrelationFactor& 0.90
+		MatthewsCorrelationFactor& 0.90\\\hline
     \end{tabular}

### 2025-06-03 Manuscript/Plantilla memòria TFG 2024_25.tex
Lassssst version

@@
 %----------FONT AND GEOMETRY DEFINITION----------%
-\usepackage[a4paper, top=3.0cm, bottom=3.0cm, left = 3.0cm, right = 3.0cm]{geometry}
+%\usepackage[a4paper, top=3.0cm, bottom=3.0cm, left = 3.0cm, right = 3.0cm]{geometry}
+\usepackage[a4paper, hmargin=3.0cm, vmargin=3cm]{geometry}
 \voffset = -0.75cm
@@
 \newcommand\NomGrau{Quimica}
-\newcommand\Mes{Juny } %cal espai al final
+\newcommand\Mes{Juny } % cal espai al final
 \newcommand\Any{2025}
@@
 \section*{Resum analític}\par
-L'intel·ligència artificial es presenta com una de les revolucions del segle XXI.
+\hspace{0.55cm}L'intel·ligència artificial es presenta com una de les revolucions del segle XXI.
 En particular, el sector de la química computacional està sent profundament sacsejat per aquesta revolució.
-Aprofitant la inèrcia i l'interès creixent en aquest camp, aquest treball pretén aplicar diferents models d'intel·ligència artificial en l'estudi d'una proteïna d'especial interès per a la nostra salut, la Ciclooxigenasa-2 (COX-2).
-
-La \emph{prostaglandin-endoperoxide sinthasa 2} (PTGS2), també coneguda com COX-2, és una proteïna que, en circumstàncies normals, acostuma a romandre inactiva \cite{Cox2Location}, llevat de la seva expressió durant processos inflamatoris.
+Aprofitant la inèrcia i l'interès creixent en aquest camp, aquest treball pretén aplicar diferents models d'intel·ligència artificial en l'estudi d'una proteïna d'especial interès per a la nostra salut, la Ciclooxigenasa-2 (\glstext{cox2}).
+
+La \emph{prostaglandina-endoperoxid sintasa 2} (\glstext{ptgs2}), també coneguda com \glstext{cox2}, és una proteïna que, en circumstàncies normals, acostuma a romandre inactiva \cite{Cox2Location}, llevat de la seva expressió durant processos inflamatoris.
 Així mateix, la manca de retorn a nivells baixos d'expressió després de la inflamació ha estat relacionada amb l'aparició de diferents formes de càncer \cite{DefinitionCOX2CancerDictionary}.
-Aquest fet ha convertit la COX-2 en objecte d'estudi de nombroses investigacions científiques \cite{Cox2InhibitorsReview}, fet que la fa un punt de partida idoni per al desenvolupament d'algoritmes de \emph{Machine Learning}, ja que disposa d'una gran quantitat de dades per entrenar els models i contrastar els resultats.
-
-L'objectiu principal del projecte és el desenvolupament d'un programari generador d'IAs capaces de predir la concentració d'inhibició al 50\% (IC$_{50}$) per a la COX-2\footnote{En realitat, el programari funciona per a qualsevol proteïna amb entrada a la base de dades de ChEMBL \cite{ChemblDatabase}, malgrat que l'objecte d'estudi és la COX-2.} amb la màxima precisió possible.
-Per fer-ho, s'extreuen totes les dades de molècules conegudes amb un potencial d'inhibició establert per a la COX-2.
+Aquest fet ha convertit la \glstext{cox2} en objecte d'estudi de nombroses investigacions científiques \cite{Cox2InhibitorsReview}, fet que la fa un punt de partida idoni per al desenvolupament d'algoritmes de Machine Learning (\glstext{ml}), ja que disposa d'una gran quantitat de dades per entrenar els models i contrastar els resultats.
+
+L'objectiu principal del projecte és el desenvolupament d'un programari generador d'IAs capaces de predir la concentració d'inhibició al 50\% (\glstext{ic50}) per a la \glstext{cox2}\footnote{En realitat, el programari funciona per a qualsevol proteïna amb entrada a la base de dades de ChEMBL \cite{ChemblDatabase}, malgrat que l'objecte d'estudi és la \glstext{cox2}.} amb la màxima precisió possible.
+Per fer-ho, s'extreuen totes les dades de molècules conegudes amb un potencial d'inhibició establert per a la \glstext{cox2}.
 Després d'un filtratge configurable per l'usuari, es calculen 5.900 descriptors químics per a cadascuna de les entrades amb el programari AlvaDesk \cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper}.
-Seguidament, una part de les dades s'utilitza per entrenar models de \emph{Random Forest} (RF) \cite{MachineLearningRandomForest}, mentre que la resta es reserva per validar la precisió de les prediccions.
+Seguidament, una part de les dades s'utilitza per entrenar models de Random Forest (\glstext{rf}) \cite{MachineLearningRandomForest}, mentre que la resta es reserva per validar la precisió de les prediccions.
 
@@
 
-Finalment, els models es fan servir per predir l'IC$_{50}$ de 50 \emph{azophotoswitches} dels quals es tenen dades sobre l'energia lliure d'acoblament proporcionades pel Departament de Química Física de la UAB \cite{UAB_ComputationalChemistry}.
+Finalment, els models es fan servir per predir l'\glstext{ic50} de 50 \emph{azophotoswitches} dels quals es tenen dades sobre l'energia de Gibbs d'acoblament proporcionades pel grup de recerca MolBioMed \cite{molbiomed}.
 L'anàlisi estadístic de les prediccions reflecteix una clara correlació entre ambdues quantitats, fet que reforça la hipòtesi del projecte.
@@
 \section*{Resumen analítico}
-La inteligencia artificial se presenta como una de las revoluciones del siglo XXI.
+\hspace{0.55cm}La inteligencia artificial se presenta como una de las revoluciones del siglo XXI.
 En particular, el sector de la química computacional está siendo profundamente sacudido por esta revolución.
-Aprovechando la inercia y el interés creciente en este campo, este trabajo pretende aplicar diferentes modelos de inteligencia artificial en el estudio de una proteína de especial interés para nuestra salud, la Ciclooxigenasa-2 (COX-2).
-
-La \emph{prostaglandin-endoperoxide sinthasa 2} (PTGS2), también conocida como COX-2, es una proteína que, en circunstancias normales, suele permanecer inactiva \cite{Cox2Location}, excepto por su expresión durante procesos inflamatorios.
+Aprovechando la inercia y el interés creciente en este campo, este trabajo pretende aplicar diferentes modelos de inteligencia artificial en el estudio de una proteína de especial interés para nuestra salud, la Ciclooxigenasa-2 (\glstext{cox2}).
+
+La prostaglandina-endoperóxido sintasa 2 (\glstext{ptgs2}), también conocida como \glstext{cox2}, es una proteína que, en circunstancias normales, suele permanecer inactiva \cite{Cox2Location}, excepto por su expresión durante procesos inflamatorios.
 Asimismo, la falta de retorno a niveles bajos de expresión después de la inflamación ha sido relacionada con la aparición de diferentes formas de cáncer \cite{DefinitionCOX2CancerDictionary}.
-Este hecho ha convertido a la COX-2 en objeto de estudio de numerosas investigaciones científicas \cite{Cox2InhibitorsReview}, lo que la convierte en un punto de partida idóneo para el desarrollo de algoritmos de \emph{Machine Learning}, ya que dispone de una gran cantidad de datos para entrenar los modelos y contrastar los resultados.
-
-El objetivo principal del proyecto es el desarrollo de un software generador de IAs capaces de predecir la concentración de inhibición al 50\% (IC$_{50}$) para la COX-2\footnote{En realidad, el software funciona para cualquier proteína con entrada en la base de datos de ChEMBL \cite{ChemblDatabase}, aunque el objeto de estudio es la COX-2.} con la máxima precisión posible.
-Para ello, se extraen todos los datos de moléculas conocidas con un potencial de inhibición establecido para la COX-2.
+Este hecho ha convertido a la \glstext{cox2} en objeto de estudio de numerosas investigaciones científicas \cite{Cox2InhibitorsReview}, lo que la convierte en un punto de partida idóneo para el desarrollo de algoritmos de Machine Learning (\glstext{ml}), ya que dispone de una gran cantidad de datos para entrenar los modelos y contrastar los resultados.
+
+El objetivo principal del proyecto es el desarrollo de un software generador de IAs capaces de predecir la concentración de inhibición al 50\% (\glstext{ic50}) para la \glstext{cox2}\footnote{En realidad, el software funciona para cualquier proteína con entrada en la base de datos de ChEMBL \cite{ChemblDatabase}, aunque el objeto de estudio es la \glstext{cox2}.} con la máxima precisión posible.
+Para ello, se extraen todos los datos de moléculas conocidas con un potencial de inhibición establecido para la \glstext{cox2}.
 Tras un filtrado configurable por el usuario, se calculan 5.900 descriptores químicos para cada una de las entradas con el software AlvaDesk \cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper}.
-Seguidamente, una parte de los datos se utiliza para entrenar modelos de \emph{Random Forest} (RF) \cite{MachineLearningRandomForest}, mientras que el resto se reserva para validar la precisión de las predicciones.
+Seguidamente, una parte de los datos se utiliza para entrenar modelos de Random Forest (\glstext{rf})\cite{MachineLearningRandomForest}, mientras que el resto se reserva para validar la precisión de las predicciones.
 
@@
 
-Finalmente, los modelos se utilizan para predecir el IC$_{50}$ de 50 \emph{azophotoswitches}, de los cuales se tienen datos sobre la energía libre de acoplamiento proporcionados por el Departamento de Química Física de la UAB \cite{UAB_ComputationalChemistry}.
+Finalmente, los modelos se utilizan para predecir el \glstext{ic50} de 50 \emph{azophotoswitches}, de los cuales se tienen datos sobre la energía libre de acoplamiento proporcionados por el grupo de investigación MolBioMed \cite{molbiomed}.
 El análisis estadístico de las predicciones refleja una clara correlación entre ambas cantidades, lo que refuerza la hipótesis del proyecto.
@@
 \section*{Analytical abstract}
-Artificial intelligence is emerging as one of the revolutions of the 21st century.
+\hspace{0.55cm}Artificial intelligence is emerging as one of the revolutions of the 21st century.
 In particular, the field of computational chemistry is being profoundly shaken by this revolution.
-Taking advantage of the momentum and growing interest in this field, this work aims to apply different artificial intelligence models to the study of a protein of special interest to our health, Cyclooxygenase-2 (COX-2).
-
-The \emph{prostaglandin-endoperoxide synthase 2} (PTGS2), also known as COX-2, is a protein that, under normal circumstances, tends to remain inactive \cite{Cox2Location}, except for its expression during inflammatory processes.
+Taking advantage of the momentum and growing interest in this field, this work aims to apply different artificial intelligence models to the study of a protein of special interest to our health, Cyclooxygenase-2 (\glstext{cox2}).
+
+The prostaglandin-endoperoxide synthase 2 (\glstext{ptgs2}), also known as \glstext{cox2}, is a protein that, under normal circumstances, tends to remain inactive \cite{Cox2Location}, except for its expression during inflammatory processes.
 Likewise, the failure to return to low expression levels after inflammation has been linked to the onset of various forms of cancer \cite{DefinitionCOX2CancerDictionary}.
-This fact has made COX-2 the subject of numerous scientific investigations \cite{Cox2InhibitorsReview}, making it an ideal starting point for the development of \emph{Machine Learning} algorithms, as it provides a large amount of data for training models and validating results.
-
-The main objective of the project is to develop software capable of generating AIs that can predict the 50\% inhibition concentration (IC$_{50}$) for COX-2\footnote{Actually, the software works for any protein with an entry in the ChEMBL database \cite{ChemblDatabase}, although the study focuses on COX-2.} with the highest possible accuracy.
-To achieve this, all known molecular data with an established inhibition potential for COX-2 are extracted.
+This fact has made \glstext{cox2} the subject of numerous scientific investigations \cite{Cox2InhibitorsReview}, making it an ideal starting point for the development of Machine Learning (\glstext{ml}) algorithms, as it provides a large amount of data for training models and validating results.
+
+The main objective of the project is to develop software capable of generating AIs that can predict the 50\% inhibition concentration (\glstext{ic50}) for \glstext{cox2}\footnote{Actually, the software works for any protein with an entry in the ChEMBL database \cite{ChemblDatabase}, although the study focuses on \glstext{cox2}.} with the highest possible accuracy.
+To achieve this, all known molecular data with an established inhibition potential for \glstext{cox2} are extracted.
 After a user-configurable filtering process, 5,900 chemical descriptors are calculated for each entry using the AlvaDesk software \cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper}.
-Subsequently, part of the data is used to train \emph{Random Forest} (RF) models \cite{MachineLearningRandomForest}, while the rest is reserved to validate the accuracy of the predictions.
+Subsequently, part of the data is used to train Random Forest (\glstext{rf}) models \cite{MachineLearningRandomForest}, while the rest is reserved to validate the accuracy of the predictions.
 
@@
 
-Finally, the models are used to predict the IC$_{50}$ of 50 \emph{azophotoswitches}, for which data on the free binding energy have been provided by the Physical Chemistry Unit at UAB \cite{UAB_ComputationalChemistry}.
+Finally, the models are used to predict the \glstext{ic50} of 50 \emph{azophotoswitches}, for which data on the free binding energy have been provided by the MolBioMed research group \cite{molbiomed}.
 The statistical analysis of the predictions shows a clear correlation between both quantities, which supports the project's hypothesis.
@@
 \section{Introduction}\label{sectionIntroduction}
-The impact of \gls{ai} on science has been nothing short of a groundbreaking revolution, with few comparable precedents.
+\hspace{0.55cm}The impact of \gls{ai} on science has been nothing short of a groundbreaking revolution, with few comparable precedents.
 The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry.
@@
 \scalebox{0.7}{
-\chemname{\chemfig[angle increment=30, scale=0.1]{
+\chemname{\chemfig[angle increment=30, scale=0.1, bond style={line width=1pt}]{
 HO-[1](=[3]O)-[-1]-[1]-[-1]-[1]=[-1]-[-3]-[-1]=[-3]-[7]-[-3]=[7]-[-7]-[7]=[-7]-[3]-[-7]-[7]-[-7]-[7]
@@
 \scalebox{0.7}{
-\chemname{\chemfig[angle increment=30]{OH-[5](=[3]O)-[7]-[-3]-[7]-[-3]=[7]-[5]>:[7]*6(-(<[-3.8])-O-O-(<[3.8]C)-(<[-1]=[1]-[-1](<:[-3]OH)-[1]-[-1]-[1]-[-1]-[1])-)
+\chemname{\chemfig[angle increment=30, bond style={line width=1pt}]{OH-[5](=[3]O)-[7]-[-3]-[7]-[-3]=[7]-[5]>:[7]*6(-(<[-3.8])-O-O-(<[3.8]C)-(<[-1]=[1]-[-1](<:[-3]OH)-[1]-[-1]-[1]-[-1]-[1])-)
 }}{Prostaglandin \chemfig{H_2}}
@@
 \schemestop
-\caption{Reaction catalysed by the COX-2 between arachidonic acid to prostaglandin H$_2$.}
+\caption{Reaction catalysed by the \gls{cox2} from arachidonic acid to prostaglandin H$_2$.}
 \label{Cox2MainReaction}
@@
 We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset.
-The chemical descriptors (Definition (\ref{definitionChemicalDescriptors})) \footnote{All the definitions are stored in the Appendix (\ref{appendixRellevantDefinitions}) \emph{Relevant definitions}.
+The chemical descriptors (Definition (\ref{definitionChemicalDescriptors})) \footnote{All the definitions are stored in the Appendix (\ref{appendixRelevantDefinitions}) \emph{Relevant definitions}.
 We recommend its consultance for further information.}  of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software.
@@
 
-The \gls{ai} algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}\cite{UAB_ComputationalChemistry}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy.
+The \gls{ai} algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}, a powerful ensemble learning method that generates multiple decision trees (Definition \ref{definitionDecisionTree}) and combines their outputs to improve prediction accuracy.
 This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting.
@@
 \scalebox{0.8}{
-	\chemfig[angle increment=30]{*6(-=-(-[1]N=[-1]N-*6(-=-=-=))=-=)}}
+	\chemfig[angle increment=30, bond style={line width=1pt}]{*6(-=-(-[1]N=[-1]N-*6(-=-=-=))=-=)}}
 	\arrow{<=>[$h\nu$]}
 \scalebox{0.8}{
-	\chemfig[angle increment=30]{
+	\chemfig[angle increment=30, bond style={line width=1pt}]{
 	N(-[-4]*6(-=-=-=))=[0]N-[-2]*6(-=-=-=)
@@
 In the context of an azophotoswitch, one isomer may fit precisely into the binding pocket, leading to strong interactions, while the other may not.
-Accordingly, we refer to the isomer that interacts most effectively with the protein as the active configuration, and the other as the inactive configuration.\footnote{In the context of this project, interaction refers to inhibition of the protein’s activity.} \footnote{Generally, the trans-isomer is considered the active configuration, while the cis-isomer is considered inactive.
+Accordingly, we refer to the isomer that interacts most effectively with the protein as the active configuration, and the other as the inactive configuration.\footnote{In the context of this project, interaction refers to inhibition of the protein’s activity.} \footnote{Generally, the cis-isomer is considered the active configuration, while the trans-isomer is considered inactive.
 However, exceptions exist.}
@@
 
-Among the most promising drug candidates for \gls{cox2} inhibition are Celecoxib (Definition \ref{definitionCelecoxib}) and Rofecoxib (Definition \ref{definitionRofecoxib}).\footnote{These compounds are often referred to as coxib drugs due to the common suffix -coxib.} At the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}, researchers are investigating azophotoswitches as potential COX-2 inhibitors, using molecular structures inspired by Celecoxib.
+Among the most promising drug candidates for \gls{cox2} inhibition are Celecoxib (Definition \ref{definitionCelecoxib}) depicted in Scheme (\ref{CelecoxibFigure}) and Rofecoxib (Definition \ref{definitionRofecoxib}).\footnote{Naturally, these compounds are often referred to as \emph{coxib drugs} due to the \gls{cox2}.} At the MolBioMed research group \cite{molbiomed}, researchers are investigating azophotoswitches as potential \gls{cox2} inhibitors, using molecular structures inspired by Celecoxib.
 Various computational analyses have been conducted, with particular attention to the binding free energy ($\Delta G_{\text{binding}}$).\footnote{Additional results are provided in Appendix \ref{appendixTableOfResults}.}
+
+\begin{figure}[H]
+\captionsetup{type=scheme}
+\centering
+\scalebox{0.8}{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
+H_2N-[1]S(=[4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
+}}
+\caption{Chemical graph of Celecoxib.}
+\label{CelecoxibFigure}
+\end{figure}
 
@@
 
-This project aims to develop a fully functional software tool capable of accurately predicting a molecule’s inhibition potential (\gls{ic50}), leveraging existing data from the ChEMBL database \cite{ChemblDatabase}.
+\hspace{0.55cm}This project aims to develop a fully functional software tool capable of accurately predicting a molecule’s inhibition potential (\gls{ic50}), leveraging existing data from the ChEMBL database \cite{ChemblDatabase}.
 The software is thoroughly documented and available in the GitHub repository: \href{https://github.com/SirSergi0/Repository—AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI Application for Azophotoswitches Optimization with Pharmacological Interest}} \cite{GitHub}\cite{azophotoswitches2025}.
@@
 The prediction process is powered by an \gls{ai} tool designed to deliver high-quality results, taking into account relevant molecular descriptors.
-The software also serves to cross-check computational results previously obtained by the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}.
-The application centers on azophotoswitches, molecules of particular pharmacological interest as discussed in Section \ref{sectionIntroduction}.
+The software also serves to cross-check computational results previously obtained by the MolBioMed research group \cite{molbiomed}.
+The application centres on azophotoswitches, molecules of particular pharmacological interest as discussed in Section \ref{sectionIntroduction}.
 Additionally, a molecular docking study is performed on one of the most promising azophotoswitch candidates.
@@
 \section{Methodology}\label{sectionMethodology}
-The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project\cite{azophotoswitches2025}.
+\hspace{0.55cm}The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project\cite{azophotoswitches2025}.
 The consultace of this repository is highly recommended in order to comprehended the insights and the workflow of the project.
@@
 
-The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database\cite{ChemblDatabase}.
-Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Definition \ref{definitionIC50}) with a limit of 1000 entries per request.
+The target protein's ID is set at \emph{CHEMBL230} corresponding to the \gls{cox2} ID in the ChEMBL database\cite{ChemblDatabase}.
+Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know \gls{ic50} value (Definition \ref{definitionIC50}) with a limit of 1000 entries per request.
 The process is iterated until all data is extracted leading a total of 7979 molecules.
-Hence the datasheet is processed in pandas dataframes\cite{PythonPackagePandas} and encrypted into binary feather files to optimise reading-writting speed.
+Hence the data-sheet is processed in pandas dataframes \cite{PythonPackagePandas} (Definition \ref{definitionPandasDataFrames}) and encrypted into binary feather files to optimise reading-writing speed.
 By removing entries with the same canonical \gls{smiles} (Definition \ref{definitionSMILES})  a total of 5112 molecules remain.
-Among this entries well known drugs such as Celecoxib (Definition \ref{definitionCelecoxib}), Rofecoxib (Definition \ref{definitionRofecoxib}) or even Ibuprofen can be found.
-However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure.
+Among these entries well known drugs such as Celecoxib (Definition \ref{definitionCelecoxib}), Rofecoxib (Definition \ref{definitionRofecoxib}) or even Ibuprofen can be found.
+However the \gls{ic50} molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure.
 Since we are interested in testing azophotoswitches with presumably low \gls{ic50}, training \gls{ml} models with data of the order of $10^{8}$ or $10^{3}$ nM can be counterproductive since the model might misinterpret the data.\footnote{Typically the range of the azophotoswitches \gls{ic50} is arround the Celecoxib's \gls{ic50}, i.e.
 arround $120$ nM}.
-Consecutivelly, a hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,300]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries, i.e.
+Consecutivelly, a hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this \gls{ic50} working range is the standard in these kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries, i.e.
 molecules.
 
-With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule.
-Still, some chemical descriptor need from the presence of a certain atom, for instance a chemical descriptor related to the presence of a metal in the molecule, or active gorup, for example chemical descriptor related to the presence of a carboxilic acid, or chemical descriptor related triple bound among other possiblities.
-The computation of this chemical descriptors appear as \emph{null values}.
-By deleting molecular descriptors with null values 2917 chemical descriptors remain.
-Here, the Pearson correlation coefficient (Definition \ref{definitionPersonCoefficient}) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.
+With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule, although only 2917 chemical descriptors yield to no \emph{null values}.
+This is because some chemical descriptors need from the presence of a certain atom or active group, for example chemical descriptor related to the presence of a carboxylic acid, or chemical descriptor related triple bound among other possibilities.
+The computations of these chemical descriptors appear as \emph{null values}.
+Here, the Pearson correlation coefficient (Definition \ref{definitionPersonCoefficient}) between each chemical descriptor and the \gls{ic50} value is computed, providing insight into the direct relationship between \gls{ic50} and the descriptors.
 This relationship will be discussed in the Results and Discussion Section (\ref{sectionResultsAndDiscussion}).
 
-At this stage, the average $IC_{50}$ is calculated, and the neighborhood size corresponding to the percentage defined by the hard-coded variable \emph{percentageErased} is removed.
-This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}, those with lower and higher $IC_{50}$ values, respectively.
+At this stage, the average \gls{ic50} is calculated, and the neighbourhood size corresponding to the percentage defined by the hard-coded variable \emph{percentageErased} is removed.
+This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}, those with lower and higher \gls{ic50} values, respectively.
 By doing so, it is possible to compute the classification accuracy statistics of the model from the cluster association of each prediction.
-Thus we can compare each prediction of each molecules with experimental data.
-For instance, for an experimentally proved highly active molecule if the model predicts this molecule to be highly active (has a low \gls{ic50} precition) we consider this as \gls{tp}.
+Thus we can compare each prediction of each molecule with experimental data.
+For instance, for an experimentally proved highly active molecule if the model predicts this molecule to be highly active (has a low \gls{ic50} prediction) we consider this prediction as \gls{tp}.
 Similarly we define a \gls{tn}, \gls{fp} and \gls{fn} .
-This procedure is an standard for evaluating a \gls{ml} model realiability.
-
-Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} for training the \gls{rf} algorithm and a \emph{testing set} for testing the statistics and realiability of the \gls{rf} model, following the proportion specified by the hard-coded variable \emph{testSizeProportion}.
+This procedure is an standard for evaluating a \gls{ml} model reliability.
+
+Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} for training the \gls{rf} algorithm and a \emph{testing set} for testing the statistics and reliability of the \gls{rf} model, following the proportion specified by the hard-coded variable \emph{testSizeProportion}.
 This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
@@
 Afterwards, a Random Forest (\gls{rf}) algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others.
-Although the project’s primary focus is not the detailed workings of Machine Learning (\gls{ml}) algorithms but its applications in computational chemestry, it is natural to ponder the essence of what the machine is doing.
+Although the project’s primary focus is not the detailed workings of Machine Learning (\gls{ml}) algorithms but its applications in computational chemistry, it is natural to ponder the essence of what the machine is doing.
 The name “Random Forest” is directly tied to the analogy between a tree and a decision tree.
@@
 The structure of each tree adjusts during training to make predictions that closely approximate the true target values.
-The final output of the Random Forest is typically an aggregate of the predictions from all the individual trees, such as a majority vote for classification tasks or an average for regression tasks.
-\par
+The final output of the Random Forest is typically an aggregate of the predictions from all the individual trees.\par
 
@@
 \end{align*}
+
 However, increasing either component in isolation, i.e.
@@
 
-Subsequently, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.
-Using the predictions, we compute the \emph{True Positive Rate} (Definition \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Definition \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Definition \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Definition \ref{definitionMatthewsCorrelationCoeficient}).
+Subsequently, these models are evaluated by predicting the \gls{ic50} values of the \emph{testing sets}.
+Using the predictions, we compute the \emph{True Positive Rate}\footnote{Which is related to how well performs a \gls{ml} model when predicting a molecule to be highly active.
+} (Definition \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Definition \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Definition \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Definition \ref{definitionMatthewsCorrelationCoeficient}).
 Based on these metrics, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to optimize model performance.
 
-Finally, the \gls{rf} model with the best performance\footnote{The criteria for determining the model with “better statistics” is discussed in Section \ref{sectionPersonCorrelationFactor} since this term references \gls{ai} statistics rather than the usual statistics.} is used to predict the \gls{ic50} values of the azophotoswitch prototypes listed in Appendix \ref{appendixAzophotoshiches}.
+Finally, the \gls{rf} model with the best performance\footnote{The criteria for determining the model with “better statistics” is discussed in the Results section (Section \ref{sectionPersonCorrelationFactor}) since this term references \gls{ai} statistics rather than the usual statistics.} is used to predict the \gls{ic50} values of the azophotoswitch prototypes listed in Appendix \ref{appendixAzophotoshiches}.
 This process begins with computing the chemical descriptors using AlvaDesc software \cite{MauriMolecularDescriptorsBook}.
@@
 
-Finally, a docking study was performed using GOLD2022 \cite{GoldReference}.
-This software employs a genetic algorithm, along with molecular modeling techniques, to predict the optimal binding pose of the ligand within the \gls{cox2} binding site.
+Finally, a docking study was performed using GOLD2022 \cite{GoldReference} by the MolBioMed research group (\cite{molbiomed}).
+This software employs a genetic algorithm, along with molecular modelling techniques, to predict the optimal binding pose of the ligand within the \gls{cox2} binding site.
 The genetic nature of the algorithm allows for a broad exploration of the conformational and positional space between the ligand and the protein.
-By evaluating and ranking ligand interactions, such as hydrogen bonding, van der Waals forces, and metal coordination, unstable or energetically unfavorable conformations are discarded, resulting in a set of plausible, energetically stable binding orientations.
-The docking calculations were carried out within a 26 Å radius sphere centered at Arg513.
+By evaluating and ranking ligand interactions, such as hydrogen bonding, van der Waals forces, and metal coordination, unstable or energetically unfavourable conformations are discarded, resulting in a set of plausible, energetically stable binding orientations.
+The docking calculations were carried out within a 26 Å radius sphere centred at Arg513, comprehending the totality of the binding site.
 
@@
 \subsection{Available Data}\label{sectionAvailableData}
-Figure (\ref{figureGraphicRecurrecyIC50}) presents the \gls{ic50} values extracted from the ChEMBL database under target ID \emph{CHEMBL230}, limited to the interval $[0, 200]$ nM.
-The figure clearly shows that multiples of 10 are significantly overrepresented compared to other values.
+\hspace{0.55cm}Figure (\ref{figureGraphicRecurrecyIC50}) presents the \gls{ic50} values extracted from the ChEMBL database under target ID \emph{CHEMBL230}, limited to the interval $[0, 200]$ nM.
+Figure (\ref{figureGraphicRecurrecyIC50}) clearly shows that multiples of 10 are significantly overrepresented compared to other values.
 Upon analyzing data from additional proteins, we can confirm this is not an exception but rather the norm.
@@
 Given a dataset, the average \gls{ic50} is first computed, approximately 47 nM in this case.
-A proportion of the data, defined by the hard-coded variable \emph{percentageErased}, is then removed to create a gap centered around the average value.
-In Figure (\ref{figureGraphicRecurrecyIC50}), the full dataset is represented in blue and orange, while the blue region, centered at 47 nM, has been deleted to introduce the gap.
+A proportion of the data, defined by the hard-coded variable \emph{percentageErased}, is then removed to create a gap centred around the average value.
+In Figure (\ref{figureGraphicRecurrecyIC50}), the full dataset is represented in blue and orange, while the blue region, centred at 47 nM, has been deleted to introduce the gap.
 In this specific example, the gap accounts for 20\% of the total data.
@@
 
-Afterwards, chemical descriptors are calculated using the AlvaDesc software.
+\hspace{0.55cm}Afterwards, chemical descriptors are calculated using the AlvaDesc software.
 Subsequently, we compute the Pearson Correlation Coefficients\footnote{The Pearson Correlation Coefficient is sometimes denoted as $r^2$, though strictly speaking $r^2$ refers to the coefficient of determination, which is the square of the correlation coefficient.} as defined in Definition (\ref{definitionPersonCoefficient}), measuring the linear relationship between each descriptor and the corresponding \gls{ic50} value for every molecule.
@@
 
-The distribution of correlation values resembles a Gaussian bell curve centered around zero, as expected.
+The distribution of correlation values resembles a Gaussian bell curve centred around zero, as expected.
 This suggests that there is no dominant or inherently preferred chemical descriptor strongly associated with \gls{ic50} variation for this protein.
@@
 Nonetheless, our central hypothesis remains valid: "\emph{there exists at least one combination of chemical descriptors that correlates directly with the inhibition of the target protein}".
-The observed distribution of correlation values does not contradict this hypothesis, rather, it highlights the need for models that can identify and exploit subtle multivariate relationships.
+The observed distribution of correlation values does not contradict this hypothesis, rather, it highlights the need for models that can identify and exploit subtle multivariable relationships.
 
@@
 
-Once the models have been generated, i.e., once the relevant hyperparameters are set, we proceed with generating predictions.
-At this stage, we compute the Pearson Correlation Coefficient (Definition (\ref{definitionPersonCoefficient})) and the Mean Squared Error (Definition (\ref{definitionMeanSquaredError})) between the predicted and experimental \gls{ic50} values.
+Once the models have been generated, i.e., once the relevant parameters are set, we proceed with generating predictions.
+At this stage, we compute the Pearson Correlation Coefficient (Definition \ref{definitionPersonCoefficient}) and the Mean Squared Error (Definition \ref{definitionMeanSquaredError}) between the predicted and experimental \gls{ic50} values.
 
@@
 
-From the discussion in Section \ref{sectionAvailableData}, we understand the dataset suffers from inherent precision issues, particularly at higher $IC_{50}$ values.
+From the discussion in Section \ref{sectionAvailableData}, we understand the dataset suffers from inherent precision issues, particularly at higher \gls{ic50} values.
 Additionally, the precision of several measurements remains unknown.
@@
 As such, discarding more than 50\% of the dataset, regardless of what statistical metrics may suggest, would be a critical error, as it would lead to substantial information loss.
+Hence, we consider this statistics as not representative of the hole model's accuracy.
 Still, the computed values of $r^2$ and mean squared error remain useful indicators of the model's performance up to a certain threshold.
@@
 \caption{Plots of $\%_{\text{Erased}}$ vs $r^2$ and $\%_{\text{Erased}}$ vs Mean Squared Error.
-For a maximum $IC_{50}$ = 200 nM and a minimum of 0 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
+For a maximum \gls{ic50} = 200 nM and a minimum of 0 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training.
 The training is done with 200 trees.}
@@
 More reliable indicators of model's performance are provided by the \emph{True Positive Rate} (Definition \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Definition \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Definition \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Definition \ref{definitionMatthewsCorrelationCoeficient}), the standard metrics used to evaluate the performance of a \gls{ml} model.
-Generally speaking, we define a method A to have "better statisitcs" than other method B if the computed quantities: \emph{True Positive Rate}, \emph{True Negative Rate}, \emph{Classification Accuracy}, and \emph{Matthews Correlation Coefficient}, for A take higher values than the same quantities for B.\footnote{Since all quantities are highly bounded by 1 we might also affirm, the closer to 1 the statistics values are the more reliable the method is.} Specifically, if this procedure for the method A and B lead to incoherences, i.e.
+Generally speaking, we define a method A to have "better statistics" than other method B if the computed quantities: \emph{True Positive Rate}, \emph{True Negative Rate}, \emph{Classification Accuracy}, and \emph{Matthews Correlation Coefficient}, for A take higher values than the same quantities for B.\footnote{Since all quantities are highly bounded by 1 we might also affirm, the closer to 1 the statistics values are the more reliable the method is.} Specifically, if this procedure for the method A and B lead to incoherences, i.e.
 some statistics of A are better than B while other are worst, we take the Matthews Correlation Factor as the most reliable statistical outcome.\footnote{This is the usual procedure in the analysis of \gls{ml} predictions\cite{MachineLearningPaper5Lipoxygenase}.}
@@
 
-Figure \ref{figureGraphicGbindingIC50} shows the predicted \gls{ic50} values of azophotoswitch compounds as a function of their binding free energy ($\Delta G_{binding}$), as provided by the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}.
-Detailed prediction results can be found in Appendix \ref{appendixTableOfResults}, specifically in Tables \ref{TableMainResults1} and \ref{TableMainResults2}.
-The training conditions for the Random Forest (\gls{rf}) model, along with a comprehensive statistical analysis of its predictions, are presented in Table~\ref{TableConditionsMainResults}.
+\hspace{0.55cm}Figure (\ref{figureGraphicGbindingIC50}) shows the predicted \gls{ic50} values of azophotoswitch compounds as a function of their binding free energy ($\Delta G_{binding}$), as provided by the MolBioMed research group \cite{molbiomed}.
+Detailed prediction results can be found in Appendix (\ref{appendixTableOfResults}), specifically in Tables (\ref{TableMainResults1}) and \ref{TableMainResults2}.
+The training conditions for the Random Forest (\gls{rf}) model, along with a comprehensive statistical analysis of its predictions, are presented in Table~(\ref{TableConditionsMainResults}).
 
@@
 
-\subsection{Azophotoswitches Analysis}
-
-Following the prediction phase, molecular docking is performed on one of the most promising azophotoswitch candidates.
+\subsection{Docking}
+
+\hspace{0.55cm}Following the prediction phase, molecular docking is performed by the MolBioMed research group \cite{molbiomed} on one of the most promising azophotoswitch candidates.
 Specifically, we select the molecule labeled as "\emph{\ref{figureCelecoxibTwoRings}.7}" in appendix \ref{appendixAzophotoshiches} \emph{Tables of azophotoswitches}, which is depicted in Scheme(\ref{figureCelecoxibTwoRingsDoking}).
-This molecule exhibited a predicted $\Delta G_{binding}$ of $-10.6712$ kcal/mol and a \gls{ic50} prediction of 77 nM.
+This molecule exhibited a predicted $\Delta G_{binding}$ of $-10.6712$ kcal/mol and a \gls{ic50} prediction of 77 nM, i.e.
+yielding to a lower \gls{ic50} prediction than the experimental Celecoxib's \gls{ic50} (120 nM).
 An image of the final frame from the docking simulation is shown in Figure (\ref{figureDockingBestResult}).
@@
 \scalebox{0.7}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30,bond style={line width=1pt}]{
 	H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-O-*5(-N(-[-3]H)-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
@@
 	\includegraphics[width = \textwidth, trim={0cm 0cm 0cm 0cm}, clip]{GeneralSources/LastFrameDockingTwoRingsFiveMembers.jpg}
-	\caption{Structural ilustration of the molecule identied as \ref{figureCelecoxibTwoRings}.7 and \gls{cox2} docking generated by the ChimeraX software[15].}
+	\caption{Structural ilustration of the molecule identified as \ref{figureCelecoxibTwoRings}.7 and \gls{cox2} docking generated by the ChimeraX software[15].}
 	\label{figureDockingBestResult}
 \end{figure}
-We observe the azophotoswitch in the \emph{cis} configuration happens to fit well within the \gls{cox2} binding cavity.
-Although the \emph{trans} isomer can, in theory, occupy the binding site,\footnote{With minor steric hindrances.} it is unlikely to access it in practice due to stereochemical constraints.
-Specifically, the extended structure of the \emph{trans} configuration results in steric clashes with the outer regions of \gls{cox2}, preventing entry into the binding pocket.
+We observe that the azophotoswitch in the cis- configuration fits well within the \gls{cox2} binding cavity, adopting a conformation similar to that of its counterpart, the Celecoxib (Definition \ref{definitionCelecoxib}).
+Although the trans- isomer can also occupy the binding site with minor steric hindrance, thanks to the large size of the \gls{cox2} cavity, which can accommodate various molecules, it is unlikely to access the site in practice due to stereochemical constraints.
+In particular, the critical differences between the cis- and trans- configurations manifest during the entry into the protein cavity, rather than within the cavity itself.
+Specifically, the extended structure of the trans- isomer causes steric clashes with the outer regions of \gls{cox2}, thereby preventing it from entering the binding pocket.
 
@@
 
-In this work, we have demonstrated the potential of Artificial Intelligence in the fields of theoretical and computational chemistry.
+\hspace{0.55cm}In this work, we have demonstrated the potential of Artificial Intelligence in the fields of theoretical and computational chemistry.
 We developed a fully functional machine learning software capable of predicting \gls{ic50} values for any protein listed in the ChEMBL database.
@@
 \section{Acknowledgements}
-I am grateful to Dr.
+\hspace{0.55cm}I am grateful to Dr.
 Josep Maria Lluch, Dr.
@@
 \addcontentsline{toc}{section}{Appendices}
-\section{Rellevant definitions}\label{appendixRellevantDefinitions}
+\section{Relevant definitions}\label{appendixRelevantDefinitions}
 \begin{definition}\label{definitionIC50}
-$IC_{50}$: Half maximal inhibitory concentration assigned to the drug concentration required for a $50\%$ inhibition a protein.
+\gls{ic50}: Half maximal inhibitory concentration assigned to the drug concentration required for a $50\%$ inhibition a protein.
 Other quantities such as $IC_{90}$ or $IC_{99}$ are also commonly used.
-However, $IC_{90}$ is generally approximated as 10 times the $IC_{50}$ concentration in virtue of experimental observations\cite{BookIC50}.
-For this project, we aim to identify substances with the lowest possible $IC_{50}$, as our goal is to minimize the presence of foreign substances in the living organism.
+However, $IC_{90}$ is generally approximated as 10 times the \gls{ic50} concentration in virtue of experimental observations\cite{BookIC50}.
+For this project, we aim to identify substances with the lowest possible \gls{ic50}, as our goal is to minimize the presence of foreign substances in the living organism.
 \end{definition}
@@
 \begin{definition}\label{definitionCelecoxib}
-Celecoxib: \footnote{UPAC name: 4-[5-(4-Methylphenyl)-3-(trifluoromethyl)pyrazol-1-yl]benzenesulfonamide} drug known to be a selective COX-2 inhibitor (currently is not \emph{highly selective} respect to newer drugs), see Scheme (\ref{CelecoxibFigure}).
-It $IC_{50}$ value is $120$ nM.
+Celecoxib: \footnote{UPAC name: 4-[5-(4-Methylphenyl)-3-(trifluoromethyl)pyrazol-1-yl]benzenesulfonamide} drug known to be a selective \gls{cox2} inhibitor, see Scheme (\ref{CelecoxibFigure}).
+Its \gls{ic50} value is $120$ nM.
 \end{definition}
@@
 \begin{definition}\label{definitionRofecoxib}
-Rofecoxib: \footnote{UPAC name: 4-(4-methylsulfonylphenyl)-3-phenyl-5H-furan-2-one} drug known to be a selective COX-2 inhibitor, see Scheme (\ref{RofecoxibFigure}). It $IC_{50}$ value is $180$ nM.
+Rofecoxib: \footnote{UPAC name: 4-(4-methylsulfonylphenyl)-3-phenyl-5H-furan-2-one} drug known to be a selective \gls{cox2} inhibitor, see Scheme (\ref{RofecoxibFigure}).
+Its \gls{ic50} value is $180$ nM.
 \end{definition}
 
+%\begin{figure}[H]
+%\captionsetup{type=scheme}
+%\centering
+%\scalebox{0.8}{
+%\chemfig[angle increment=30, bond style={line width=1pt}]{
+%H_2N-[1]S(=[4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
+%}}
+%\caption{Chemical graph of Celecoxib.}
+%\label{CelecoxibFigure}
+%\end{figure}
+
 \begin{figure}[H]
@@
 \scalebox{0.8}{
-\chemfig[angle increment=30]{
-H_2N-[1]S(=[4]O)(=[-2]O)-[1]*6(-=-(-[1]N*5(-N=(-[-1](-[-4]F)(-[-2]F)-[1])-=(-[4.5]*6(-=-(-[4.5])=-=))-))=-=)
-}}
-\caption{Chemical graph of Celecoxib.}
-\label{CelecoxibFigure}
-\end{figure}
-
-\begin{figure}[H]
-\captionsetup{type=scheme}
-\centering
-\scalebox{0.8}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 -[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]*5(--O-(=[2.25]O)-(-[4.5]*6(-=-=-=))=))=-=)
@@
 \begin{align}
-\frac{TN}{TN+FN}
+\frac{TN}{TN+FP}
 \end{align}
@@
 
+\begin{definition}\label{definitionPandasDataFrames}
+Pandas dataframes: type of data structure in Python characterized by a two-dimensional, size-mutable, and heterogeneous tabular data structure.
+The class dataframes class is provided by the Pandas library\cite{PythonPackagePandas}.
+It resambles to a table in a database or an Excel spreadsheet.
+\end{definition}
+
 \section{Tables of azophotoswitches}\label{appendixAzophotoshiches}
@@
 \scalebox{0.8}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-R_1)-(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-R_3)-=))=-))=-=)
@@
 \scalebox{0.8}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-O-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
@@
 \scalebox{0.8}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-S-(-R_1)=(-[:45]N=[3]N-[:135]*6(-=-(-R_2)=(-)-=))-=))=-=)
@@
 \scalebox{0.8}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*6(-=(-R_1)-(-N=[2]N-[4]*6(-=-(-R_2)=-=))=-=))=-=)
@@
 \scalebox{0.8}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-*5(-\chembelow{N}{H}-*6(-=-(-)=(-[3]N=[4.5]N-[6]*6(-=-(-R_1)=-=))-=)--=))=-=)
@@
 \scalebox{0.7}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-\chembelow{N}{H}-*6(-=-(-)=(-*6(-=-(-)=-=))-=)--))=-=)
@@
 \scalebox{0.7}{
-\chemfig[angle increment=30]{
+\chemfig[angle increment=30, bond style={line width=1pt}]{
 H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N=[-1.5]N-[-3]*5(=-R_1-*5(-R_2-(-)=(-*6(-=-(-R_3)=-=))-=)--))=-=)
@@
 
-Notice some molecules data do not appear in Table \ref{TableMainResults1}. This is due to inconclusives results of the $\Delta G_{binding}$ conputations.
+Notice some molecules data do not appear in Table \ref{TableMainResults1}. This is due to inconclusive results of the $\Delta G_{binding}$ computations.
 
@@
     \centering
-	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
+	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and statistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
 	\label{TableMainResults1}
@@
         Furan & \ref{figureCelecoxibFuran}.9 & \ch{F} & F &  & -0.1311 & 189\\ \hline
-        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
-        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241\\ \hline
             \end{tabular}
@@
     \centering	
-	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
+	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and statistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
 	\label{TableMainResults2}
@@
 Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
+        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
+        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241\\ \hline
         Thiophene & \ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} &  & 1.2724 & 192\\ \hline
@@
 		NumberOfTrees            & 250\\\hline
-		Erased Percentatge       & 0.0\%\\\hline
-		Splitting proportion     & 10.0\% for testing \\\hline
+		ErasedPercentatge       & 0.0\%\\\hline
+		SplittingProportion     & 10.0\% for testing \\\hline
 		minimumCorrelationFactor & 0.0\\\hline
